---
title: "CO_dataupdate.rmd"
author: "Ryan Peterson"
date: "2025-01-28"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r library}
suppressMessages( library(fields))
```

Work on data updates for:
  1. OLR: add in kernel function to scale larger lags
  2. Climate Mode Index: add in the excedance indicator functions to relate (via graph) to existing data.

Reference:
- data_cleaning.rmd (how all of this was originally orgnaized.)

# Data Import
  
```{r}
setwd("~/CO_AUS/Aus_CO-main")

load( "ne_data.rda")
load( "se_data.rda")
load( "bounded_data.rda")
load( "data_matrix.rda")
load( "lag_list.rda")

load( "lasso_pred.rda")

season_weeks <- c(35:52, 1:14)
```
  
  
# 1. OLR Kernel 



# 2. Climate Mode Indicator

Do we do like a quantile regression here? 

## Plot Data

(by week)

```{r}
#TODO plot data by week across all years (maybe include jitter?)
#x-axis as weeks

scale_preds <- bounded_pred_df
scale_preds$nino.anomaly <- scale(bounded_pred_df$nino.anomaly)
scale_preds$dmi.anomaly <- scale(bounded_pred_df$dmi.anomaly)
scale_preds$tsa.anomaly <- scale(bounded_pred_df$tsa.anomaly)
scale_preds$aao.anomaly <- scale(bounded_pred_df$aao.anomaly)

set.panel(2,2)
hist(scale_preds$nino.anomaly, main = "Nino")
hist(scale_preds$dmi.anomaly, main = "DMI")
hist(scale_preds$tsa.anomaly, main = "TSA")
hist(scale_preds$aao.anomaly, main = "AAO")

#data plot (test)
#TODO: add in color and a legend
#do this where only specific years have color
year_colors <- rep("black", length(unique(scale_preds$year)))
#loc_int <- which(unique(scale_preds$year) == 2015)
#year_colors[loc_int] <- "magenta2"

set.panel(2,2)
plot(1, type = "n", xlim = c(1, 52), ylim = range(scale_preds$nino.anomaly),
     xlab = "Week Number", ylab = " ", main = "Weekly Nino Data")
for (i in unique(scale_preds$year)) {
  year_data <- subset(scale_preds, year == i)
  points(jitter(year_data$week, amount = 0.25 ), year_data$nino.anomaly, pch = 20,
  col = year_colors[which(unique(scale_preds$year) == i)])
}

plot(1, type = "n", xlim = c(1, 52), ylim = range(scale_preds$dmi.anomaly),
     xlab = "Week Number", ylab = " ", main = "Weekly DMI Data")
for (i in unique(scale_preds$year)) {
  year_data <- subset(scale_preds, year == i)
  points(jitter(year_data$week, amount = 0.25 ), year_data$dmi.anomaly, pch = 20,
  col = year_colors[which(unique(scale_preds$year) == i)])
}

plot(1, type = "n", xlim = c(1, 52), ylim = range(scale_preds$tsa.anomaly),
     xlab = "Week Number", ylab = " ", main = "Weekly TSA Data")
for (i in unique(scale_preds$year)) {
  year_data <- subset(scale_preds, year == i)
  points(jitter(year_data$week, amount = 0.25 ), year_data$tsa.anomaly, pch = 20,
  col = year_colors[which(unique(scale_preds$year) == i)])
}

plot(1, type = "n", xlim = c(1, 52), ylim = range(scale_preds$aao.anomaly),
     xlab = "Week Number", ylab = " ", main = "Weekly AAO Data")
for (i in unique(scale_preds$year)) {
  year_data <- subset(scale_preds, year == i)
  points(jitter(year_data$week, amount = 0.25 ), year_data$aao.anomaly, pch = 20,
  col = year_colors[which(unique(scale_preds$year) == i)])
}

#dev.off()
```

## Quantile Checks

Plot a basic quantile lines on plots

Create a quantile regression for the data as well.

```{r nino_quantiles}
nino_base <- quantile(scale_preds$nino.anomaly, probs = c(0.25, 0.5, 0.75, 0.90))

nino_quant <- as.data.frame(matrix(NA, ncol = 5))
colnames(nino_quant) <- c("first", "second", "third", "top", "week")

for (j in unique(scale_preds$week)) {
  week_data <- subset(scale_preds, week == j)
  temp_quant <- quantile(week_data$nino.anomaly, probs = c(0.25, 0.5, 0.75, 0.9))
  nino_quant <- rbind(nino_quant, c(temp_quant,j))
}

nino_quant <- nino_quant[-1, ]

plot(1, type = "n", xlim = c(1, 52), ylim = range(scale_preds$nino.anomaly),
     xlab = "Week Number", ylab = " ", main = "Weekly Nino Data")
lines(unique(scale_preds$week), nino_quant$second, col = "cyan3", lwd = 3)
lines(unique(scale_preds$week), nino_quant$first, col = "blue2", lwd = 3)
lines(unique(scale_preds$week), nino_quant$third, col = "red3", lwd = 3)
lines(unique(scale_preds$week), nino_quant$top, col = "magenta3", lwd = 3)
yline(nino_base[1:3], col = c("blue2", "cyan3", "red3"), lty = 2, lwd =3)
for (i in unique(scale_preds$year)) {
  year_data <- subset(scale_preds, year == i)
  points(jitter(year_data$week, amount = 0.25 ), year_data$nino.anomaly, pch = 20,
  col = year_colors[which(unique(scale_preds$year) == i)])
}

#TODO add in legend

#update plot (and output .png) to color values above a quantile.
#nino_col <- ifelse()

```


```{r dmi_quant}
dmi_base <- quantile(scale_preds$dmi.anomaly, probs = c(0.25, 0.5, 0.75, 0.90))

dmi_quant <- as.data.frame(matrix(NA, ncol = 5))
colnames(dmi_quant) <- c("first", "second", "third", "top", "week")

for (j in unique(scale_preds$week)) {
  week_data <- subset(scale_preds, week == j)
  temp_quant <- quantile(week_data$dmi.anomaly, probs = c(0.25, 0.5, 0.75, 0.9))
  dmi_quant <- rbind(dmi_quant, c(temp_quant,j))
}

dmi_quant <- dmi_quant[-1, ]

plot(1, type = "n", xlim = c(1, 52), ylim = range(scale_preds$dmi.anomaly),
     xlab = "Week Number", ylab = " ", main = "Weekly DMI Data")
lines(unique(scale_preds$week), dmi_quant$second, col = "cyan3", lwd = 3)
lines(unique(scale_preds$week), dmi_quant$first, col = "blue2", lwd = 3)
lines(unique(scale_preds$week), dmi_quant$third, col = "red3", lwd = 3)
lines(unique(scale_preds$week), dmi_quant$top, col = "magenta3", lwd = 3)
yline(dmi_base[1:3], col = c("blue2", "cyan3", "red3"), lty = 2, lwd =3)
for (i in unique(scale_preds$year)) {
  year_data <- subset(scale_preds, year == i)
  points(jitter(year_data$week, amount = 0.25 ), year_data$dmi.anomaly, pch = 20,
  col = year_colors[which(unique(scale_preds$year) == i)])
}
```


```{r tsa_quant}
tsa_base <- quantile(scale_preds$tsa.anomaly, probs = c(0.25, 0.5, 0.75, 0.90))

tsa_quant <- as.data.frame(matrix(NA, ncol = 5))
colnames(tsa_quant) <- c("first", "second", "third", "top", "week")

for (j in unique(scale_preds$week)) {
  week_data <- subset(scale_preds, week == j)
  temp_quant <- quantile(week_data$tsa.anomaly, probs = c(0.25, 0.5, 0.75, 0.9))
  tsa_quant <- rbind(tsa_quant, c(temp_quant,j))
}

tsa_quant <- tsa_quant[-1, ]

plot(1, type = "n", xlim = c(1, 52), ylim = range(scale_preds$tsa.anomaly),
     xlab = "Week Number", ylab = " ", main = "Weekly TSA Data")
lines(unique(scale_preds$week), tsa_quant$second, col = "cyan3", lwd = 3)
lines(unique(scale_preds$week), tsa_quant$first, col = "blue2", lwd = 3)
lines(unique(scale_preds$week), tsa_quant$third, col = "red3", lwd = 3)
lines(unique(scale_preds$week), tsa_quant$top, col = "magenta3", lwd = 3)
yline(tsa_base[1:3], col = c("blue2", "cyan3", "red3"), lty = 2, lwd =3)
for (i in unique(scale_preds$year)) {
  year_data <- subset(scale_preds, year == i)
  points(jitter(year_data$week, amount = 0.25 ), year_data$tsa.anomaly, pch = 20,
  col = year_colors[which(unique(scale_preds$year) == i)])
}
```

```{r aao_quant}
aao_base <- quantile(scale_preds$aao.anomaly, probs = c(0.25, 0.5, 0.75, 0.9))

aao_quant <- as.data.frame(matrix(NA, ncol = 5))
colnames(aao_quant) <- c("first", "second", "third", "top", "week")

for (j in unique(scale_preds$week)) {
  week_data <- subset(scale_preds, week == j)
  temp_quant <- quantile(week_data$aao.anomaly, probs = c(0.25, 0.5, 0.75, 0.9))
  aao_quant <- rbind(aao_quant, c(temp_quant,j))
}

aao_quant <- aao_quant[-1, ]

plot(1, type = "n", xlim = c(1, 52), ylim = range(scale_preds$aao.anomaly),
     xlab = "Week Number", ylab = " ", main = "Weekly AAO Data")
lines(unique(scale_preds$week), aao_quant$second, col = "cyan3", lwd = 3)
lines(unique(scale_preds$week), aao_quant$first, col = "blue2", lwd = 3)
lines(unique(scale_preds$week), aao_quant$third, col = "red3", lwd = 3)
lines(unique(scale_preds$week), aao_quant$top, col = "magenta3", lwd = 3)
yline(aao_base[1:3], col = c("blue2", "cyan3", "red3"), lty = 2, lwd =3)
for (i in unique(scale_preds$year)) {
  year_data <- subset(scale_preds, year == i)
  points(jitter(year_data$week, amount = 0.25 ), year_data$aao.anomaly, pch = 20,
  col = year_colors[which(unique(scale_preds$year) == i)])
}

```


```{r}
setwd("~/CO_AUS/Aus_CO-main/Interactions")
  
png(filename = "pred_ind.png", width = 3200, height = 1600, res = 200)
set.panel(1,2)
hist(scale_preds$nino.anomaly, main = "Nino", xlab = "", cex.main = 2)
abline(v = nino_base[3], lty = 2, col = "red2", lwd = 2)

hist(scale_preds$dmi.anomaly, main = "DMI", xlab = "", cex.main = 2)
abline(v= dmi_base[3], lty = 2, col = "red2", lwd = 2)
dev.off()
```

Time permitting create a nice 'time-series' plot with values above the threshold a different color

```{r}
#get info from scale_preds to produce a point ts.
```


## Create Identity Function

```{r}
#using 0.9 quantile for full dataset
nino_subset <- subset(scale_preds, nino.anomaly >= nino_base[4])
dmi_subset <- subset(scale_preds, dmi.anomaly >= dmi_base[4])
tsa_subset <- subset(scale_preds, tsa.anomaly >= tsa_base[4])
aao_subset <- subset(scale_preds, aao.anomaly >= aao_base[4])

```


Referencing data_cleaning.rmd to create new matrices for this data.


```{r}
#using laglists (and the full quantiles) to create new identity function matrix

NE_laglist_q90 <- list()
SE_laglist_q90 <- list()

for (k in 1:32) {
  #temp dfs
  tempNE_df <- NE_laglist_std[[k]]
  tempSE_df <- SE_laglist_std[[k]]
  
  #NE modes
  nino_tempNE <- tempNE_df[,3:54]
  nino_indNE <- as.data.frame(ifelse(nino_tempNE > nino_base[4], 1, 0))
  
  dmi_tempNE <- tempNE_df[,55:106]
  dmi_indNE <- as.data.frame(ifelse(dmi_tempNE > dmi_base[4], 1, 0))
  
  tsa_tempNE <- tempNE_df[,107:158]
  tsa_indNE <- as.data.frame(ifelse(tsa_tempNE > tsa_base[4], 1, 0))
  
  aao_tempNE <- tempNE_df[,159:210]
  aao_indNE <- as.data.frame(ifelse(aao_tempNE > aao_base[4], 1, 0))
  
  #SE modes
  nino_tempSE <- tempSE_df[,3:54]
  nino_indSE <- as.data.frame(ifelse(nino_tempSE > nino_base[4], 1, 0))
  
  dmi_tempSE <- tempSE_df[,55:106]
  dmi_indSE <- as.data.frame(ifelse(dmi_tempSE > dmi_base[4], 1, 0))
  
  tsa_tempSE <- tempSE_df[,107:158]
  tsa_indSE <- as.data.frame(ifelse(tsa_tempSE > tsa_base[4], 1, 0))
  
  aao_tempSE <- tempSE_df[,159:210]
  aao_indSE <- as.data.frame(ifelse(aao_tempSE > aao_base[4], 1, 0)) 
  
  
  NEweek <- data.frame(tempNE_df[,1:2], nino_indNE, dmi_indNE, tsa_indNE, aao_indNE)
  SEweek <- data.frame(tempSE_df[,1:2], nino_indSE, dmi_indSE, tsa_indSE, aao_indSE)
  
  NE_laglist_q90[[paste("Week ", season_weeks[k])]] <- NEweek
  SE_laglist_q90[[paste("Week ", season_weeks[k])]] <- SEweek
}
```


```{r}
NE_laglist_q75 <- list()
SE_laglist_q75 <- list()

for (k in 1:32) {
  #temp dfs
  tempNE_df <- NE_laglist_std[[k]]
  tempSE_df <- SE_laglist_std[[k]]
  
  #NE modes
  nino_tempNE <- tempNE_df[,3:54]
  nino_indNE <- as.data.frame(ifelse(nino_tempNE > nino_base[3], 1, 0))
  
  dmi_tempNE <- tempNE_df[,55:106]
  dmi_indNE <- as.data.frame(ifelse(dmi_tempNE > dmi_base[3], 1, 0))
  
  tsa_tempNE <- tempNE_df[,107:158]
  tsa_indNE <- as.data.frame(ifelse(tsa_tempNE > tsa_base[3], 1, 0))
  
  aao_tempNE <- tempNE_df[,159:210]
  aao_indNE <- as.data.frame(ifelse(aao_tempNE > aao_base[3], 1, 0))
  
  #SE modes
  nino_tempSE <- tempSE_df[,3:54]
  nino_indSE <- as.data.frame(ifelse(nino_tempSE > nino_base[3], 1, 0))
  
  dmi_tempSE <- tempSE_df[,55:106]
  dmi_indSE <- as.data.frame(ifelse(dmi_tempSE > dmi_base[3], 1, 0))
  
  tsa_tempSE <- tempSE_df[,107:158]
  tsa_indSE <- as.data.frame(ifelse(tsa_tempSE > tsa_base[3], 1, 0))
  
  aao_tempSE <- tempSE_df[,159:210]
  aao_indSE <- as.data.frame(ifelse(aao_tempSE > aao_base[3], 1, 0)) 
  
  
  NEweek <- data.frame(tempNE_df[,1:2], nino_indNE, dmi_indNE, tsa_indNE, aao_indNE)
  SEweek <- data.frame(tempSE_df[,1:2], nino_indSE, dmi_indSE, tsa_indSE, aao_indSE)
  
  NE_laglist_q75[[paste("Week ", season_weeks[k])]] <- NEweek
  SE_laglist_q75[[paste("Week ", season_weeks[k])]] <- SEweek
}
```


```{r}
setwd("~/CO_AUS/Aus_CO-main")

save(NE_laglist_q90, SE_laglist_q90, NE_laglist_q75, SE_laglist_q75, file = "data_quantile.rda")
```

