---
title: "data_cleaning"
author: "Ryan Peterson"
date: "2024-07-14"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Library

```{r library}
#for data/date manipulating
suppressMessages(library(lubridate))
suppressMessages(library(reshape2)) #matrix long format
```


Baseline data cleaning markdown files, modify into an R script and adapt for all data cleaning uses.


TODO: 
1. add in lag.
2. add in other needed data matrices:
  a. response matrix
  b. predictor matrix
3. combine with initial data cleaning into a single R script. 

Continued Cleaning:
1. Include groupings from clustering.

# Data Upload

```{r import}
setwd("~/CO_AUS/Aus_CO-main")

#anomaly only response with week data
response_anoms <- read.csv("Data/response_anoms.csv", header = TRUE, stringsAsFactors = FALSE)

#predictors with week data
predictor_anoms <- read.csv("Data/predictor_anoms.csv", header = TRUE, stringsAsFactors = FALSE)

#weekly correlation data
week_corr <- read.csv("Data/week_correlation.csv", header = TRUE, 
                      stringsAsFactors = FALSE)

#add in OLR data
load( "olr_anom.rda")
```

# Cleaning Functions
(if needed)
```{r}

```

# Basic Cleaning

## OLR inclusions

(set-up OLR df to share similar information with current resp/pred data)

```{r olr_cleaning}
#additional cleaning for OLR data

olr_anom_df$Year <- year(olr_anom_df$Date)
bounded_olr_df <- olr_anom_df
```


## (Other...)

```{r data_cleaning}
week <- 1

response <- response_anoms
predictor <- predictor_anoms

resp_dates <- as_date(response[response$week == week, ]$time)
pred_dates <- as_date(predictor[predictor$week == week, ]$time)

#get minimum prediction date from response data
low_bound <- pred_dates[which(pred_dates == min(resp_dates)) - 1]
#get maximum response date from predictor data
upper_bound <- max(as_date(predictor$time)) + days(7)

#this requires week being set correctly above, that req should be fixed
bounded_pred_df <- predictor[predictor$time >= low_bound & predictor$time <= upper_bound, ]

bounded_resp_df <- response[response$time <= upper_bound, ]#temporarily changed so that each week has the same number of years

#2019 boundary (week 14 2019: end of 2018/2019 season)
max_date <- as_date(response_anoms[response_anoms$week == 14 & 
                                     response_anoms$year == 2020, ]$time)

bounded_pred_df <- bounded_pred_df[bounded_pred_df$time <= max_date, ]
bounded_resp_df <- bounded_resp_df[bounded_resp_df$time <= max_date, ]

rm(response, predictor, low_bound, upper_bound, 
   week, resp_dates, pred_dates, max_date)

### Correct for week 53

week_53 <- which(bounded_resp_df$week == 53, )
for (k in week_53) {
  bounded_resp_df[k-1, 3] <- mean(c(bounded_resp_df[k-1, 3], 
                                    bounded_resp_df[k, 3]))
  bounded_resp_df[k-1, 4] <- mean(c(bounded_resp_df[k-1, 4], 
                                    bounded_resp_df[k, 4]))
}
rm(k)
bounded_resp_df <- bounded_resp_df[-week_53, ]

#fix for the correct columns
week_53pred <- which(bounded_pred_df$week == 53, )
for (j in week_53pred) {
  bounded_pred_df[j-1, 3] <- mean(c(bounded_pred_df[j-1, 3], 
                                    bounded_pred_df[j, 3]))
  bounded_pred_df[j-1, 4] <- mean(c(bounded_pred_df[j-1, 4],
                                    bounded_pred_df[j, 4]))
  bounded_pred_df[j-1, 5] <- mean(c(bounded_pred_df[j-1, 5],
                                    bounded_pred_df[j, 5]))
  bounded_pred_df[j-1, 6] <- mean(c(bounded_pred_df[j-1, 6], 
                                    bounded_pred_df[j, 6]))
}

bounded_pred_df <- bounded_pred_df[-week_53pred, ]
rm(j, week_53, week_53pred)

bounded_pred_df <- bounded_pred_df[ ,-1]
row.names(bounded_pred_df) <- NULL

bounded_resp_df <- bounded_resp_df[, -1]
row.names(bounded_resp_df) <- NULL
```


# Set-up

```{r setup}
season_weeks <- c(35:52, 1:14)

#get years from bounded_resp
season_years <- unique(bounded_resp_df$year)

seasons <- c()
for (i in 1:(length(season_years)-1)) {
  temp_season <- paste0(season_years[i], "-", season_years[i+1])
  #print(temp_season)  
  seasons <- c(seasons, temp_season)
}


rm(i, season_years, temp_season)
```

# Modeling Data Frames

```{r}
NE_list <- list()
SE_list <- list()

for (k in season_weeks) {
  temp_resp <- bounded_resp_df[bounded_resp_df$week == k, ]
  
  if (k <= 14) {
    temp_resp <- temp_resp[-which(temp_resp$year == 2001), ]
  }
  
  test_year <- as.data.frame(matrix(seasons, ncol = 1, byrow = TRUE))
  test_year <- cbind(test_year, temp_resp$year)
  colnames(test_year) <- c("Seasons", "RespYear")
  
  
  tempNE_df <- as.data.frame(matrix(seasons, ncol = 1, byrow = TRUE))
  tempNE_df <- cbind(tempNE_df, temp_resp$NE_Aus_anomaly_co)
  colnames(tempNE_df) <- c("Seasons", "NE_Aus")
  
  tempSE_df <- as.data.frame(matrix(seasons, ncol = 1, byrow = TRUE))
  tempSE_df <- cbind(tempSE_df, temp_resp$SE_Aus_anomaly_co)
  colnames(tempSE_df) <- c("Seasons", "SE_Aus")
  
  #create temp df for each index
  tempNino_df <- as.data.frame(matrix(NA, nrow = nrow(tempNE_df), ncol = 1))
  tempDMI_df <- as.data.frame(matrix(NA, nrow = nrow(tempNE_df), ncol = 1))
  tempTSA_df <- as.data.frame(matrix(NA, nrow = nrow(tempNE_df), ncol = 1))
  tempAAO_df <- as.data.frame(matrix(NA, nrow = nrow(tempNE_df), ncol = 1))
  
  #temp df for OLRs
  tempNE_OLR_df <- as.data.frame(matrix(NA, nrow = nrow(tempNE_df), ncol = 1))
  tempSE_OLR_df <- as.data.frame(matrix(NA, nrow = nrow(tempNE_df), ncol = 1))
  
  for (j in 1:52) {
   temp_pred <- bounded_pred_df[bounded_pred_df$week == j, ]
   temp_olr <- olr_anom_df[olr_anom_df$Week == j, ]
  
    if(k > 14){ #for resp weeks in 35-52
      
      if (j <= 14) {
        temp_pred <- temp_pred[-which(temp_pred$year == 2020), ]
        temp_olr <- temp_olr[-which(temp_olr$Year == 2020), ]
      }
      
      if (j < k) { # for pred weeks < resp week (remove previous year)
        temp_pred <- temp_pred[-which(temp_pred$year == 2000), ]
        temp_olr <- temp_olr[-which(temp_olr$Year == 2000), ]
      } else { #for pred weeks >= resp weeks (remove latter year)
        temp_pred <- temp_pred[-which(temp_pred$year == 2019), ]
        temp_olr <- temp_olr[-which(temp_olr$Year == 2019), ]
      }
      
    } else { # for resp weeks in 1-14 (first year 2002)
      temp_pred <- temp_pred[-which(temp_pred$year == 2000), ]
      temp_olr <- temp_olr[-which(temp_olr$Year == 2000), ]
      
      if (j < k) { #pred weeks in 1-14 and < resp week
        
        temp_pred <- temp_pred[-which(temp_pred$year == 2001), ]
        temp_olr <- temp_olr[-which(temp_olr$Year == 2001), ]
      } else { # for pred week  >= resp week (previous year)
        
        if (j <= 14) {
          temp_pred <- temp_pred[-which(temp_pred$year == 2020), ]
          temp_olr <- temp_olr[-which(temp_olr$Year == 2020), ]
        }
      }
    }
    
    #temp nino assignment
    tempNino_df <- cbind(tempNino_df, temp_pred$nino.anomaly)
    colnames(tempNino_df)[ncol(tempNino_df)] <- paste0("nino", j)
  
    #temp dmi assignment
    tempDMI_df <- cbind(tempDMI_df, temp_pred$dmi.anomaly)
    colnames(tempDMI_df)[ncol(tempDMI_df)] <- paste0("dmi", j) 
    
    #temp tsa assignment
    tempTSA_df <- cbind(tempTSA_df, temp_pred$tsa.anomaly)
    colnames(tempTSA_df)[ncol(tempTSA_df)] <- paste0("tsa", j) 
    
    #temp aao assignment
    tempAAO_df <- cbind(tempAAO_df, temp_pred$aao.anomaly)
    colnames(tempAAO_df)[ncol(tempAAO_df)] <- paste0("aao", j) 
    
    test_year <- cbind(test_year, temp_pred$year)
    colnames(test_year)[ncol(test_year)] <- paste0("Week ", j)
    
    #olr:
    ##olr ne
    tempNE_OLR_df <- cbind(tempNE_OLR_df, temp_olr$NE_anom)
    colnames(tempNE_OLR_df)[ncol(tempNE_OLR_df)] <- paste0("NEolr", j)
    
    ##olr se
    tempSE_OLR_df <- cbind(tempSE_OLR_df, temp_olr$SE_anom)
    colnames(tempSE_OLR_df)[ncol(tempSE_OLR_df)] <- paste0("SEolr", j)    
  }
    
  tempNino_df <- tempNino_df[ ,-1]
  tempDMI_df <- tempDMI_df[ ,-1]
  tempTSA_df <- tempTSA_df[ ,-1]
  tempAAO_df <- tempAAO_df[ ,-1]
  
  tempNE_OLR_df <- tempNE_OLR_df[ ,-1]
  tempSE_OLR_df <- tempSE_OLR_df[ ,-1]
  
  tempNE_df <- cbind(tempNE_df, tempNino_df, tempDMI_df, tempTSA_df, tempAAO_df, tempNE_OLR_df)
  tempSE_df <- cbind(tempSE_df, tempNino_df, tempDMI_df, tempTSA_df, tempAAO_df, tempSE_OLR_df)
  
  NE_list[[paste("Week ", k)]] <- tempNE_df
  SE_list[[paste("Week ", k)]] <- tempSE_df
}
```

Update: change this to single .rda for multiple data frames.

```{r saves}
setwd("~/CO_AUS/Aus_CO-main")

save(NE_list, file = "ne_data.rda")
save(SE_list, file = "se_data.rda")

#save(bounded_pred_df, file = "bounded_pred.rda")
#save(bounded_resp_df, file = "bounded_resp.rda")
save(bounded_resp_df, bounded_pred_df, bounded_olr_df, file = "bounded_data.rda")
```


# Data Matrices

(From bounded data frames)

```{r}
#pred df to matrix

#predictors:

##indices
ex_preds <- NE_list[[1]][ ,3:210] #example df (for col names)
pred_matrix <- matrix(NA, ncol = 208)
colnames(pred_matrix) <- colnames(ex_preds)

for(i in 2000:2019){
  temp_pred <- bounded_pred_df[which(bounded_pred_df$year == i), ]
  pred_matrix <- rbind(pred_matrix, c(temp_pred$nino.anomaly, temp_pred$dmi.anomaly, 
                                      temp_pred$tsa.anomaly, temp_pred$aao.anomaly))
}

pred_matrix <- pred_matrix[-1, ]
rownames(pred_matrix) <-  2000:2019

##olr
ex_olr <- cbind(NE_list[[1]][ ,211:262], SE_list[[1]][ ,211:262]) #example df (for col names)
olr_matrix <- matrix(NA, ncol = 104)
colnames(olr_matrix) <- colnames(ex_olr)

for(k in 2000:2019){
  temp_olr <- bounded_olr_df[which(bounded_olr_df$Year == k), ]
  olr_matrix <- rbind(olr_matrix, c(temp_olr$NE_anom, temp_olr$SE_anom))
}

olr_matrix <- olr_matrix[-1, ]
rownames(olr_matrix) <- 2000:2019

#response (wildfire season only)

resp_matrix <- matrix(NA, ncol = 64)
colnames(resp_matrix) <- c(paste0("NEAus", season_weeks), paste0("SEAus", season_weeks))

for(j in 2001:2019){
#  temp_resp <- bounded_resp_df[which(bounded_resp_df$year == j), ]
  temp_resp1 <- bounded_resp_df[which(bounded_resp_df$year == j), ]
  season1 <- temp_resp1[which(temp_resp1$week %in% 35:52), ]
  
  temp_resp2 <- bounded_resp_df[which(bounded_resp_df$year == j+1), ]
  season2 <- temp_resp2[which(temp_resp2$week %in% 1:14), ]
  
  c(season1$NE_Aus_anomaly_co, season2$NE_Aus_anomaly_co)
  resp_matrix <- rbind(resp_matrix, c(season1$NE_Aus_anomaly_co, season2$NE_Aus_anomaly_co,
                                      season1$SE_Aus_anomaly_co, season2$SE_Aus_anomaly_co))
}


resp_matrix <- resp_matrix[-1, ]
rownames(resp_matrix) <- seasons

```



```{r matrix_out}
setwd("~/CO_AUS/Aus_CO-main")

save(pred_matrix, resp_matrix, olr_matrix, file = "data_matrix.rda")
#save(resp_matrix, file = "resp_matrix.rda")
```


# Lag Data

## Build data matrix/df for each week within range of study
(repeat the NE_list/SE_list that was done for weekly data)


```{r lagdata_list}
#TODO: create list of dfs (add in for loop)
NE_laglist <- list()
SE_laglist <- list()

#for i in season_weeks
for(i in season_weeks){
  
  temp_resp <- bounded_resp_df[bounded_resp_df$week == i, ]
    
  if (i <= 14) {
    temp_resp <- temp_resp[-which(temp_resp$year == 2001), ]
  }
  
  #TODO: use this to add the start of the weekly df's
  tempNE_df <- as.data.frame(matrix(seasons, ncol = 1, byrow = TRUE))
  tempNE_df <- cbind(tempNE_df, temp_resp$NE_Aus_anomaly_co)
  colnames(tempNE_df) <- c("Seasons", "NE_Aus")
    
  tempSE_df <- as.data.frame(matrix(seasons, ncol = 1, byrow = TRUE))
  tempSE_df <- cbind(tempSE_df, temp_resp$SE_Aus_anomaly_co)
  colnames(tempSE_df) <- c("Seasons", "SE_Aus")
  
  #current
  lag_resp <- temp_resp[which(temp_resp$week == i), ]
  min_year <- min(lag_resp$year)
  max_year <- max(lag_resp$year)
  
  #lag loop (inner loop)
  #resp_week_lag <- as.data.frame(matrix())
  nino_lag <- matrix(NA, nrow = length(lag_resp$NE_Aus_anomaly_co))
  dmi_lag <- matrix(NA, nrow = length(lag_resp$NE_Aus_anomaly_co))
  tsa_lag <- matrix(NA, nrow = length(lag_resp$NE_Aus_anomaly_co))
  aao_lag <- matrix(NA, nrow = length(lag_resp$NE_Aus_anomaly_co))
  
  NEolr_lag <- matrix(NA, nrow = length(lag_resp$NE_Aus_anomaly_co))
  SEolr_lag <- matrix(NA, nrow = length(lag_resp$NE_Aus_anomaly_co))
  
  week_vec <- c()
  lag_vec <- c()
  for (j in 1:52) {
    lag <- j
    lag_week <- i - lag
    if (lag_week <= 0) {
      lag_week <- 52 + lag_week
      lag_year <- c(min_year - 1, max_year -1)
    } else {
      lag_year <- min_year
      lag_year <- c(min_year, max_year)
    }
    
    lag_pred <- bounded_pred_df[which(bounded_pred_df$week == lag_week), ]
    lag_pred <- lag_pred[which(lag_pred$year >= lag_year[1] & lag_pred$year <= lag_year[2]), ]
    
    lag_olr <- bounded_olr_df[which(bounded_olr_df$Week == lag_week), ]
    lag_olr <- lag_olr[which(lag_olr$Year >= lag_year[1] & lag_olr$Year <= lag_year[2]), ]
    
    nino_lag <- cbind(nino_lag, lag_pred$nino.anomaly)
    dmi_lag <- cbind(dmi_lag, lag_pred$dmi.anomaly)
    tsa_lag <- cbind(tsa_lag, lag_pred$tsa.anomaly)
    aao_lag <- cbind(aao_lag, lag_pred$aao.anomaly)
    
    NEolr_lag <- cbind(NEolr_lag, lag_olr$NE_anom)
    SEolr_lag <- cbind(SEolr_lag, lag_olr$SE_anom) 
    
    week_vec <- c(week_vec, lag_week)
    lag_vec <- c(lag_vec, lag)
  }
  
  nino_lag <- nino_lag[,-1]
  colnames(nino_lag) <- paste0("nino_lag", lag_vec[1:52])
  
  dmi_lag <- dmi_lag[,-1]
  colnames(dmi_lag) <- paste0("dmi_lag", lag_vec[1:52])
  
  tsa_lag <- tsa_lag[,-1]
  colnames(tsa_lag) <- paste0("tsa_lag", lag_vec[1:52])
  
  aao_lag <- aao_lag[,-1]
  colnames(aao_lag) <- paste0("aao_lag", lag_vec[1:52])
  
  NEolr_lag <- NEolr_lag[ ,-1]
  colnames(NEolr_lag) <- paste0("NEolr_lag", lag_vec[1:52])
  
  SEolr_lag <- SEolr_lag[ ,-1]
  colnames(SEolr_lag) <- paste0("SEolr_lag", lag_vec[1:52])
  
  
  NEweek_lag <- data.frame(tempNE_df, nino_lag, dmi_lag, tsa_lag, aao_lag, NEolr_lag)
  SEweek_lag <- data.frame(tempSE_df, nino_lag, dmi_lag, tsa_lag, aao_lag, SEolr_lag)
  
  NE_laglist[[paste("Week ", i)]] <- NEweek_lag
  SE_laglist[[paste("Week ", i)]] <- SEweek_lag
}




```


```{r lagscake_list}
#TODO: create list of dfs (add in for loop)
NE_laglist_std <- list()
SE_laglist_std <- list()

#for i in season_weeks
for(i in season_weeks){
  
  temp_resp <- bounded_resp_df[bounded_resp_df$week == i, ]
    
  if (i <= 14) {
    temp_resp <- temp_resp[-which(temp_resp$year == 2001), ]
  }
  
  #TODO: use this to add the start of the weekly df's
  tempNE_df <- as.data.frame(matrix(seasons, ncol = 1, byrow = TRUE))
  tempNE_df <- cbind(tempNE_df, temp_resp$NE_Aus_anomaly_co)
  colnames(tempNE_df) <- c("Seasons", "NE_Aus")
    
  tempSE_df <- as.data.frame(matrix(seasons, ncol = 1, byrow = TRUE))
  tempSE_df <- cbind(tempSE_df, temp_resp$SE_Aus_anomaly_co)
  colnames(tempSE_df) <- c("Seasons", "SE_Aus")
  
  #current
  lag_resp <- temp_resp[which(temp_resp$week == i), ]
  min_year <- min(lag_resp$year)
  max_year <- max(lag_resp$year)
  
  #lag loop (inner loop)
  #resp_week_lag <- as.data.frame(matrix())
  nino_lag <- matrix(NA, nrow = length(lag_resp$NE_Aus_anomaly_co))
  dmi_lag <- matrix(NA, nrow = length(lag_resp$NE_Aus_anomaly_co))
  tsa_lag <- matrix(NA, nrow = length(lag_resp$NE_Aus_anomaly_co))
  aao_lag <- matrix(NA, nrow = length(lag_resp$NE_Aus_anomaly_co))
  
  NEolr_lag <- matrix(NA, nrow = length(lag_resp$NE_Aus_anomaly_co))
  SEolr_lag <- matrix(NA, nrow = length(lag_resp$NE_Aus_anomaly_co))
  
  week_vec <- c()
  lag_vec <- c()
  for (j in 1:52) {
    lag <- j
    lag_week <- i - lag
    if (lag_week <= 0) {
      lag_week <- 52 + lag_week
      lag_year <- c(min_year - 1, max_year -1)
    } else {
      lag_year <- min_year
      lag_year <- c(min_year, max_year)
    }
    
    lag_pred <- bounded_pred_df[which(bounded_pred_df$week == lag_week), ]
    lag_pred <- lag_pred[which(lag_pred$year >= lag_year[1] & lag_pred$year <= lag_year[2]), ]
    
    lag_olr <- bounded_olr_df[which(bounded_olr_df$Week == lag_week), ]
    lag_olr <- lag_olr[which(lag_olr$Year >= lag_year[1] & lag_olr$Year <= lag_year[2]), ]
    
    nino_lag <- cbind(nino_lag, lag_pred$nino.anomaly)
    dmi_lag <- cbind(dmi_lag, lag_pred$dmi.anomaly)
    tsa_lag <- cbind(tsa_lag, lag_pred$tsa.anomaly)
    aao_lag <- cbind(aao_lag, lag_pred$aao.anomaly)
    
    NEolr_lag <- cbind(NEolr_lag, lag_olr$NE_anom)
    SEolr_lag <- cbind(SEolr_lag, lag_olr$SE_anom) 
    
    week_vec <- c(week_vec, lag_week)
    lag_vec <- c(lag_vec, lag)
  }
  
  nino_lag <- nino_lag[,-1]
  colnames(nino_lag) <- paste0("nino_lag", lag_vec[1:52])
  nino_lag <- scale(nino_lag, center = TRUE, scale = TRUE)
  
  dmi_lag <- dmi_lag[,-1]
  colnames(dmi_lag) <- paste0("dmi_lag", lag_vec[1:52])
  dmi_lag <- scale(dmi_lag, center = TRUE, scale = TRUE)
  
  tsa_lag <- tsa_lag[,-1]
  colnames(tsa_lag) <- paste0("tsa_lag", lag_vec[1:52])
  tsa_lag <- scale(tsa_lag, center = TRUE, scale = TRUE)
  
  aao_lag <- aao_lag[,-1]
  colnames(aao_lag) <- paste0("aao_lag", lag_vec[1:52])
  aao_lag <- scale(aao_lag, center = TRUE, scale = TRUE)
  
  NEolr_lag <- NEolr_lag[ ,-1]
  colnames(NEolr_lag) <- paste0("NEolr_lag", lag_vec[1:52])
  NEolr_lag <- scale(NEolr_lag, center = TRUE, scale = TRUE)
  
  SEolr_lag <- SEolr_lag[ ,-1]
  colnames(SEolr_lag) <- paste0("SEolr_lag", lag_vec[1:52])
  SEolr_lag <- scale(SEolr_lag, center = TRUE, scale = TRUE)
  
  
  NEweek_lag <- data.frame(tempNE_df, nino_lag, dmi_lag, tsa_lag, aao_lag, NEolr_lag)
  SEweek_lag <- data.frame(tempSE_df, nino_lag, dmi_lag, tsa_lag, aao_lag, SEolr_lag)
  
  NE_laglist_std[[paste("Week ", i)]] <- NEweek_lag
  SE_laglist_std[[paste("Week ", i)]] <- SEweek_lag
}




```


```{r test}
#delete when done

test_std <- scale(nino_lag)
mean(test_std[,3])
var(test_std[,4])
```


```{r laglist_out}
setwd("~/CO_AUS/Aus_CO-main")

save(NE_laglist, NE_laglist_std, SE_laglist, SE_laglist_std, file = "lag_list.rda")
```


## Lag Matrix

```{r lag_matrix}

```




## Test Blocks

```{r lag_test}

i <- 35

j <- 1
lag <- j
lag_week <- i - lag

lag_week

```



```{r}

NE_list <- list()
SE_list <- list()

#week test
k <- season_weeks[20]
temp_resp <- bounded_resp_df[bounded_resp_df$week == k, ]

if (k <= 14) {
  temp_resp <- temp_resp[-which(temp_resp$year == 2001), ]
}

test_year <- as.data.frame(matrix(seasons, ncol = 1, byrow = TRUE))
test_year <- cbind(test_year, temp_resp$year)
colnames(test_year) <- c("Seasons", "RespYear")


tempNE_df <- as.data.frame(matrix(seasons, ncol = 1, byrow = TRUE))
tempNE_df <- cbind(tempNE_df, temp_resp$NE_Aus_anomaly_co)
colnames(tempNE_df) <- c("Seasons", "NE_Aus")

tempSE_df <- as.data.frame(matrix(seasons, ncol = 1, byrow = TRUE))
tempSE_df <- cbind(tempSE_df, temp_resp$SE_Aus_anomaly_co)
colnames(tempSE_df) <- c("Seasons", "SE_Aus")

#create temp df for each index
tempNino_df <- as.data.frame(matrix(NA, nrow = nrow(tempNE_df), ncol = 1))
tempDMI_df <- as.data.frame(matrix(NA, nrow = nrow(tempNE_df), ncol = 1))
tempTSA_df <- as.data.frame(matrix(NA, nrow = nrow(tempNE_df), ncol = 1))
tempAAO_df <- as.data.frame(matrix(NA, nrow = nrow(tempNE_df), ncol = 1))

for (j in 1:52) {
 temp_pred <- bounded_pred_df[bounded_pred_df$week == j, ]

  if(k > 14){ #for resp weeks in 35-52
    
    if (j <= 14) {
      temp_pred <- temp_pred[-which(temp_pred$year == 2020), ]
    }
    
    if (j < k) { # for pred weeks < resp week (remove previous year)
      temp_pred <- temp_pred[-which(temp_pred$year == 2000), ]
    } else { #for pred weeks >= resp weeks (remove latter year)
      temp_pred <- temp_pred[-which(temp_pred$year == 2019), ]
    }
    
  } else { # for resp weeks in 1-14 (first year 2002)
    temp_pred <- temp_pred[-which(temp_pred$year == 2000), ]
    
    if (j < k) { #pred weeks in 1-14 and < resp week
      
      temp_pred <- temp_pred[-which(temp_pred$year == 2001), ]
    } else { # for pred week  >= resp week (previous year)
      
      if (j <= 14) {
        temp_pred <- temp_pred[-which(temp_pred$year == 2020), ]
      }
    }
  }
  
  #temp nino assignment
  tempNino_df <- cbind(tempNino_df, temp_pred$nino.anomaly)
  colnames(tempNino_df)[ncol(tempNino_df)] <- paste0("nino", j)

  #temp dmi assignment
  tempDMI_df <- cbind(tempDMI_df, temp_pred$dmi.anomaly)
  colnames(tempDMI_df)[ncol(tempDMI_df)] <- paste0("dmi", j) 
  
  #temp tsa assignment
  tempTSA_df <- cbind(tempTSA_df, temp_pred$tsa.anomaly)
  colnames(tempTSA_df)[ncol(tempTSA_df)] <- paste0("tsa", j) 
  
  #temp aao assignment
  tempAAO_df <- cbind(tempAAO_df, temp_pred$aao.anomaly)
  colnames(tempAAO_df)[ncol(tempAAO_df)] <- paste0("aao", j) 
  
  test_year <- cbind(test_year, temp_pred$year)
  colnames(test_year)[ncol(test_year)] <- paste0("Week ", j)
}
  
tempNino_df <- tempNino_df[ ,-1]
tempDMI_df <- tempDMI_df[ ,-1]
tempTSA_df <- tempTSA_df[ ,-1]
tempAAO_df <- tempAAO_df[ ,-1]

#rm(k, j, temp_resp, temp_pred, temp_nino)
```


```{r histograms}
std_pred <- scale(pred_matrix)
std_resp <- scale(resp_matrix)

hist(resp_matrix)
hist(resp_matrix[ ,1:32], main = "NE Aus")
hist(std_resp[ ,1:32], main = "NE Aus - Std")
hist(resp_matrix[ ,33:64], main = "SE Aus")
hist(std_resp[ ,33:64], main = "SE Aus - Std")


hist(pred_matrix[ ,1:52], main = "Nino")
hist(std_pred[ ,1:52], main = "Nino - Std")
hist(pred_matrix[ ,53:104], main = "DMI")
hist(std_pred[ ,53:104], main = "DMI - Std")
hist(pred_matrix[ ,105:156], main = "TSA")
hist(std_pred[ ,105:156], main = "TSA - Std")
hist(pred_matrix[ ,157:208], main = "AAO")
hist(std_pred[ ,157:208], main = "AAO - Std")
```

