---
title: "interaction_lasso.rmd"
author: "Ryan Peterson"
date: "2025-06-16"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r library}
suppressMessages( library(hierNet)) #yes
suppressMessages( library(glmnet)) #test ridge regression for coefs
suppressMessages( library(RAMP)) #maybe
suppressMessages( library(MASS)) #for lm.ridge

suppressMessages( library(foreach)) #parallelization setup
suppressMessages( library(parallel))
suppressMessages( library(doParallel))

suppressMessages( library( lubridate)) #you know why
suppressMessages( library( colorspace)) #for some color alternatives
suppressMessages( library( fields)) #for set.panel() and others 
suppressMessages( library(ggpubr)) #nice tables for dfs (uses ggplot)

suppressMessages( library( caret)) #for confusion matrix

suppressMessages( library( tictoc)) #some timing
```

```{r data_functions}
# Data Set-Up
setwd("~/CO_AUS/Aus_CO-main/Interactions")

load( "Data/ne_data.rda")
load( "Data/se_data.rda")
load( "Data/bounded_data.rda")
load( "Data/data_matrix.rda")
load( "Data/lag_list.rda")
load( "Data/data_quantile.rda")

#functions:
#source("group_functions.R") #grouping/clustering
source("group_functionsNew.R") #new groupings
source("refit_functions.R") #coef/refit functions

```


Most up to date interaction lasso model runs.

(Note: the previous file 'new_interaction.rmd' was a little too messy after all the different runs that exist there.)

```{r setup}
#season years/weeks
season_weeks <- c(38:52, 1:14)
season_years <- unique(bounded_resp_df$year)

seasons <- c()
for (i in 1:(length(season_years)-1)) {
  temp_season <- paste0(season_years[i], "-", season_years[i+1])
  #print(temp_season)  
  seasons <- c(seasons, temp_season)
}
rm(i, temp_season)

#center response data
NEbase_matrix <- scale(resp_matrix[ ,1:32], center = TRUE, scale = FALSE)
SEbase_matrix <- scale(resp_matrix[ ,33:64], center = TRUE, scale = FALSE)

#NEAus
NEAus_1 <- NEbase_matrix[ ,4:12] 
NEAus_2 <- NEbase_matrix[ ,13:17]
NEAus_3 <- NEbase_matrix[ ,18:32]

#NEAus
SEAus_1 <- SEbase_matrix[ ,4:16] 
SEAus_2 <- SEbase_matrix[ ,17:20] 
SEAus_3 <- SEbase_matrix[ ,21:32]

NEAus_mat <- list(NEAus_1, NEAus_2, NEAus_3)
SEAus_mat <- list(SEAus_1, SEAus_2, SEAus_3)

rm(NEAus_1, NEAus_2, NEAus_3, SEAus_1, SEAus_2, SEAus_3)
```


# Test Cases

## NE Aus Group 1 (new)

Test case for NE Aus Group 1

```{r data_setup}
#temporary setup for testing use.
NE_resp <- NEresp_3group(NEAus_mat = NEAus_mat, j = 1:19)
NE_preds_test <- NElag_3group(NE_laglist = NE_laglist_std, j = 1:19)

#lambda setup (expand the range here)

#TODO: re-run this
lambda_seq <- seq(750, 580, length.out = 32)
```


```{r test_model}

y_1 <- as.numeric(NE_resp[[1]])

X_1 <- cbind(as.matrix(NE_preds_test[[1]][ ,1:260]))
  
test_path <- hierNet.path( X_1, y_1, strong = TRUE, lamlist = lambda_seq,
                              diagonal = TRUE, trace = 0) 
 

NE1_path <- test_path
#rerun without lambda list
 # test_path <- hierNet.path( X_1, y_1, strong = TRUE, nlam = 20,
 #                             diagonal = TRUE, trace = 0) 
```


```{r refit_test}

#NE Aus Group 1
NEcoefs1 <- get_coefs(NE1_path, max_index = 32, 
                      resp = NE_resp[[1]], preds = NE_preds_test[[1]], 
                      preds_quant =NE_preds_test[[1]])


NErefit1 <- refit_bic(NE1_path, max_index = 32, ebic.gamma = 0.25, gic.gamma = 2.15,
                      lambda.min = FALSE, AIC.c = FALSE,
                      intercept = FALSE,
                      resp = NE_resp[[1]], preds = NE_preds_test[[1]], 
                      preds_quant =NE_preds_test[[1]])

NErefit1[[5]]

NErefit1[[5]][,c(1,5,6)]
NErefit1[[5]][,c(1,8,9)]

which.min(NErefit1[[5]][ , 5]) #ridge BIC 
which.min(NErefit1[[5]][ , 6]) #lasso BIC 

which.min(NErefit1[[5]][ , 8]) #ridge eBIC 
which.min(NErefit1[[5]][ , 9]) #lasso eBIC 

i <- 1
ridge_coef <- NErefit1[[4]][[i]]
NEridge1_main <- ridge_coef
ridge_coef
length(ridge_coef)

#get length
fit_length <- NULL
for (i in 1:32) {
  ridge_coef <- NErefit1[[4]][[i]]
  fit_length <- c(fit_length, length(ridge_coef))
}
```

```{r temp_plots}


plot(1:32, NErefit1[[5]][,6], type = "b")

plot(1:32, fit_length)

```

### Old NE Aus group 1

```{r}

```



## SE Aus Group 1 (test)

Update SElag_3group to remove weeks 35-37 

```{r setup}
#temporary setup for testing use.
SE_resp <- SEresp_3group(SEAus_mat = SEAus_mat, j = 1:19)
SE_preds_test <- SElag_3group(SE_laglist = SE_laglist_std, j = 1:19)


#lambda setup
lambda_seq <- seq(650, 350, length.out = 32)
```


```{r model_path}
y_1 <- as.numeric(SE_resp[[1]])

X_1 <- cbind(as.matrix(SE_preds_test[[1]][ ,1:260]))
  
SE1_path <- hierNet.path( X_1, y_1, strong = TRUE, lamlist = lambda_seq,
                              diagonal = TRUE, trace = 0) 

#run as CV
#test_cv <- hierNet::hierNet.cv(test_path, X_1, y_1, nfolds = 5)
 
```


```{r refit}
SErefit1 <- refit_bic(SE1_path, max_index = 32, ebic.gamma = 0.25, gic.gamma = 2.15,
                      lambda.min = FALSE, AIC.c = FALSE,
                      intercept = FALSE,
                      resp = SE_resp[[1]], preds = SE_preds_test[[1]], 
                      preds_quant =SE_preds_test[[1]])

SErefit1[[5]]

SErefit1[[5]][,c(1,5,6)]
SErefit1[[5]][,c(1,8,9)]

which.min(SErefit1[[5]][ , 5]) #ridge BIC 
which.min(SErefit1[[5]][ , 6]) #lasso BIC 
which.min(SErefit1[[5]][ , 8]) #ridge eBIC 
which.min(SErefit1[[5]][ , 9]) #lasso eBIC 

i <- 16
ridge_coef <- SErefit1[[4]][[i]]
NEridge1_main <- ridge_coef
ridge_coef
length(ridge_coef)


#get LM coefs
j <- 16
lm_coef <- SErefit1[[2]][[j]]
#NEridge2_main <- ridge_coef
lm_coef
length(lm_coef)

summary(SErefit1[[1]][[j]])


#get length
fit_length <- NULL
for (i in 1:32) {
  ridge_coef <- SErefit1[[4]][[i]]
  fit_length <- c(fit_length, length(ridge_coef))
}
```

```{r temp_plots}


plot(1:32, SErefit1[[5]][,6], type = "b")

plot(1:32, fit_length)

```

```{r cv_test}

plot(test_cv)

```

## NE Aus Group 2 (Test)

```{r setup}
#temporary setup for testing use.
NE_resp <- NEresp_3group(NEAus_mat = NEAus_mat, j = 1:19)
NE_preds_test <- NElag_3group(NE_laglist = NE_laglist_std, j = 1:19)


#lambda setup (expand the range here)
lambda_seq <- seq(380, 155, length.out = 32)
```

```{r model_fit}
y_1 <- as.numeric(NE_resp[[2]])

X_1 <- cbind(as.matrix(NE_preds_test[[2]][ ,1:260]))
  
NE2_path <- hierNet.path( X_1, y_1, strong = TRUE, lamlist = lambda_seq,
                              diagonal = TRUE, trace = 0) 
 
```

```{r refit}
NErefit2 <- refit_bic(NE2_path, max_index = 32, ebic.gamma = 0.2, gic.gamma = 2.15,
                      lambda.min = FALSE, AIC.c = FALSE,
                      intercept = FALSE,
                      resp = NE_resp[[2]], preds = NE_preds_test[[2]], 
                      preds_quant =NE_preds_test[[2]])

NErefit2[[5]]

NErefit2[[5]][,c(1,5,6)]
NErefit2[[5]][,c(1,8,9)]

which.min(NErefit2[[5]][ , 5]) #ridge BIC 
which.min(NErefit2[[5]][ , 6]) #lasso BIC 
which.min(NErefit2[[5]][ , 7]) #glm eBIC 
which.min(NErefit2[[5]][ , 8]) #ridge eBIC 
which.min(NErefit2[[5]][ , 9]) #lasso eBIC 

i <- 3
ridge_coef <- NErefit2[[4]][[i]]
NEridge2_main <- ridge_coef
ridge_coef
length(ridge_coef)


#get LM coefs
j <- 3
lm_coef <- NErefit2[[2]][[j]]
#NEridge2_main <- ridge_coef
lm_coef
length(lm_coef)

summary(NErefit2[[1]][[j]])


#TODO: get lasso values (and compare to ridge)
NEcoefs2 <- get_coefs(NE2_path, max_index = 24, 
                      resp = NE_resp[[2]], preds = NE_preds_test[[2]], 
                      preds_quant =NE_preds_test[[2]])

NEcoefs2[[12]][[1]]$Main_Effect
NEcoefs2[[12]][[1]]$Coef

#get length
fit_length <- NULL
for (i in 1:32) {
  ridge_coef <- NErefit2[[4]][[i]]
  fit_length <- c(fit_length, length(ridge_coef))
}
```

```{r temp_plots}


plot(1:32, NErefit2[[5]][,6], type = "b")

plot(1:32, fit_length)

```



## SE Aus Group 2 (test)


```{r setup}
#temporary setup for testing use.
SE_resp <- SEresp_3group(SEAus_mat = SEAus_mat, j = 1:19)
SE_preds_test <- SElag_3group(SE_laglist = SE_laglist_std, j = 1:19)


#lambda setup
lambda_seq <- seq(205, 80, length.out = 32)
```

```{r model_fit}
y_1 <- as.numeric(SE_resp[[2]])

X_1 <- cbind(as.matrix(SE_preds_test[[2]][ ,1:260]))
  
SE2_path <- hierNet.path( X_1, y_1, strong = TRUE, lamlist = lambda_seq,
                              diagonal = TRUE, trace = 0) 

```

```{r refit}
SErefit2 <- refit_bic(SE2_path, max_index = 32, ebic.gamma = 0.25, gic.gamma = 2.15,
                      lambda.min = FALSE, AIC.c = FALSE,
                      intercept = FALSE,
                      resp = SE_resp[[2]], preds = SE_preds_test[[2]], 
                      preds_quant =SE_preds_test[[2]])

SErefit2[[5]]

SErefit2[[5]][,c(1,5,6)]
SErefit2[[5]][,c(1,8,9)]

which.min(SErefit2[[5]][ , 5]) #ridge BIC 
which.min(SErefit2[[5]][ , 6]) #lasso BIC 
which.min(SErefit2[[5]][ , 8]) #ridge eBIC 
which.min(SErefit2[[5]][ , 9]) #lasso eBIC 

i <- 14
ridge_coef <- SErefit2[[4]][[i]]
ridge_coef
length(ridge_coef)

#look at lm coeff
#get LM coefs
j <- 14
lm_coef <- SErefit2[[2]][[j]]
#NEridge2_main <- ridge_coef
lm_coef
length(lm_coef)

summary(SErefit2[[1]][[j]])



SEcoefs2 <- get_coefs(SE2_path, max_index = 32, 
                      resp = SE_resp[[2]], preds = SE_preds_test[[2]], 
                      preds_quant = SE_preds_test[[2]])


#SEcoefs2
SEcoefs2[[i]][[1]]$Main_Effect
SEcoefs2[[i]][[1]]$Coef

SEcoefs2[[i]][[2]]$Interact_Effect
SEcoefs2[[i]][[2]]$Coef

#due to hiernet constraints the above interaction coefs cannot exceed the main effect coefs.

#get length
fit_length <- NULL
for (i in 1:32) {
  ridge_coef <- SErefit2[[4]][[i]]
  fit_length <- c(fit_length, length(ridge_coef))
}

```

```{r plots}
plot(1:32, SErefit2[[5]][,6], type = "b")

plot(1:32, fit_length)
```


## NE Aus group 3 (Test)

### Full Group (no cuts)

```{r group3_Setup}
#temporary setup for testing use.
NE_resp <- NEresp_3group(NEAus_mat = NEAus_mat, j = 1:19)
NE_preds_test <- NElag_3group(NE_laglist = NE_laglist_std, j = 1:19)


#lambda setup (expand the range here)
lambda_seq <- seq(700, 270, length.out = 24)
```

```{r model_fit}
y_1 <- as.numeric(NE_resp[[3]])

X_1 <- cbind(as.matrix(NE_preds_test[[3]][ ,1:260]))
  
NE3_path <- hierNet.path( X_1, y_1, strong = TRUE, lamlist = lambda_seq,
                              diagonal = TRUE, trace = 0) 
 
```

```{r}

NErefit3 <- refit_bic(NE3_path, max_index = 24, ebic.gamma = 0.2, gic.gamma = 2.15,
                      lambda.min = FALSE, AIC.c = FALSE,
                      intercept = FALSE,
                      resp = NE_resp[[3]], preds = NE_preds_test[[3]], 
                      preds_quant =NE_preds_test[[3]])

NErefit3[[5]]

NErefit3[[5]][,c(1,5,6)]
NErefit3[[5]][,c(1,6)]

which.min(NErefit3[[5]][ , 5]) #ridge BIC 
which.min(NErefit3[[5]][ , 6]) #lasso BIC 
which.min(NErefit3[[5]][ , 7]) #glm eBIC 
which.min(NErefit3[[5]][ , 8]) #ridge eBIC 
which.min(NErefit3[[5]][ , 9]) #lasso eBIC 

i <- 16
ridge_coef <- NErefit3[[4]][[i]]
#NEridge2_main <- ridge_coef
ridge_coef
length(ridge_coef)


i <- 12
ridge_coef <- NErefit3[[4]][[i]]
#NEridge2_main <- ridge_coef
ridge_coef
length(ridge_coef)



#get LM coefs
j <- 13
lm_coef <- NErefit3[[2]][[j]]
#NEridge2_main <- ridge_coef
lm_coef
length(lm_coef)

summary(NErefit3[[1]][[j]])


#TODO: get lasso values (and compare to ridge)
NEcoefs3 <- get_coefs(NE3_path, max_index = 24, 
                      resp = NE_resp[[3]], preds = NE_preds_test[[3]], 
                      preds_quant =NE_preds_test[[3]])

NEcoefs3[[i]][[1]]$Main_Effect
NEcoefs3[[i]][[1]]$Coef

NEcoefs3[[i]][[2]]$Interact_Effect
NEcoefs3[[i]][[2]]$Coef

#get length
fit_length <- NULL
for (i in 1:24) {
  ridge_coef <- NErefit3[[4]][[i]]
  fit_length <- c(fit_length, length(ridge_coef))
}

```

```{r test_plots}
plot(1:24, NErefit3[[5]][,6], type = "b")

plot(1:24, fit_length)
```


### Reduced Group


```{r group3_Setup}
#NEAus
NEAus_1 <- NEbase_matrix[ ,4:12] 
NEAus_2 <- NEbase_matrix[ ,13:17]
NEAus_3 <- NEbase_matrix[ ,18:29]

#NEAus
SEAus_1 <- SEbase_matrix[ ,4:16] 
SEAus_2 <- SEbase_matrix[ ,17:20] 
SEAus_3 <- SEbase_matrix[ ,21:29]

NEAus_mat <- list(NEAus_1, NEAus_2, NEAus_3)
SEAus_mat <- list(SEAus_1, SEAus_2, SEAus_3)

rm(NEAus_1, NEAus_2, NEAus_3, SEAus_1, SEAus_2, SEAus_3)


#temporary setup for testing use.
NE_resp <- NEresp_3group(NEAus_mat = NEAus_mat, j = 1:19)
NE_preds_test <- NElag_3group(NE_laglist = NE_laglist_std, j = 1:19)


#lambda setup (expand the range here)
#lambda_seq <- seq(630, 450, length.out = 10)
lambda_seq <- seq(655, 450, length.out = 24)
```

```{r model_fit}
y_1 <- as.numeric(NE_resp[[3]])

X_1 <- cbind(as.matrix(NE_preds_test[[3]][ ,1:260]))
  
NE3_path_alt <- hierNet.path( X_1, y_1, strong = TRUE, lamlist = lambda_seq,
                              diagonal = TRUE, trace = 0) 
 
```

```{r}
NEcoefs3_test <- get_coefs(NE3_path_alt, max_index = 24, 
                      resp = NE_resp[[3]], preds = NE_preds_test[[3]], 
                      preds_quant =NE_preds_test[[3]])
#NEcoefs3_test

NErefit3_alt <- refit_bic(NE3_path_alt, max_index = 24, ebic.gamma = 0.2, gic.gamma = 2.15,
                      lambda.min = FALSE, AIC.c = FALSE,
                      intercept = FALSE,
                      resp = NE_resp[[3]], preds = NE_preds_test[[3]], 
                      preds_quant =NE_preds_test[[3]])

NErefit3_alt[[5]]

NErefit3_alt[[5]][,c(1,5,6)]
NErefit3_alt[[5]][,c(1,6)]

which.min(NErefit3_alt[[5]][ , 5]) #ridge BIC 
which.min(NErefit3_alt[[5]][ , 6]) #lasso BIC 
which.min(NErefit3_alt[[5]][ , 7]) #glm eBIC 
which.min(NErefit3_alt[[5]][ , 8]) #ridge eBIC 


i <- 2
ridge_coef <- NErefit3_alt[[4]][[i]]
#NEridge2_main <- ridge_coef
ridge_coef
length(ridge_coef)
```




## SE Aus Group 3 (test)

```{r setup}
#temporary setup for testing use.
SE_resp <- SEresp_3group(SEAus_mat = SEAus_mat, j = 1:19)
SE_preds_test <- SElag_3group(SE_laglist = SE_laglist_std, j = 1:19)


#lambda setup
lambda_seq <- seq(445, 120, length.out = 24)
```

```{r model_fit}
y_1 <- as.numeric(SE_resp[[3]])

X_1 <- cbind(as.matrix(SE_preds_test[[3]][ ,1:260]))
  
SE3_path <- hierNet.path( X_1, y_1, strong = TRUE, lamlist = lambda_seq,
                              diagonal = TRUE, trace = 0) 

```


```{r}
SErefit3_test <- refit_bic(SE3_path, max_index = 24, ebic.gamma = 0.25, gic.gamma = 2.15,
                      lambda.min = FALSE, AIC.c = FALSE,
                      intercept = FALSE,
                      resp = SE_resp[[3]], preds = SE_preds_test[[3]], 
                      preds_quant =SE_preds_test[[3]])

SErefit3_test[[5]]

SErefit3_test[[5]][,c(1,5,6)]
SErefit3_test[[5]][,c(1,8,9)]

which.min(SErefit3_test[[5]][ , 5]) #ridge BIC 
which.min(SErefit3_test[[5]][ , 6]) #lasso BIC 
which.min(SErefit3_test[[5]][ , 8]) #ridge eBIC 
which.min(SErefit3_test[[5]][ , 9]) #lasso eBIC 


i <- 6
ridge_coef <- SErefit3_test[[4]][[i]]
ridge_coef
length(ridge_coef)


#get length
fit_length <- NULL
for (i in 1:24) {
  ridge_coef <- SErefit3_test[[4]][[i]]
  fit_length <- c(fit_length, length(ridge_coef))
}

```

```{r plots}
plot(1:24, SErefit3_test[[5]][,6], type = "b")

plot(1:24, fit_length)
```

### Reduced Group 3

```{r setup}
#NEAus
SEAus_1 <- SEbase_matrix[ ,4:16] 
SEAus_2 <- SEbase_matrix[ ,17:20] 
SEAus_3 <- SEbase_matrix[ ,21:29]

SEAus_mat <- list(SEAus_1, SEAus_2, SEAus_3)

rm(SEAus_1, SEAus_2, SEAus_3)


#temporary setup for testing use.
SE_resp <- SEresp_3group(SEAus_mat = SEAus_mat, j = 1:19)
SE_preds_test <- SElag_3group(SE_laglist = SE_laglist_std, j = 1:19)


#lambda setup (expand the range here)
lambda_seq <- seq(400, 150, length.out = 24)
```

```{r}
y_1 <- as.numeric(SE_resp[[3]])

X_1 <- cbind(as.matrix(SE_preds_test[[3]][ ,1:260]))
  
SE3path_new <- hierNet.path( X_1, y_1, strong = TRUE, lamlist = lambda_seq,
                              diagonal = TRUE, trace = 0) 
```


```{r}

SEcoefs3 <- get_coefs(SE3path_new, max_index = 24, 
                      resp = SE_resp[[3]], preds = SE_preds_test[[3]], 
                      preds_quant = SE_preds_test[[3]])


SErefit3_new <- refit_bic(SE3path_new, max_index = 24, ebic.gamma = 0.25, gic.gamma = 2.15,
                      lambda.min = FALSE, AIC.c = FALSE,
                      intercept = FALSE,
                      resp = SE_resp[[3]], preds = SE_preds_test[[3]], 
                      preds_quant =SE_preds_test[[3]])

SErefit3_new[[5]]

SErefit3_new[[5]][,c(1,5,6)]
SErefit3_new[[5]][,c(1,8,9)]

which.min(SErefit3_new[[5]][ , 5]) #ridge BIC 
which.min(SErefit3_new[[5]][ , 6]) #lasso BIC 
which.min(SErefit3_new[[5]][ , 8]) #ridge eBIC 
which.min(SErefit3_new[[5]][ , 9]) #lasso eBIC 

i <- 16
ridge_coef <- SErefit3_new[[4]][[i]]
ridge_coef
length(ridge_coef)

```


# Models w/o 2019-2020

```{r NE_Aus_data}
#NEAus
NEAus_1 <- NEbase_matrix[ ,4:12] 
NEAus_2 <- NEbase_matrix[ ,13:17]
NEAus_3 <- NEbase_matrix[ ,18:32]

NEAus_mat <- list(NEAus_1, NEAus_2, NEAus_3)

rm(NEAus_1, NEAus_2, NEAus_3)
```


```{r SE_Aus_data}
#SEAus
SEAus_1 <- SEbase_matrix[ ,4:16] 
SEAus_2 <- SEbase_matrix[ ,17:20] 
SEAus_3 <- SEbase_matrix[ ,21:32]

SEAus_mat <- list(SEAus_1, SEAus_2, SEAus_3)

rm(SEAus_1, SEAus_2, SEAus_3)
```


## NE Aus Group 1 (w/o weeks 35-37)

(Note we need to re-run this)

```{r setup}
NE_preds <- NElag_3group(NE_laglist = NE_laglist_std, j = -c(19))
NE_resp <- NEresp_3group(NEAus_mat = NEAus_mat, j = -c(19))

lambda_seq <- seq(750, 575, length.out = 24)
#lambda_seq <- seq(770, 400, length.out = 15)
```


```{r model_fit}
y_1 <- as.numeric(NE_resp[[1]])

X_1 <- cbind(as.matrix(NE_preds[[1]][ ,1:260]))
  
NE1path_sans <- hierNet.path( X_1, y_1, strong = TRUE, lamlist = lambda_seq,
                              diagonal = TRUE, trace = 0) 

```


```{r refit}
NEcoefs1 <- get_coefs(NE1path_sans, max_index = 24, 
                      resp = NE_resp[[1]], preds = NE_preds[[1]], 
                      preds_quant = NE_preds[[1]])

NErefit1_sans <- refit_bic(NE1path_sans, max_index = 24, ebic.gamma = 0.25, gic.gamma = 2.15,
                      lambda.min = FALSE, AIC.c = FALSE,
                      intercept = TRUE,
                      resp = NE_resp[[1]], preds = NE_preds[[1]], 
                      preds_quant =NE_preds[[1]])

NErefit1_sans[[5]]

NErefit1_sans[[5]][,c(1,5,6)]
NErefit1_sans[[5]][,c(1,8,9)]

which.min(NErefit1_sans[[5]][ , 5]) #ridge BIC 
which.min(NErefit1_sans[[5]][ , 6]) #lasso BIC 
which.min(NErefit1_sans[[5]][ , 8]) #ridge eBIC 
which.min(NErefit1_sans[[5]][ , 9]) #lasso eBIC 

i <- 2
ridge_coef <- NErefit1_sans[[4]][[i]]
ridge_coef
length(ridge_coef)

summary(NErefit1_sans[[3]][[i]])


#get length
fit_length <- NULL
for (i in 1:24) {
  ridge_coef <- NErefit1_sans[[4]][[i]]
  fit_length <- c(fit_length, length(ridge_coef))
}
```

```{r plots}
plot(1:24, NErefit1_sans[[5]][,6], type = "b")

plot(1:24, fit_length)
```


## NE Aus Group 2

```{r setup}
NE_preds <- NElag_3group(NE_laglist = NE_laglist_std, j = -c(19))
NE_resp <- NEresp_3group(NEAus_mat = NEAus_mat, j = -c(19))

lambda_seq <- seq(425, 150, length.out = 24)
```


```{r model_fit}
y_1 <- as.numeric(NE_resp[[2]])

X_1 <- cbind(as.matrix(NE_preds[[2]][ ,1:260]))
  
NE2path_sans <- hierNet.path( X_1, y_1, strong = TRUE, lamlist = lambda_seq,
                              diagonal = TRUE, trace = 0) 

```


```{r refit}
NEcoefs2 <- get_coefs(NE2path_sans, max_index = 24, 
                      resp = NE_resp[[2]], preds = NE_preds[[2]], 
                      preds_quant = NE_preds[[2]])

NErefit2_sans <- refit_bic(NE2path_sans, max_index = 24, ebic.gamma = 0.25, gic.gamma = 2.15,
                      lambda.min = FALSE, AIC.c = FALSE,
                      intercept = FALSE,
                      resp = NE_resp[[2]], preds = NE_preds[[2]], 
                      preds_quant =NE_preds[[2]])

NErefit2_sans[[5]]

NErefit2_sans[[5]][,c(1,5,6)]
NErefit2_sans[[5]][,c(1,8,9)]

##which.min(NErefit2_sans[[5]][ , 4])
which.min(NErefit2_sans[[5]][ , 5]) #ridge BIC 
which.min(NErefit2_sans[[5]][ , 6]) #lasso BIC 
which.min(NErefit2_sans[[5]][ , 8]) #ridge eBIC 
which.min(NErefit2_sans[[5]][ , 9]) #lasso eBIC 

i <- 11
ridge_coef <- NErefit2_sans[[4]][[i]]
ridge_coef
length(ridge_coef)


#get LM coefs
j <- 11
lm_coef <- NErefit2_sans[[2]][[j]]
lm_coef
length(lm_coef)

summary(NErefit2_sans[[1]][[j]])

```


## NE Aus Group 3

TODO: update with end of season week cuts

```{r setup}
NE_preds <- NElag_3group(NE_laglist = NE_laglist_std, j = -c(19))
NE_resp <- NEresp_3group(NEAus_mat = NEAus_mat, j = -c(19))

lambda_seq <- seq(467, 225, length.out = 24) #using previous range
```

```{r model_fit}
y_1 <- as.numeric(NE_resp[[3]])

X_1 <- cbind(as.matrix(NE_preds[[3]][ ,1:260]))
  
NE3path_sans <- hierNet.path( X_1, y_1, strong = TRUE, lamlist = lambda_seq,
                              diagonal = TRUE, trace = 0) 
```

```{r refit}
NEcoefs3 <- get_coefs(NE3path_sans, max_index = 24, 
                      resp = NE_resp[[3]], preds = NE_preds[[3]], 
                      preds_quant = NE_preds[[3]])

NErefit3_sans <- refit_bic(NE3path_sans, max_index = 24, ebic.gamma = 0.25, gic.gamma = 2.15,
                      lambda.min = FALSE, AIC.c = FALSE,
                      intercept = FALSE,
                      resp = NE_resp[[3]], preds = NE_preds[[3]], 
                      preds_quant =NE_preds[[3]])

NErefit3_sans[[5]]

NErefit3_sans[[5]][,c(1,5,6)]
NErefit3_sans[[5]][,c(1,8,9)]

##which.min(NErefit2_sans[[5]][ , 4])
which.min(NErefit3_sans[[5]][ , 5]) #ridge BIC 
which.min(NErefit3_sans[[5]][ , 6]) #lasso BIC 
which.min(NErefit3_sans[[5]][ , 8]) #ridge eBIC 
which.min(NErefit3_sans[[5]][ , 9]) #lasso eBIC 


i <- 7
ridge_coef <- NErefit2_sans[[4]][[i]]
ridge_coef
length(ridge_coef)
```

## SE Aus Group 1 (w/o weeks 35-37)

TODO: pick up here tweak with the lambda range (good enough for now)

```{r setup}
SE_preds <- SElag_3group(SE_laglist = SE_laglist_std, j = -c(19))
SE_resp <- SEresp_3group(SEAus_mat = SEAus_mat, j = -c(19))

#lambda_seq <- seq(650, 275, length.out = 24) #using previous range
#test now that we cut weeks 35-37
lambda_seq <- seq(625, 350, length.out = 24)

```

```{r model_fit}
y_1 <- as.numeric(SE_resp[[1]])

X_1 <- cbind(as.matrix(SE_preds[[1]][ ,1:260]))
  
SE1path_sans <- hierNet.path( X_1, y_1, strong = TRUE, lamlist = lambda_seq,
                              diagonal = TRUE, trace = 0) 
```

```{r refit}
SEcoefs1 <- get_coefs(SE1path_sans, max_index = 24, 
                      resp = SE_resp[[1]], preds = SE_preds[[1]], 
                      preds_quant = SE_preds[[1]])


SErefit1_sans <- refit_bic(SE1path_sans, max_index = 24, ebic.gamma = 0.25, gic.gamma = 2.15,
                      lambda.min = FALSE, AIC.c = FALSE,
                      intercept = FALSE,
                      resp = SE_resp[[1]], preds = SE_preds[[1]], 
                      preds_quant =SE_preds[[1]])

SErefit1_sans[[5]]

SErefit1_sans[[5]][,c(1,5,6)]
SErefit1_sans[[5]][,c(1,8,9)]

##which.min(NErefit2_sans[[5]][ , 4])
which.min(SErefit1_sans[[5]][ , 5]) #ridge BIC 
which.min(SErefit1_sans[[5]][ , 6]) #lasso BIC 
which.min(SErefit1_sans[[5]][ , 8]) #ridge eBIC 
which.min(SErefit1_sans[[5]][ , 9]) #lasso eBIC 


i <- 13
ridge_coef <- SErefit1_sans[[4]][[i]]
ridge_coef
length(ridge_coef)


#get length
fit_length <- NULL
for (i in 1:24) {
  ridge_coef <- SErefit1_sans[[4]][[i]]
  fit_length <- c(fit_length, length(ridge_coef))
}

```

```{r plots}
plot(1:24, SErefit1_sans[[5]][,6], type = "b")

plot(1:24, fit_length)
```


## SE Aus Group 2


```{r setup}
SE_preds <- SElag_3group(SE_laglist = SE_laglist_std, j = -c(19))
SE_resp <- SEresp_3group(SEAus_mat = SEAus_mat, j = -c(19))


lambda_seq <- seq(140, 72, length.out = 32)

```


```{r model_fit}
y_1 <- as.numeric(SE_resp[[2]])

X_1 <- cbind(as.matrix(SE_preds[[2]][ ,1:260]))
  
SE2path_sans <- hierNet.path( X_1, y_1, strong = TRUE, lamlist = lambda_seq,
                              diagonal = TRUE, trace = 0) 
```


```{r refit}
SEcoefs2 <- get_coefs(SE2path_sans, max_index = 32, 
                      resp = SE_resp[[2]], preds = SE_preds[[2]], 
                      preds_quant = SE_preds[[2]])


SErefit2_sans <- refit_bic(SE2path_sans, max_index = 32, ebic.gamma = 0.25, gic.gamma = 2.15,
                      lambda.min = FALSE, AIC.c = FALSE,
                      intercept = FALSE,
                      resp = SE_resp[[2]], preds = SE_preds[[2]], 
                      preds_quant =SE_preds[[2]])

SErefit2_sans[[5]]

SErefit2_sans[[5]][,c(1,5,6)]
SErefit2_sans[[5]][,c(1,8,9)]

##which.min(NErefit2_sans[[5]][ , 4])
which.min(SErefit2_sans[[5]][ , 5]) #ridge BIC 
which.min(SErefit2_sans[[5]][ , 6]) #lasso BIC 
which.min(SErefit2_sans[[5]][ , 8]) #ridge eBIC 
which.min(SErefit2_sans[[5]][ , 9]) #lasso eBIC 


i <- 6
ridge_coef <- SErefit2_sans[[4]][[i]]
ridge_coef
length(ridge_coef)

summary(SErefit2_sans[[1]][[i]])


#get length
fit_length <- NULL
for (i in 1:32) {
  ridge_coef <- SErefit2_sans[[4]][[i]]
  fit_length <- c(fit_length, length(ridge_coef))
}

```


```{r plots}
plot(1:32, SErefit2_sans[[5]][,5], type = "b")

plot(1:32, fit_length)
```


## SE Aus Group 3

```{r setup}
SE_preds <- SElag_3group(SE_laglist = SE_laglist_std, j = -c(19))
SE_resp <- SEresp_3group(SEAus_mat = SEAus_mat, j = -c(19))


lambda_seq <- seq(345, 215, length.out = 24)

```


```{r model_fit}
y_1 <- as.numeric(SE_resp[[3]])

X_1 <- cbind(as.matrix(SE_preds[[3]][ ,1:260]))
  
SE3path_sans <- hierNet.path( X_1, y_1, strong = TRUE, lamlist = lambda_seq,
                              diagonal = TRUE, trace = 0) 
```


```{r refit}
SEcoefs3 <- get_coefs(SE3path_sans, max_index = 24, 
                      resp = SE_resp[[3]], preds = SE_preds[[3]], 
                      preds_quant = SE_preds[[3]])


SErefit3_sans <- refit_bic(SE3path_sans, max_index = 24, ebic.gamma = 0.25, gic.gamma = 2.15,
                      lambda.min = FALSE, AIC.c = FALSE,
                      intercept = FALSE,
                      resp = SE_resp[[3]], preds = SE_preds[[3]], 
                      preds_quant =SE_preds[[3]])

SErefit3_sans[[5]]

SErefit3_sans[[5]][,c(1,5,6)]
SErefit3_sans[[5]][,c(1,8,9)]

##which.min(NErefit2_sans[[5]][ , 4])
which.min(SErefit3_sans[[5]][ , 5]) #ridge BIC 
which.min(SErefit3_sans[[5]][ , 6]) #lasso BIC 
which.min(SErefit3_sans[[5]][ , 8]) #ridge eBIC 
which.min(SErefit3_sans[[5]][ , 9]) #lasso eBIC 


i <- 7
ridge_coef <- SErefit3_sans[[4]][[i]]
ridge_coef
length(ridge_coef)

summary(SErefit3_sans[[1]][[i]])


#get length
fit_length <- NULL
for (i in 1:24) {
  ridge_coef <- SErefit3_sans[[4]][[i]]
  fit_length <- c(fit_length, length(ridge_coef))
}

```

