---
title: "IOD_sst_prep"
author: "Ryan Peterson"
date: "2025-08-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r library}
#.nc files
suppressMessages(library(ncdf4))
suppressMessages(library(terra))

# date/data mgmt
suppressMessages(library(lubridate))
suppressMessages(library(abind))

#visualization and interpolation
suppressMessages(library(fields))
suppressMessages(library(colorspace))
suppressMessages(library(RColorBrewer))
suppressMessages(library(scales)) #for adjusting opacity
```

Data Prep file for the following reanalysis products:

1. GODAS (NCEP Global Ocean Data Assimilation System from 1980 to 2019)
  a. Resolution:
2. ORA-S5 (ECMWF Ocean Reanalysis System 5 from 1979 to 2018)
  a. Resolution
3. OISST v2 (NOAA Optimum Interpolation SST version 2 from 1982 to 2019)
  a. Resolution
4. SODA3.3.1 (Simple Ocean Data Assimilation version 3.3.1 from 1980 to 2015)
  a. Resolution


Goal: be able to produce flexible (wrt spatial grid and time) sst arrays for each data product


# GODAS

```{r GODAS_import}
setwd("~/CO_AUS/Aus_CO-main")

#GODAS data only (yearly .nc 1982-2015)
#1982
nc.GODAS.1982 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1982.nc")

#1983
nc.GODAS.1983 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1983.nc")

#1984
nc.GODAS.1984 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1984.nc")

#1985
nc.GODAS.1985 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1985.nc")

#1986
nc.GODAS.1986 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1986.nc")

#1987
nc.GODAS.1987 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1987.nc")

#1988
nc.GODAS.1988 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1988.nc")

#1989
nc.GODAS.1989 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1989.nc")

#1990
nc.GODAS.1990 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1990.nc")

#1991
nc.GODAS.1991 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1991.nc")

#1992
nc.GODAS.1992 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1992.nc")

#1993
nc.GODAS.1993 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1993.nc")

#1994
nc.GODAS.1994 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1994.nc")

#1995
nc.GODAS.1995 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1995.nc")

#1996
nc.GODAS.1996 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1996.nc")

#1997
nc.GODAS.1997 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1997.nc")

#1998
nc.GODAS.1998 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1998.nc")

#1999
nc.GODAS.1999 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1999.nc")

#2000
nc.GODAS.2000 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2000.nc")

#2001
nc.GODAS.2001 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2001.nc")

#2002
nc.GODAS.2002 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2002.nc")

#2003
nc.GODAS.2003 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2003.nc")

#2004
nc.GODAS.2004 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2004.nc")

#2005
nc.GODAS.2005 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2005.nc")

#2006
nc.GODAS.2006 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2006.nc")

#2007
nc.GODAS.2007 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2007.nc")

#2008
nc.GODAS.2008 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2008.nc")

#2009
nc.GODAS.2009 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2009.nc")

#2010
nc.GODAS.2010 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2010.nc")

#2011
nc.GODAS.2011 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2011.nc")

#2012
nc.GODAS.2012 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2012.nc")

#2013
nc.GODAS.2013 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2013.nc")

#2014
nc.GODAS.2014 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2014.nc")

#2015
nc.GODAS.2015 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2015.nc")

```

```{r additional_GODAS_import}
#include back to 1980
#1980
nc.GODAS.1980 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1980.nc")

#1981
nc.GODAS.1981 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1981.nc")

#include up to 2019
#2016
nc.GODAS.2016 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2016.nc")

#2017
nc.GODAS.2017 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2017.nc")

#2018
nc.GODAS.2018 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2018.nc")

#2019
nc.GODAS.2019 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2019.nc")
```



