---
title: "IOD_sst_prep"
author: "Ryan Peterson"
date: "2025-08-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r library}
#.nc files
suppressMessages(library(ncdf4))
suppressMessages(library(terra))

# date/data mgmt
suppressMessages(library(lubridate))
suppressMessages(library(abind))

#visualization and interpolation
suppressMessages(library(fields))
suppressMessages(library(colorspace))
suppressMessages(library(RColorBrewer))
suppressMessages(library(scales)) #for adjusting opacity
```

Data Prep file for the following reanalysis products:

1. GODAS (NCEP Global Ocean Data Assimilation System from 1980 to 2019)
  a. Resolution:
2. ORA-S5 (ECMWF Ocean Reanalysis System 5 from 1979 to 2018)
  a. Resolution
3. OISST v2 (NOAA Optimum Interpolation SST version 2 from 1982 to 2019)
  a. Resolution
4. SODA3.3.1 (Simple Ocean Data Assimilation version 3.3.1 from 1980 to 2015)
  a. Resolution


Goal: be able to produce flexible (wrt spatial grid and time) sst arrays for each data product

Note: we are moving all the associated EOF prep files to here then moving them elsewhere.

# Set-up

```{r ranges}
#indian ocean region
wide_maxLon <- 120
wide_minLon <- 30
wide_maxLat <- 20
wide_minLat <- -20

#DMI west/WTIO (50, -10) X (70, 10) 
wDMI_maxLon <- 70
wDMI_minLon <- 50
wDMI_maxLat <- 10
wDMI_minLat <- -10

#DMI east/SETIO (90, -10) X (110, 0)
eDMI_maxLon <- 110
eDMI_minLon <- 90
eDMI_maxLat <- 0
eDMI_minLat <- -10

#pIOD (40, -5) X (100, 5)
pIOD_maxLon <- 100
pIOD_minLon <- 40 
pIOD_maxLat <- 5
pIOD_minLat <- -5

```

```{r grid_points}
#setup grid points for 1x1 degree resolution.
#lon.wide <- seq(wide_minLon+0.5, wide_maxLon-0.5, by = 1)
#lat.wide <- seq(wide_minLat+0.5, wide_maxLat-0.5, by = 1)

lon.wide <- seq(wide_minLon, wide_maxLon, by = 1)
lat.wide <- seq(wide_minLat, wide_maxLat, by = 1)

#grid list from 
grid.list <- list(x = lon.wide,
                  y = lat.wide)


#TODO: rm() region boundaries after all the points and ranges are setup
```


# GODAS

```{r GODAS_import}
setwd("~/CO_AUS/Aus_CO-main")

#GODAS data only (yearly .nc 1982-2015)
#1982
nc.GODAS.1982 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1982.nc")

#1983
nc.GODAS.1983 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1983.nc")

#1984
nc.GODAS.1984 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1984.nc")

#1985
nc.GODAS.1985 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1985.nc")

#1986
nc.GODAS.1986 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1986.nc")

#1987
nc.GODAS.1987 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1987.nc")

#1988
nc.GODAS.1988 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1988.nc")

#1989
nc.GODAS.1989 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1989.nc")

#1990
nc.GODAS.1990 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1990.nc")

#1991
nc.GODAS.1991 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1991.nc")

#1992
nc.GODAS.1992 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1992.nc")

#1993
nc.GODAS.1993 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1993.nc")

#1994
nc.GODAS.1994 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1994.nc")

#1995
nc.GODAS.1995 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1995.nc")

#1996
nc.GODAS.1996 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1996.nc")

#1997
nc.GODAS.1997 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1997.nc")

#1998
nc.GODAS.1998 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1998.nc")

#1999
nc.GODAS.1999 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1999.nc")

#2000
nc.GODAS.2000 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2000.nc")

#2001
nc.GODAS.2001 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2001.nc")

#2002
nc.GODAS.2002 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2002.nc")

#2003
nc.GODAS.2003 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2003.nc")

#2004
nc.GODAS.2004 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2004.nc")

#2005
nc.GODAS.2005 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2005.nc")

#2006
nc.GODAS.2006 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2006.nc")

#2007
nc.GODAS.2007 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2007.nc")

#2008
nc.GODAS.2008 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2008.nc")

#2009
nc.GODAS.2009 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2009.nc")

#2010
nc.GODAS.2010 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2010.nc")

#2011
nc.GODAS.2011 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2011.nc")

#2012
nc.GODAS.2012 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2012.nc")

#2013
nc.GODAS.2013 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2013.nc")

#2014
nc.GODAS.2014 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2014.nc")

#2015
nc.GODAS.2015 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2015.nc")

```

```{r additional_GODAS_import}
#include back to 1980
#1980
nc.GODAS.1980 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1980.nc")

#1981
nc.GODAS.1981 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.1981.nc")

#include up to 2019
#2016
nc.GODAS.2016 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2016.nc")

#2017
nc.GODAS.2017 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2017.nc")

#2018
nc.GODAS.2018 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2018.nc")

#2019
nc.GODAS.2019 <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/pottmp.2019.nc")
```


## GODAS Functions

```{r prep_functions}
#sorting/extraction of godas .nc data
godas_prep <- function(nc.data){
  
  #extract lon.lat
  lon.grid.temp <- nc.data[["dim"]][["lon"]][["vals"]]
  lat.grid.temp <- nc.data[["dim"]][["lat"]][["vals"]]
  
  #reorder lon for 
  lon.grid.temp[lon.grid.temp >= 180] <- lon.grid.temp[lon.grid.temp >= 180] - 360
  lon.order.temp <- order(lon.grid.temp)
  
  lon.grid.temp <- lon.grid.temp[lon.order.temp]
  
  #reorder lat
  lat.order.temp <- order(lat.grid.temp, decreasing = TRUE)
  lat.grid.temp <- lat.grid.temp[lat.order.temp]
  
  #times for months
  times.temp <- ncvar_get(nc.data, "time") # days since 1800-01-01 00:00:0.0
  times.temp <- as_datetime("1800-01-01T00:00:00") + days(times.temp)
  
  #temps, as array (lon, lat, level, time)
  #TODO adjust from K to c (K - 273.15)
  sst.temp <- ncvar_get(nc.data, "pottmp")
  sst.temp <- sst.temp[lon.order.temp, lat.order.temp, 1, ] #level: depth 5m
  
  #adjust to C from K (c = K - 273.15)
  sst.temp <- sst.temp - 273.15
  
  #return lon, lat, time, sst
  return(list(
    lon = lon.grid.temp,
    lat = lat.grid.temp,
    time = times.temp,
    sst = sst.temp))
}


```

## GODAS Data Setup

```{r data_cleaning}
#data cleaning 
godas_list <- list(nc.GODAS.1982, nc.GODAS.1983, nc.GODAS.1984, nc.GODAS.1985, nc.GODAS.1986, 
                   nc.GODAS.1987, nc.GODAS.1988, nc.GODAS.1989, nc.GODAS.1990, nc.GODAS.1991,
                   nc.GODAS.1992, nc.GODAS.1993, nc.GODAS.1994, nc.GODAS.1995, nc.GODAS.1996,
                   nc.GODAS.1997, nc.GODAS.1998, nc.GODAS.1999, nc.GODAS.2000, nc.GODAS.2001,
                   nc.GODAS.2002, nc.GODAS.2003, nc.GODAS.2004, nc.GODAS.2005, nc.GODAS.2006,
                   nc.GODAS.2007, nc.GODAS.2008, nc.GODAS.2009, nc.GODAS.2010, nc.GODAS.2011,
                   nc.GODAS.2012, nc.GODAS.2013, nc.GODAS.2014, nc.GODAS.2015)

#get lon, lat, sst, and times
sst.GODAS.new <- NULL
for (i in 1:length(godas_list)) {
  nc.temp <- godas_list[[i]] 
  
  temp.nc.godas <- godas_prep(nc.temp)
  temp.lon <- temp.nc.godas$lon
  temp.lat <- temp.nc.godas$lat
  temp.sst <- temp.nc.godas$sst
  
  #get reduce range (indian ocean region)
  new.lon <- temp.lon[temp.lon <= wide_maxLon & temp.lon >= wide_minLon]
  lon.range <- range(which(temp.lon <= wide_maxLon & temp.lon >= wide_minLon))
  new.lat <- temp.lat[temp.lat <= wide_maxLat & temp.lat >= wide_minLat]
  lat.range <- range(which(temp.lat <= wide_maxLat & temp.lat >= wide_minLat))
  
  new.sst <- temp.sst[lon.range[1]:lon.range[2], lat.range[1]:lat.range[2], ]
  
  #interpolate to 1x1 grid
  sst.godas.interp <- NULL
  for (j in 1:dim(new.sst)[3]) {
    obj.godas <- list(x = new.lon, y = rev(new.lat), z = new.sst[,,j])
  
    interp.out <-  interp.surface.grid(obj.godas, grid.list)
    
    sst.godas.interp <- abind(sst.godas.interp, interp.out$z[ ,ncol(interp.out$z):1 ], along = 3)
  }
  sst.GODAS.new <- abind(sst.GODAS.new, sst.godas.interp, along = 3)
}

rm(nc.GODAS.1982, nc.GODAS.1983, nc.GODAS.1984, nc.GODAS.1985, nc.GODAS.1986, 
                   nc.GODAS.1987, nc.GODAS.1988, nc.GODAS.1989, nc.GODAS.1990, nc.GODAS.1991,
                   nc.GODAS.1992, nc.GODAS.1993, nc.GODAS.1994, nc.GODAS.1995, nc.GODAS.1996,
                   nc.GODAS.1997, nc.GODAS.1998, nc.GODAS.1999, nc.GODAS.2000, nc.GODAS.2001,
                   nc.GODAS.2002, nc.GODAS.2003, nc.GODAS.2004, nc.GODAS.2005, nc.GODAS.2006,
                   nc.GODAS.2007, nc.GODAS.2008, nc.GODAS.2009, nc.GODAS.2010, nc.GODAS.2011,
                   nc.GODAS.2012, nc.GODAS.2013, nc.GODAS.2014, nc.GODAS.2015)


dim(sst.GODAS.new)



```

### GODAS w/o Interpolation

```{r godas_raw}
#data cleaning 
godas_list <- list(nc.GODAS.1982, nc.GODAS.1983, nc.GODAS.1984, nc.GODAS.1985, nc.GODAS.1986, 
                   nc.GODAS.1987, nc.GODAS.1988, nc.GODAS.1989, nc.GODAS.1990, nc.GODAS.1991,
                   nc.GODAS.1992, nc.GODAS.1993, nc.GODAS.1994, nc.GODAS.1995, nc.GODAS.1996,
                   nc.GODAS.1997, nc.GODAS.1998, nc.GODAS.1999, nc.GODAS.2000, nc.GODAS.2001,
                   nc.GODAS.2002, nc.GODAS.2003, nc.GODAS.2004, nc.GODAS.2005, nc.GODAS.2006,
                   nc.GODAS.2007, nc.GODAS.2008, nc.GODAS.2009, nc.GODAS.2010, nc.GODAS.2011,
                   nc.GODAS.2012, nc.GODAS.2013, nc.GODAS.2014, nc.GODAS.2015)

#get lon, lat, sst, and times
sst.GODAS.new2 <- NULL
for (i in 1:length(godas_list)) {
  nc.temp <- godas_list[[i]] 
  
  temp.nc.godas <- godas_prep(nc.temp)
  temp.lon <- temp.nc.godas$lon
  temp.lat <- temp.nc.godas$lat
  temp.sst <- temp.nc.godas$sst
  
  #get reduce range (indian ocean region)
  new.lon <- temp.lon[temp.lon <= wide_maxLon & temp.lon >= wide_minLon]
  lon.range <- range(which(temp.lon <= wide_maxLon & temp.lon >= wide_minLon))
  new.lat <- temp.lat[temp.lat <= wide_maxLat & temp.lat >= wide_minLat]
  lat.range <- range(which(temp.lat <= wide_maxLat & temp.lat >= wide_minLat))
  
  #assign
  sst.temp <- temp.sst[lon.range[1]:lon.range[2], lat.range[1]:lat.range[2], ]
  
  sst.GODAS.new2 <- abind(sst.GODAS.new2, sst.temp, along = 3)
}

GODAS.lon <- new.lon
GODAS.lat <- new.lat

rm(nc.GODAS.1982, nc.GODAS.1983, nc.GODAS.1984, nc.GODAS.1985, nc.GODAS.1986, 
                   nc.GODAS.1987, nc.GODAS.1988, nc.GODAS.1989, nc.GODAS.1990, nc.GODAS.1991,
                   nc.GODAS.1992, nc.GODAS.1993, nc.GODAS.1994, nc.GODAS.1995, nc.GODAS.1996,
                   nc.GODAS.1997, nc.GODAS.1998, nc.GODAS.1999, nc.GODAS.2000, nc.GODAS.2001,
                   nc.GODAS.2002, nc.GODAS.2003, nc.GODAS.2004, nc.GODAS.2005, nc.GODAS.2006,
                   nc.GODAS.2007, nc.GODAS.2008, nc.GODAS.2009, nc.GODAS.2010, nc.GODAS.2011,
                   nc.GODAS.2012, nc.GODAS.2013, nc.GODAS.2014, nc.GODAS.2015)

dim(sst.GODAS.new2)

```

```{r save_godas}
setwd("~/CO_AUS/Aus_CO-main/pIOD")
save(sst.GODAS.new, sst.GODAS.new2, GODAS.lon, GODAS.lat,  file = "sstGODAS.rda")
```


# ORA-S5

```{r oras_import}
#import some of the associated data
setwd("~/CO_AUS/Aus_CO-main")

#ORAS5
##1982
#sept 1982
nc.ORAS.1982s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198209_CONS_v0.1.nc")
#oct 1982
nc.ORAS.1982o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198210_CONS_v0.1.nc")
#nov 1982
nc.ORAS.1982n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198211_CONS_v0.1.nc")

##1983
#sept 1983
nc.ORAS.1983s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198309_CONS_v0.1.nc")
#oct 1983
nc.ORAS.1983o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198310_CONS_v0.1.nc")
#nov 1983
nc.ORAS.1983n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198311_CONS_v0.1.nc")

##1984
#sept 1984
nc.ORAS.1984s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198409_CONS_v0.1.nc")
#oct 1984
nc.ORAS.1984o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198410_CONS_v0.1.nc")
#nov 1984
nc.ORAS.1984n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198411_CONS_v0.1.nc")

##1985
#sept 1985
nc.ORAS.1985s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198509_CONS_v0.1.nc")
#oct 1985
nc.ORAS.1985o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198510_CONS_v0.1.nc")
#nov 1985
nc.ORAS.1985n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198511_CONS_v0.1.nc")

##1986
#sept 1986
nc.ORAS.1986s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198609_CONS_v0.1.nc")
#oct 1986
nc.ORAS.1986o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198610_CONS_v0.1.nc")
#nov 1986
nc.ORAS.1986n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198611_CONS_v0.1.nc")

##1987
#sept 1987
nc.ORAS.1987s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198709_CONS_v0.1.nc")
#oct 1987
nc.ORAS.1987o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198710_CONS_v0.1.nc")
#nov 1987
nc.ORAS.1987n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198711_CONS_v0.1.nc")

##1988
#sept 1988
nc.ORAS.1988s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198809_CONS_v0.1.nc")
#oct 1988
nc.ORAS.1988o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198810_CONS_v0.1.nc")
#nov 1988
nc.ORAS.1988n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198811_CONS_v0.1.nc")

##1989
#sept 1989
nc.ORAS.1989s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198909_CONS_v0.1.nc")
#oct 1989
nc.ORAS.1989o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198910_CONS_v0.1.nc")
#nov 1989
nc.ORAS.1989n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_198911_CONS_v0.1.nc")

##1990
#sept 1990
nc.ORAS.1990s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199009_CONS_v0.1.nc")
#oct 1990
nc.ORAS.1990o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199010_CONS_v0.1.nc")
#nov 1990
nc.ORAS.1990n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199011_CONS_v0.1.nc")

##1991
#sept 1991
nc.ORAS.1991s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199109_CONS_v0.1.nc")
#oct 1991
nc.ORAS.1991o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199110_CONS_v0.1.nc")
#nov 1991
nc.ORAS.1991n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199111_CONS_v0.1.nc")

##1992
#sept 1992
nc.ORAS.1992s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199209_CONS_v0.1.nc")
#oct 1992
nc.ORAS.1992o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199210_CONS_v0.1.nc")
#nov 1992
nc.ORAS.1992n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199211_CONS_v0.1.nc")

##1993
#sept 1993
nc.ORAS.1993s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199309_CONS_v0.1.nc")
#oct 1993
nc.ORAS.1993o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199310_CONS_v0.1.nc")
#nov 1993
nc.ORAS.1993n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199311_CONS_v0.1.nc")

##1994
#sept 1994
nc.ORAS.1994s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199409_CONS_v0.1.nc")
#oct 1994
nc.ORAS.1994o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199410_CONS_v0.1.nc")
#nov 1994
nc.ORAS.1994n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199411_CONS_v0.1.nc")

##1995
#sept 1995
nc.ORAS.1995s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199509_CONS_v0.1.nc")
#oct 1995
nc.ORAS.1995o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199510_CONS_v0.1.nc")
#nov 1995
nc.ORAS.1995n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199511_CONS_v0.1.nc")

##1996
#sept 1996
nc.ORAS.1996s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199609_CONS_v0.1.nc")
#oct 1996
nc.ORAS.1996o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199610_CONS_v0.1.nc")
#nov 1996
nc.ORAS.1996n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199611_CONS_v0.1.nc")

##1997
#sept 1997
nc.ORAS.1997s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199709_CONS_v0.1.nc")
#oct 1997
nc.ORAS.1997o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199710_CONS_v0.1.nc")
#nov 1997
nc.ORAS.1997n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199711_CONS_v0.1.nc")

##1998
#sept 1998
nc.ORAS.1998s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199809_CONS_v0.1.nc")
#oct 1998
nc.ORAS.1998o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199810_CONS_v0.1.nc")
#nov 1998
nc.ORAS.1998n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199811_CONS_v0.1.nc")

##1999
#sept 1999
nc.ORAS.1999s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199909_CONS_v0.1.nc")
#oct 1999
nc.ORAS.1999o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199910_CONS_v0.1.nc")
#nov 1999
nc.ORAS.1999n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_199911_CONS_v0.1.nc")

##2000
#sept 2000
nc.ORAS.2000s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200009_CONS_v0.1.nc")
#oct 2000
nc.ORAS.2000o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200010_CONS_v0.1.nc")
#nov 2000
nc.ORAS.2000n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200011_CONS_v0.1.nc")

##2001
#sept 2001
nc.ORAS.2001s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200109_CONS_v0.1.nc")
#oct 2001
nc.ORAS.2001o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200110_CONS_v0.1.nc")
#nov 2001
nc.ORAS.2001n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200111_CONS_v0.1.nc")

##2002
#sept 2002
nc.ORAS.2002s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200209_CONS_v0.1.nc")
#oct 2002
nc.ORAS.2002o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200210_CONS_v0.1.nc")
#nov 2002
nc.ORAS.2002n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200211_CONS_v0.1.nc")

##2003
#sept 2003
nc.ORAS.2003s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200309_CONS_v0.1.nc")
#oct 2003
nc.ORAS.2003o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200310_CONS_v0.1.nc")
#nov 2003
nc.ORAS.2003n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200311_CONS_v0.1.nc")

##2004
#sept 2004
nc.ORAS.2004s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200409_CONS_v0.1.nc")
#oct 2004
nc.ORAS.2004o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200410_CONS_v0.1.nc")
#nov 2004
nc.ORAS.2004n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200411_CONS_v0.1.nc")

##2005
#sept 2005
nc.ORAS.2005s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200509_CONS_v0.1.nc")
#oct 2005
nc.ORAS.2005o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200510_CONS_v0.1.nc")
#nov 2005
nc.ORAS.2005n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200511_CONS_v0.1.nc")

##2006
#sept 2006
nc.ORAS.2006s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200609_CONS_v0.1.nc")
#oct 2006
nc.ORAS.2006o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200610_CONS_v0.1.nc")
#nov 2006
nc.ORAS.2006n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200611_CONS_v0.1.nc")

##2007
#sept 2007
nc.ORAS.2007s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200709_CONS_v0.1.nc")
#oct 2007
nc.ORAS.2007o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200710_CONS_v0.1.nc")
#nov 2007
nc.ORAS.2007n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200711_CONS_v0.1.nc")

##2008
#sept 2008
nc.ORAS.2008s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200809_CONS_v0.1.nc")
#oct 2008
nc.ORAS.2008o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200810_CONS_v0.1.nc")
#nov 2008
nc.ORAS.2008n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200811_CONS_v0.1.nc")

##2009
#sept 2009
nc.ORAS.2009s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200909_CONS_v0.1.nc")
#oct 2009
nc.ORAS.2009o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200910_CONS_v0.1.nc")
#nov 2009
nc.ORAS.2009n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_200911_CONS_v0.1.nc")

##2010
#sept 2010
nc.ORAS.2010s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201009_CONS_v0.1.nc")
#oct 2010
nc.ORAS.2010o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201010_CONS_v0.1.nc")
#nov 2010
nc.ORAS.2010n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201011_CONS_v0.1.nc")

##2011
#sept 2011
nc.ORAS.2011s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201109_CONS_v0.1.nc")
#oct 2011
nc.ORAS.2011o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201110_CONS_v0.1.nc")
#nov 2011
nc.ORAS.2011n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201111_CONS_v0.1.nc")

##2012
#sept 2012
nc.ORAS.2012s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201209_CONS_v0.1.nc")
#oct 2012
nc.ORAS.2012o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201210_CONS_v0.1.nc")
#nov 2012
nc.ORAS.2012n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201211_CONS_v0.1.nc")

##2013
#sept 2013
nc.ORAS.2013s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201309_CONS_v0.1.nc")
#oct 2013
nc.ORAS.2013o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201310_CONS_v0.1.nc")
#nov 2013
nc.ORAS.2013n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201311_CONS_v0.1.nc")

##2014
#sept 2014
nc.ORAS.2014s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201409_CONS_v0.1.nc")
#oct 2014
nc.ORAS.2014o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201410_CONS_v0.1.nc")
#nov 2014
nc.ORAS.2014n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201411_CONS_v0.1.nc")

##2015
#sept 2015
nc.ORAS.2015s <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201509_OPER_v0.1.nc")
#oct 2015
nc.ORAS.2015o <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201510_OPER_v0.1.nc")
#nov 2015
nc.ORAS.2015n <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/ORAS5/sosstsst_control_monthly_highres_2D_201511_OPER_v0.1.nc")

#TODO: add in years 2016-2019

```

## ORA-S5 Functions

```{r oras_functions}
array_setup <- function(nc.data, wide.lon, wide.lat){

  #lon/lat matrices [nx, ny] ([lon, lat])
  get.lat <- ncvar_get(nc.data, "nav_lat")
  get.lon <- ncvar_get(nc.data, "nav_lon")
  
  #get sst data
  sst.oras <- ncvar_get(nc.data, "sosstsst")
  
  iod.mask <- get.lat >= wide.lat[1] & get.lat <= wide.lat[2] &
          get.lon >= wide.lon[1] & get.lon <= wide.lon[2]
  
  lat.in <- get.lat[iod.mask]
  lon.in <- get.lon[iod.mask]
  sst.oras.in <- sst.oras[iod.mask]
  
  return(list(lon = lon.in,
              lat = lat.in,
              sst = sst.oras.in))
}


reformat_interpolate <- function(lon.in, lat.in, sst.oras.in, 
                                 grid.list){
  #TODO: adjust raw numbers if needed
  #reformat 
  n <- length(lon.in) /363
  
  seq.list <- split(1:59169, ceiling(seq_along(1:59169) / 363))
  
  #take chunk of 363 reorder, and remove duplicate data manually
  new.order <- c(191:363, 3:190)
  
  #TODO: setup additional matrix just for the sst data
  sst.mat <- matrix(NA, ncol = 3)
  colnames(sst.mat) < c("lon", "lat", "sst")
  for (i in 1:n) {
    lon.temp <- lon.in[seq.list[[i]]]
    lat.temp <- lat.in[seq.list[[i]]]
    sst.temp <- sst.oras.in[seq.list[[i]]]
    
    #temporary matrix setup
    temp.mat <- cbind(lon = lon.temp[new.order], 
                      lat = lat.temp[new.order], 
                      sst = sst.temp[new.order])
    
    sst.mat <- rbind(sst.mat, temp.mat)
  }
  
  sst.df <- as.data.frame(sst.mat[-1,])
  
  get.x <- unique(sst.df$lon)
  get.y <- unique(sst.df$lat)
  
  sst.oras.matrix <- matrix(sst.df$sst, nrow = 361)
  
  #interpolate

  obj.oras <- list(x = get.x, y = get.y, z = sst.oras.matrix)
  
  out.interp <- interp.surface.grid(obj.oras, grid.list) #not currently working (duplicated data)

  return(out.interp$z)
}



reformat_oras <- function(lon.in, lat.in, sst.oras.in){
  
  #TODO: adjust raw numbers if needed
  #reformat 
  n <- length(lon.in) /363
  
  seq.list <- split(1:59169, ceiling(seq_along(1:59169) / 363))
  
  #take chunk of 363 reorder, and remove duplicate data manually
  new.order <- c(191:363, 3:190)
  
  #TODO: setup additional matrix just for the sst data
  sst.mat <- matrix(NA, ncol = 3)
  colnames(sst.mat) < c("lon", "lat", "sst")
  for (i in 1:n) {
    lon.temp <- lon.in[seq.list[[i]]]
    lat.temp <- lat.in[seq.list[[i]]]
    sst.temp <- sst.oras.in[seq.list[[i]]]
    
    #temporary matrix setup
    temp.mat <- cbind(lon = lon.temp[new.order], 
                      lat = lat.temp[new.order], 
                      sst = sst.temp[new.order])
    
    sst.mat <- rbind(sst.mat, temp.mat)
  }
  
  sst.df <- as.data.frame(sst.mat[-1,])
  
  sst.oras.matrix <- matrix(sst.df$sst, nrow = 361)
  
  get.x <- unique(sst.df$lon)
  get.y <- unique(sst.df$lat)
  

  return(list(lon = get.x,
              lat = get.y, 
              sst = sst.oras.matrix))
}

```

## ORA-S5 Data Setup

```{r data_clean}

#wide, reduced boundary (Indian Ocean) setup
wide.lon <- c(wide_minLon, wide_maxLon)
wide.lat <- c(wide_minLat, wide_maxLat)

oras_list <- list(nc.ORAS.1982s, nc.ORAS.1982o, nc.ORAS.1982n,
                  nc.ORAS.1983s, nc.ORAS.1983o, nc.ORAS.1983n,
                  nc.ORAS.1984s, nc.ORAS.1984o, nc.ORAS.1984n,
                  nc.ORAS.1985s, nc.ORAS.1985o, nc.ORAS.1985n,
                  nc.ORAS.1986s, nc.ORAS.1986o, nc.ORAS.1986n,
                  nc.ORAS.1987s, nc.ORAS.1987o, nc.ORAS.1987n,
                  nc.ORAS.1988s, nc.ORAS.1988o, nc.ORAS.1988n,
                  nc.ORAS.1989s, nc.ORAS.1989o, nc.ORAS.1989n,
                  nc.ORAS.1990s, nc.ORAS.1990o, nc.ORAS.1990n,
                  nc.ORAS.1991s, nc.ORAS.1991o, nc.ORAS.1991n,
                  nc.ORAS.1992s, nc.ORAS.1992o, nc.ORAS.1992n,
                  nc.ORAS.1993s, nc.ORAS.1993o, nc.ORAS.1993n,
                  nc.ORAS.1994s, nc.ORAS.1994o, nc.ORAS.1994n,
                  nc.ORAS.1995s, nc.ORAS.1995o, nc.ORAS.1995n,
                  nc.ORAS.1996s, nc.ORAS.1996o, nc.ORAS.1996n,
                  nc.ORAS.1997s, nc.ORAS.1997o, nc.ORAS.1997n,
                  nc.ORAS.1998s, nc.ORAS.1998o, nc.ORAS.1998n,
                  nc.ORAS.1999s, nc.ORAS.1999o, nc.ORAS.1999n,
                  nc.ORAS.2000s, nc.ORAS.2000o, nc.ORAS.2000n,
                  nc.ORAS.2001s, nc.ORAS.2001o, nc.ORAS.2001n,
                  nc.ORAS.2002s, nc.ORAS.2002o, nc.ORAS.2002n,
                  nc.ORAS.2003s, nc.ORAS.2003o, nc.ORAS.2003n,
                  nc.ORAS.2004s, nc.ORAS.2004o, nc.ORAS.2004n,
                  nc.ORAS.2005s, nc.ORAS.2005o, nc.ORAS.2005n,
                  nc.ORAS.2006s, nc.ORAS.2006o, nc.ORAS.2006n,
                  nc.ORAS.2007s, nc.ORAS.2007o, nc.ORAS.2007n,
                  nc.ORAS.2008s, nc.ORAS.2008o, nc.ORAS.2008n,
                  nc.ORAS.2009s, nc.ORAS.2009o, nc.ORAS.2009n,
                  nc.ORAS.2010s, nc.ORAS.2010o, nc.ORAS.2010n,
                  nc.ORAS.2011s, nc.ORAS.2011o, nc.ORAS.2011n,
                  nc.ORAS.2012s, nc.ORAS.2012o, nc.ORAS.2012n,
                  nc.ORAS.2013s, nc.ORAS.2013o, nc.ORAS.2013n,
                  nc.ORAS.2014s, nc.ORAS.2014o, nc.ORAS.2014n,
                  nc.ORAS.2015s, nc.ORAS.2015o, nc.ORAS.2015n)
                  
#sst array setup
sst.ORAS.new <- NULL
for (j in 1:length(oras_list)) {
  temp.nc <- oras_list[[j]]
  
  out.temp <- array_setup(temp.nc, wide.lon, wide.lat)
  
  temp.sst <- reformat_interpolate(out.temp$lon, out.temp$lat, 
                     out.temp$sst, grid.list)
  
  
  sst.ORAS.new <- abind(sst.ORAS.new, temp.sst, along = 3)
}



rm(nc.ORAS.1982s, nc.ORAS.1982o, nc.ORAS.1982n,
    nc.ORAS.1983s, nc.ORAS.1983o, nc.ORAS.1983n,
    nc.ORAS.1984s, nc.ORAS.1984o, nc.ORAS.1984n,
    nc.ORAS.1985s, nc.ORAS.1985o, nc.ORAS.1985n,
    nc.ORAS.1986s, nc.ORAS.1986o, nc.ORAS.1986n,
    nc.ORAS.1987s, nc.ORAS.1987o, nc.ORAS.1987n,
    nc.ORAS.1988s, nc.ORAS.1988o, nc.ORAS.1988n,
    nc.ORAS.1989s, nc.ORAS.1989o, nc.ORAS.1989n,
    nc.ORAS.1990s, nc.ORAS.1990o, nc.ORAS.1990n,
    nc.ORAS.1991s, nc.ORAS.1991o, nc.ORAS.1991n,
    nc.ORAS.1992s, nc.ORAS.1992o, nc.ORAS.1992n,
    nc.ORAS.1993s, nc.ORAS.1993o, nc.ORAS.1993n,
    nc.ORAS.1994s, nc.ORAS.1994o, nc.ORAS.1994n,
    nc.ORAS.1995s, nc.ORAS.1995o, nc.ORAS.1995n,
    nc.ORAS.1996s, nc.ORAS.1996o, nc.ORAS.1996n,
    nc.ORAS.1997s, nc.ORAS.1997o, nc.ORAS.1997n,
    nc.ORAS.1998s, nc.ORAS.1998o, nc.ORAS.1998n,
    nc.ORAS.1999s, nc.ORAS.1999o, nc.ORAS.1999n,
    nc.ORAS.2000s, nc.ORAS.2000o, nc.ORAS.2000n,
    nc.ORAS.2001s, nc.ORAS.2001o, nc.ORAS.2001n,
    nc.ORAS.2002s, nc.ORAS.2002o, nc.ORAS.2002n,
    nc.ORAS.2003s, nc.ORAS.2003o, nc.ORAS.2003n,
    nc.ORAS.2004s, nc.ORAS.2004o, nc.ORAS.2004n,
    nc.ORAS.2005s, nc.ORAS.2005o, nc.ORAS.2005n,
    nc.ORAS.2006s, nc.ORAS.2006o, nc.ORAS.2006n,
    nc.ORAS.2007s, nc.ORAS.2007o, nc.ORAS.2007n,
    nc.ORAS.2008s, nc.ORAS.2008o, nc.ORAS.2008n,
    nc.ORAS.2009s, nc.ORAS.2009o, nc.ORAS.2009n,
    nc.ORAS.2010s, nc.ORAS.2010o, nc.ORAS.2010n,
    nc.ORAS.2011s, nc.ORAS.2011o, nc.ORAS.2011n,
    nc.ORAS.2012s, nc.ORAS.2012o, nc.ORAS.2012n,
    nc.ORAS.2013s, nc.ORAS.2013o, nc.ORAS.2013n,
    nc.ORAS.2014s, nc.ORAS.2014o, nc.ORAS.2014n,
    nc.ORAS.2015s, nc.ORAS.2015o, nc.ORAS.2015n)

dim(sst.ORAS.new) #[lon, lat, son_months]



```

### ORA-S5 w/o Interpolation
 
```{r raw_oras}

#wide, reduced boundary (Indian Ocean) setup
wide.lon <- c(wide_minLon, wide_maxLon)
wide.lat <- c(wide_minLat, wide_maxLat)



oras_list <- list(nc.ORAS.1982s, nc.ORAS.1982o, nc.ORAS.1982n,
                  nc.ORAS.1983s, nc.ORAS.1983o, nc.ORAS.1983n,
                  nc.ORAS.1984s, nc.ORAS.1984o, nc.ORAS.1984n,
                  nc.ORAS.1985s, nc.ORAS.1985o, nc.ORAS.1985n,
                  nc.ORAS.1986s, nc.ORAS.1986o, nc.ORAS.1986n,
                  nc.ORAS.1987s, nc.ORAS.1987o, nc.ORAS.1987n,
                  nc.ORAS.1988s, nc.ORAS.1988o, nc.ORAS.1988n,
                  nc.ORAS.1989s, nc.ORAS.1989o, nc.ORAS.1989n,
                  nc.ORAS.1990s, nc.ORAS.1990o, nc.ORAS.1990n,
                  nc.ORAS.1991s, nc.ORAS.1991o, nc.ORAS.1991n,
                  nc.ORAS.1992s, nc.ORAS.1992o, nc.ORAS.1992n,
                  nc.ORAS.1993s, nc.ORAS.1993o, nc.ORAS.1993n,
                  nc.ORAS.1994s, nc.ORAS.1994o, nc.ORAS.1994n,
                  nc.ORAS.1995s, nc.ORAS.1995o, nc.ORAS.1995n,
                  nc.ORAS.1996s, nc.ORAS.1996o, nc.ORAS.1996n,
                  nc.ORAS.1997s, nc.ORAS.1997o, nc.ORAS.1997n,
                  nc.ORAS.1998s, nc.ORAS.1998o, nc.ORAS.1998n,
                  nc.ORAS.1999s, nc.ORAS.1999o, nc.ORAS.1999n,
                  nc.ORAS.2000s, nc.ORAS.2000o, nc.ORAS.2000n,
                  nc.ORAS.2001s, nc.ORAS.2001o, nc.ORAS.2001n,
                  nc.ORAS.2002s, nc.ORAS.2002o, nc.ORAS.2002n,
                  nc.ORAS.2003s, nc.ORAS.2003o, nc.ORAS.2003n,
                  nc.ORAS.2004s, nc.ORAS.2004o, nc.ORAS.2004n,
                  nc.ORAS.2005s, nc.ORAS.2005o, nc.ORAS.2005n,
                  nc.ORAS.2006s, nc.ORAS.2006o, nc.ORAS.2006n,
                  nc.ORAS.2007s, nc.ORAS.2007o, nc.ORAS.2007n,
                  nc.ORAS.2008s, nc.ORAS.2008o, nc.ORAS.2008n,
                  nc.ORAS.2009s, nc.ORAS.2009o, nc.ORAS.2009n,
                  nc.ORAS.2010s, nc.ORAS.2010o, nc.ORAS.2010n,
                  nc.ORAS.2011s, nc.ORAS.2011o, nc.ORAS.2011n,
                  nc.ORAS.2012s, nc.ORAS.2012o, nc.ORAS.2012n,
                  nc.ORAS.2013s, nc.ORAS.2013o, nc.ORAS.2013n,
                  nc.ORAS.2014s, nc.ORAS.2014o, nc.ORAS.2014n,
                  nc.ORAS.2015s, nc.ORAS.2015o, nc.ORAS.2015n)

#sst array setup
sst.ORAS.new2 <- NULL
#TODO: get lon, lat (unique) output:

for (j in 1:length(oras_list)) {
  temp.nc <- oras_list[[j]]
  
  out.temp <- array_setup(temp.nc, wide.lon, wide.lat)
  
  temp.sst <- reformat_oras(out.temp$lon, out.temp$lat, 
                     out.temp$sst)
  
  oras.lon <- temp.sst$lon
  oras.lat <- temp.sst$lat
  
  sst.ORAS.new2 <- abind(sst.ORAS.new2, temp.sst$sst, along = 3)
}



rm(nc.ORAS.1982s, nc.ORAS.1982o, nc.ORAS.1982n,
    nc.ORAS.1983s, nc.ORAS.1983o, nc.ORAS.1983n,
    nc.ORAS.1984s, nc.ORAS.1984o, nc.ORAS.1984n,
    nc.ORAS.1985s, nc.ORAS.1985o, nc.ORAS.1985n,
    nc.ORAS.1986s, nc.ORAS.1986o, nc.ORAS.1986n,
    nc.ORAS.1987s, nc.ORAS.1987o, nc.ORAS.1987n,
    nc.ORAS.1988s, nc.ORAS.1988o, nc.ORAS.1988n,
    nc.ORAS.1989s, nc.ORAS.1989o, nc.ORAS.1989n,
    nc.ORAS.1990s, nc.ORAS.1990o, nc.ORAS.1990n,
    nc.ORAS.1991s, nc.ORAS.1991o, nc.ORAS.1991n,
    nc.ORAS.1992s, nc.ORAS.1992o, nc.ORAS.1992n,
    nc.ORAS.1993s, nc.ORAS.1993o, nc.ORAS.1993n,
    nc.ORAS.1994s, nc.ORAS.1994o, nc.ORAS.1994n,
    nc.ORAS.1995s, nc.ORAS.1995o, nc.ORAS.1995n,
    nc.ORAS.1996s, nc.ORAS.1996o, nc.ORAS.1996n,
    nc.ORAS.1997s, nc.ORAS.1997o, nc.ORAS.1997n,
    nc.ORAS.1998s, nc.ORAS.1998o, nc.ORAS.1998n,
    nc.ORAS.1999s, nc.ORAS.1999o, nc.ORAS.1999n,
    nc.ORAS.2000s, nc.ORAS.2000o, nc.ORAS.2000n,
    nc.ORAS.2001s, nc.ORAS.2001o, nc.ORAS.2001n,
    nc.ORAS.2002s, nc.ORAS.2002o, nc.ORAS.2002n,
    nc.ORAS.2003s, nc.ORAS.2003o, nc.ORAS.2003n,
    nc.ORAS.2004s, nc.ORAS.2004o, nc.ORAS.2004n,
    nc.ORAS.2005s, nc.ORAS.2005o, nc.ORAS.2005n,
    nc.ORAS.2006s, nc.ORAS.2006o, nc.ORAS.2006n,
    nc.ORAS.2007s, nc.ORAS.2007o, nc.ORAS.2007n,
    nc.ORAS.2008s, nc.ORAS.2008o, nc.ORAS.2008n,
    nc.ORAS.2009s, nc.ORAS.2009o, nc.ORAS.2009n,
    nc.ORAS.2010s, nc.ORAS.2010o, nc.ORAS.2010n,
    nc.ORAS.2011s, nc.ORAS.2011o, nc.ORAS.2011n,
    nc.ORAS.2012s, nc.ORAS.2012o, nc.ORAS.2012n,
    nc.ORAS.2013s, nc.ORAS.2013o, nc.ORAS.2013n,
    nc.ORAS.2014s, nc.ORAS.2014o, nc.ORAS.2014n,
    nc.ORAS.2015s, nc.ORAS.2015o, nc.ORAS.2015n)

dim(sst.ORAS.new2) #[lon, lat, son_months]
```


```{r save_oras}
setwd("~/CO_AUS/Aus_CO-main/pIOD")
save(sst.ORAS.new, sst.ORAS.new2, oras.lon, oras.lat, file = "sstORAS.rda")
```


## Get ORA-S5 Land-Sea Mask
(Note: this mask looks very close to those presented in the paper)

```{r oras_lsm}

temp.lsm <- is.na(sst.ORAS.new[,,1])

```


# OISST v2

('default' data product: use as a template for other products )

```{r load_data}
setwd("~/CO_AUS/Aus_CO-main")

#begin easy with monthly OISST
nc.OISST.month <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/sst.mnmean.nc")

#OISST land sea mask
nc.OISST.lsm <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/lsmask.nc")
```


## OISST Data Setup

```{r data_cleaning}
#extract lon, lat
lat.grid <- nc.OISST.month[["dim"]][["lat"]][["vals"]]
lon.grid <- nc.OISST.month[["dim"]][["lon"]][["vals"]]

#reorder lon
lon.grid[lon.grid >= 180] <- lon.grid[lon.grid >= 180] - 360
lon.order <- order(lon.grid)

lon.grid <- lon.grid[lon.order]

#reorder lat (maybe?)
lat.order <- order(lat.grid)
lat.grid <- lat.grid[lat.order]

#time data
times <- ncvar_get(nc.OISST.month, "time") # days since 1800-01-01 00:00:0.0
times <- as_datetime("1800-01-01T00:00:00") + days(times)

#sst data, as array (lon, lat, time)
sst.oisst <- ncvar_get(nc.OISST.month, "sst")
sst.oisst <- sst.oisst[lon.order, lat.order, ]

#TODO: get wider Indian Ocean domain so we can interpolate onto the correct one.
#get reduced indian ocean region
lat.range <- range(which(lat.grid <= (wide_maxLat+1) & lat.grid >= (wide_minLat-1)))
lon.range <- range(which(lon.grid <= (wide_maxLon+1) & lon.grid >= (wide_minLon-1)))

lat.values.oisst <- lat.grid[lat.grid <= (wide_maxLat+1) & lat.grid >=  (wide_minLat-1)]
lon.values.oisst <- lon.grid[lon.grid <= (wide_maxLon+1) & lon.grid >= (wide_minLon-1)]

lat.range.base <- range(which(lat.grid <= (wide_maxLat) & lat.grid >= (wide_minLat)))
lon.range.base <- range(which(lon.grid <= (wide_maxLon) & lon.grid >= (wide_minLon)))

lat.values.base <- lat.grid[lat.grid <= (wide_maxLat) & lat.grid >=  (wide_minLat)]
lon.values.base <- lon.grid[lon.grid <= (wide_maxLon) & lon.grid >= (wide_minLon)]



#get OISST SST reduced matrix
sst.OISST.wide <- sst.oisst[lon.range[1]:lon.range[2], lat.range[1]:lat.range[2], 2:409]

dim(sst.OISST.wide)

sst.OISST.base <- sst.oisst[lon.range.base[1]:lon.range.base[2], lat.range.base[1]:lat.range.base[2], 2:409]

dim(sst.OISST.base)


#interpolate onto 1.0 x 1.0 grid
sst.OISST.new <- NULL
for (j in 1:dim(sst.OISST.wide)[3]) {
  base.obj <- list(x = lon.values.oisst, y = lat.values.oisst, z = sst.OISST.wide[,,j])

  
  out.interp <- interp.surface.grid(base.obj, grid.list)
  
  #interp.mat <- out.interp$z[ ,ncol(out.interp$z):1 ]
  
  sst.OISST.new <- abind(sst.OISST.new, out.interp$z, along = 3)
}

dim(sst.OISST.new)

#mask land
sst.OISST.new <- apply(sst.OISST.new, 3, function(X) {
  X[temp.lsm] <- NA
  return(X)
})

dim(sst.OISST.new) <- c(91, 41, 408)


```


```{r alt_lsm}
#lsm for sst.OISST.base 

##Land Sea Mask
#extract lon, lat
lat.grid.lsm <- nc.OISST.lsm[["dim"]][["lat"]][["vals"]]
lon.grid.lsm <- nc.OISST.lsm[["dim"]][["lon"]][["vals"]]

#reorder lon for 
lon.grid.lsm[lon.grid.lsm >= 180] <- lon.grid.lsm[lon.grid.lsm >= 180] - 360
this.order.lsm <- order(lon.grid.lsm)

lon.grid.lsm <- lon.grid.lsm[this.order.lsm]


#setup (or find) a land sea mask.
lsm <- ncvar_get(nc.OISST.lsm, "mask")
lsm <- lsm[this.order.lsm, ]

#TODO update lsm for reduced region
#get lsm for IOD only
lsm_IOD <- lsm[lon.range.base[1]:lon.range.base[2], lat.range.base[1]:lat.range.base[2]] 

lsm.IOD <- lsm_IOD[ ,ncol(lsm_IOD):1]

#setup (land sea mask for OISST data)
lsm.IOD.array <- array(lsm.IOD, dim = dim(sst.OISST.base))

sst.OISST.new2 <- ifelse(lsm.IOD.array == 1, sst.OISST.base, NA)

dim(sst.OISST.new2)

```


```{r save_oisst}

setwd("~/CO_AUS/Aus_CO-main/pIOD")
save(sst.OISST.new, sst.OISST.new2, lat.values.base, lon.values.base, file = "sstOISST.rda")
```


# SODA3.3.1

```{r load_data}
setwd("~/CO_AUS/Aus_CO-main")

##SODA3.3.1
#all monthly data in a single file
nc.SODA.month <- nc_open("~/CO_AUS/Aus_CO-main/pIOD/Data/erdSoda331oceanmday_6a77_2294_0698.nc")

```

## SODA Data Setup

```{r data_cleaning}
#and interpolation

#for monthly
lat.grid.soda <- nc.SODA.month[["dim"]][["latitude"]][["vals"]]
lon.grid.soda <- nc.SODA.month[["dim"]][["longitude"]][["vals"]]

#adjust lon order
lon.grid.soda[lon.grid.soda >= 180] <- lon.grid.soda[lon.grid.soda >= 180] - 360
lon.order.soda <- order(lon.grid.soda)

lon.grid.soda <- lon.grid.soda[lon.order.soda]

#adjust lat order
#TODO: double check this, it might be wrong
#lat.order.soda <- order(lat.grid.soda, decreasing = TRUE)
#lat.grid.soda <- lat.grid.soda[lat.order.soda]

#get times
times.soda <- ncvar_get(nc.SODA.month, "time") #seconds since 1970-01-01T00:00:00Z
times.soda <- as_datetime("1970-01-01T00:00:00") + seconds(times.soda)
  
  
sst.soda <- ncvar_get(nc.SODA.month, "temp")
sst.soda <- sst.soda[lon.order.soda, , ]


#TODO: get bounded data for wider data
#SODA range
lat.values.soda <- lat.grid.soda[lat.grid.soda <= wide_maxLat & lat.grid.soda >= wide_minLat]
lat.range.soda <- range(which(lat.grid.soda <= wide_maxLat & lat.grid.soda >= wide_minLat))

lon.values.soda <- lon.grid.soda[lon.grid.soda <= wide_maxLon & lon.grid.soda >= wide_minLon]
lon.range.soda <- range(which(lon.grid.soda <= wide_maxLon & lon.grid.soda >= wide_minLon))

times.soda[25]
times.soda[432]

#get SODA SST reduced matrix 
sst_soda <- sst.soda[lon.range.soda[1]:lon.range.soda[2], lat.range.soda[1]:lat.range.soda[2], ]
sst.SODA.new2 <- sst_soda[,, 25:432]

dim(sst.SODA.new2) #[nx, ny, nt]

#interpolate onto 1.0 x 1.0 grid
sst.SODA.new <- NULL
for (j in 1:dim(sst.SODA.new2)[3]) {
  base.obj <- list(x = lon.values.soda, y = lat.values.soda, z = sst.SODA.new2[,,j])

  
  out.interp <- interp.surface.grid(base.obj, grid.list)
  
  #interp.mat <- out.interp$z[ ,ncol(out.interp$z):1 ]
  
  sst.SODA.new <- abind(sst.SODA.new, out.interp$z, along = 3)
}

dim(sst.SODA.new)


```


```{r save_soda}

setwd("~/CO_AUS/Aus_CO-main/pIOD")

save(sst.SODA.new, sst.SODA.new2, lon.values.soda, lat.values.soda, file = "sstSODA.rda")
```


# SST Anomalies

(produce sst anomalies here)

## Anomaly Functions

```{r functions}

#son average (seasonal mean for each year)
son.avg <- function(sst, son.only = FALSE){
  ##sst as [lon, lat, time]
  A.new <- aperm(sst, perm = c(3, 2, 1))  # reorder data as [time, lat, lon]
  
  #get dimensions from reordered array
  nx <- dim(A.new)[3]
  ny <- dim(A.new)[2] 
  nt <- dim(A.new)[1]
  
  #get SON mean (get 1 sst per year (as son mean))
  if (son.only) {
    #if only provided with 3 months (son) per year
    nyears <- nt %/% 3
    A.temp <- array(A.new, dim = c(3, nyears, ny, nx))
    A.son <- apply(A.temp[1:3, , , ], c(2,3,4), mean, na.rm = TRUE) #already at correct subset
  }else {
    nyears <- nt %/% 12
    #reshape data array
    A.temp <- array(A.new, dim = c(12, nyears, ny, nx))
    A.son <- apply(A.temp[9:11, , , ], c(2,3,4), mean, na.rm = TRUE) #already at correct subset
  }
  
  return(aperm(A.son, perm = c(3, 2, 1))) #return as [lon, lat, time]
}

##son anomalies
#1. compute SON (seasonal) climatology
#2. seasonal means minus seasonal climatology
son.anom <- function(sst){

  climate.mean <- apply(sst, c(1, 2), mean, na.rm = FALSE)
  son.anom <- sweep(sst, MARGIN = c(1, 2), STATS = climate.mean, FUN = "-")

  return(son.anom)
}


##detrend son anomalies
son.detrend <- function(anom, order = 1){
  #get dimensions
  nx <- dim(anom)[1]
  ny <- dim(anom)[2]
  nt <- dim(anom)[3]
  
  t <- 1:nt
  sst.resid <- anom
  #double for-loop (not efficient, but oh well)
  for (i in 1:nx) {
    for (j in 1:ny) {
      x <- anom[i,j,]
      if (all(!is.na(x))){ 
        fit.lm <- switch(order,
                         '1' = lm(x ~ t),
                         '2' = lm(x ~ t + I(t^2)))
    
      }
      
      }
    sst.resid[i,j,] <- fit.lm$residuals
  }
  return(sst.resid)
}

```


## SON (Seasonal) Anomalies

```{r son_anoms}
#son avg
sst.GODAS.son <- son.avg(sst.GODAS.new)
sst.ORAS.son <- son.avg(sst.ORAS.new, son.only = TRUE)
sst.OISST.son <- son.avg(sst.OISST.new)
sst.SODA.son <- son.avg(sst.SODA.new)

#get son anomalies
sst.GODAS.anom <- son.anom(sst.GODAS.son)
sst.ORAS.anom <- son.anom(sst.ORAS.son)
sst.OISST.anom <- son.anom(sst.OISST.son)
sst.SODA.anom <- son.anom(sst.SODA.son)

#get detrended data
sst.GODAS.anom2 <- son.detrend(sst.GODAS.anom)
sst.ORAS.anom2 <- son.detrend(sst.ORAS.anom)
sst.OISST.anom2 <- son.detrend(sst.OISST.anom)
sst.SODA.anom2 <- son.detrend(sst.SODA.anom)

#dimension check
dim(sst.GODAS.anom2)
dim(sst.ORAS.anom2)
dim(sst.OISST.anom2)
dim(sst.SODA.anom2)

setwd("~/CO_AUS/Aus_CO-main/pIOD")
save(sst.GODAS.anom2, sst.ORAS.anom2,
    sst.OISST.anom2, sst.SODA.anom2, 
    lon.wide, lat.wide, file = "sstAnoms.rda")

```


## SON Multi-Product Averages

```{r}
#temp location for multi prod averages.


```

## Alternative SST Anoms

```{r alt_function}
sst.anoms <- function(A, son.only = FALSE, quadratic = FALSE){
    
  A.new <- aperm(A, perm = c(3, 2, 1))  # reorder data as [time, lat, lon]
  
  #get dimensions from reordered array
  nx <- dim(A.new)[3]
  ny <- dim(A.new)[2] 
  nt <- dim(A.new)[1]
  
  #get SON mean (get 1 sst per year (as son mean))
  if (son.only) {
    #if only provided with 3 months (son) per year
    nyears <- nt %/% 3
    A.temp <- array(A.new, dim = c(3, nyears, ny, nx))
    A.son <- apply(A.temp[1:3, , , ], c(2,3,4), mean, na.rm = TRUE) #already at correct subset
  }else {
    nyears <- nt %/% 12
    #reshape data array
    A.temp <- array(A.new, dim = c(12, nyears, ny, nx))
    A.son <- apply(A.temp[9:11, , , ], c(2,3,4), mean, na.rm = TRUE) #already at correct subset
  }
  
  rm(A.temp)
  
  #update time dim
  nt <- dim(A.son)[1]
  
  #remove mean
  var <- matrix(A.son, nrow = nt, ncol = ny * nx) #from earlier work on detrend
  
  #get full period mean
  var.mean <- colMeans(var) #TODO: visualize this spatially (transform to [lon, lat])
  var <- sweep(var, 2, colMeans(var), "-") #TODO: check how this might hold up with irregular spatial masks
  
  #de-trend
  #TODO: figure out how to work with irregular NAs in time/space (some years have different spatial NAs)
  test.na <- which(!is.na(var), arr.ind = TRUE) 
  true.index <- unique(test.na[,2])
  
  A.resid <- matrix(NA, nrow = nt, ncol = ny*nx)
  A.coef <- matrix(NA, nrow = 2, ncol = ny*nx)
  
  var.x <- seq_len(nt) #time "covariates"
  var.y <- var[ ,true.index] #response variable (sst anoms)
  
  
  if (quadratic) {
    var.fit <- lm(var.y ~ var.x + I(var.x^2))
    A.coef[,true.index] <- var.fit$coefficients[1:2, ] #only works for first two coeffs
  } else {
    var.fit <- lm(var.y ~ var.x)
    A.coef[,true.index] <- var.fit$coefficients
  }
  
  A.resid[,true.index] <- var.fit$residuals
  
  #TODO: update this handle quadratic fit
  #A.coef[,true.index] <- var.fit$coefficients
  
  return(list(mean = var.mean,
              anom = A.resid,
              coef = A.coef))
}
```


```{r}
#sst anomalies SON, for 
##OISST
sst.anom.oisst <- sst.anoms(sst.OISST.new, quadratic = FALSE)
#GODAS
sst.anom.godas <- sst.anoms(sst.GODAS.new, quadratic = FALSE)
#SODA
sst.anom.soda <- sst.anoms(sst.SODA.new, quadratic = FALSE)
#ORA-S5
sst.anom.oras <- sst.anoms(sst.ORAS.new, son.only = TRUE, quadratic = FALSE)

#get 'full' son avg for all 4 data product sst anoms
sst.full.avg <- (sst.anom.oisst$anom + sst.anom.godas$anom + 
                   sst.anom.soda$anom + sst.anom.oras$anom)/4

```


# Figures

## SST anomalies

```{r 1994_fig}
##SST anomalies (detrended)
nt <- 34
ny <- 41
nx <- 91
temp <- array(sst.full.avg, dim = c(nt, ny, nx))  # from [nt, ny*nx] to [nt, ny, nx]
spat.resid <- aperm(temp, c(3, 2, 1))  # from [nt, ny, nx] to [nx, ny, nt]


#1994 SON anom detrended
k <- 13
resid.absmax <- max(abs(spat.resid[,,k]), na.rm = TRUE)
resid.range <- c(-resid.absmax, resid.absmax) 
#default breaks
cols.ryb <- rev(colorRampPalette(brewer.pal(11, "RdYlBu"))(12))
cols_alpha <- adjustcolor(cols.ryb, alpha.f = 0.25)
breaks.dumb <- c(resid.range[1], seq(-1,1, 0.2), resid.range[2])
leg.brks2 <- seq(-1.2, 1.2, 0.2) 


png(filename = "sst1994anom_overlay.png", width = 2400, height = 1600, bg = "transparent", type = "cairo")
par(mar = c(7, 5, 2, 5), mgp = c(2.25, 1, 0))
image(list(x = lon.wide, y = lat.wide, z = spat.resid[,,k]), 
           col = cols_alpha, breaks = breaks.dumb, zlim = resid.range, 
           xlab = "Lon", ylab = "Lat",
           axes = FALSE)
axis(1, at = c(60, 90, 120))  
axis(2)                      
box()
rect(pIOD_minLon ,pIOD_minLat , pIOD_maxLon , pIOD_maxLat, lty = 2, lwd = 5 )
world(add=TRUE, lwd = 6)
contour(x = lon.wide, y = lat.wide, z = spat.resid[,,k], add = TRUE, 
        levels = breaks.dumb, drawlabels = FALSE, lwd = 4)
dev.off()

```

```{r 1997_fig}

#1997 SON anom detrended
k <- 16
resid.absmax <- max(abs(spat.resid[,,k]), na.rm = TRUE)
resid.range <- c(-resid.absmax, resid.absmax) 
#default breaks
cols.ryb <- rev(colorRampPalette(brewer.pal(11, "RdYlBu"))(12))
cols_alpha <- adjustcolor(cols.ryb, alpha.f = 0.15)

breaks.dumb <- c(resid.range[1], seq(-1,1, 0.2), resid.range[2])
leg.brks2 <- seq(-1.2, 1.2, 0.2) 

png(filename = "sst1997anom_overlay.png", width = 2400, height = 1600, bg = "transparent", type = "cairo")
par(mar = c(7, 5, 2, 5), mgp = c(2.25, 1, 0))
image(list(x = lon.wide, y = lat.wide, z = spat.resid[,,k]), 
           col = cols_alpha, breaks = breaks.dumb, zlim = resid.range, 
           xlab = "Lon", ylab = "Lat",
           axes = FALSE)
axis(1, at = c(60, 90, 120))  
axis(2)                      
box()
rect(pIOD_minLon ,pIOD_minLat , pIOD_maxLon , pIOD_maxLat, lty = 2, lwd = 5 )
world(add=TRUE, lwd = 6)
contour(x = lon.wide, y = lat.wide, z = spat.resid[,,k], add = TRUE, 
        levels = breaks.dumb, drawlabels = FALSE, lwd = 4)
dev.off()

png(filename = "sst1997anom_new.png", width = 2400, height = 1600, res = 250)
par(mar = c(7, 5, 2, 5), mgp = c(2.25, 1, 0))
image(list(x = lon.wide, y = lat.wide, z = spat.resid[,,k]), 
           col = cols.ryb, breaks = breaks.dumb, zlim = resid.range, 
           xlab = "Lon", ylab = "Lat",
           axes = FALSE)
axis(1, at = c(60, 90, 120))  
axis(2)                      
box()
rect(pIOD_minLon ,pIOD_minLat , pIOD_maxLon , pIOD_maxLat, lty = 2, lwd = 2 )
world(add=TRUE, lwd = 2)
contour(x = lon.wide, y = lat.wide, z = spat.resid[,,k], add = TRUE, 
        levels = breaks.dumb, drawlabels = FALSE, lwd = 1)
dev.off()

```


### SST Anomalies (w/o Interpolation)

```{r test_section}
#sst.GODAS.new2
son.GODAS.sst <- son.avg(sst.GODAS.new2)

#sst.ORAS.new2
son.ORAS.sst <- son.avg(sst.ORAS.new2, son.only = TRUE)

#sst.OISST.new2
son.OISST.sst <-  son.avg(sst.OISST.new2)

#sst.SODA.new2
son.SODA.sst <- son.avg(sst.SODA.new2)


dim(son.GODAS.sst)
dim(son.ORAS.sst)
dim(son.OISST.sst)
dim(son.SODA.sst)

```

```{r test_sst_anoms}
#sst anoms
##OISST
sst.anom.oisst2 <- sst.anoms(sst.OISST.new2, quadratic = FALSE)
#GODAS
sst.anom.godas2 <- sst.anoms(sst.GODAS.new2, quadratic = FALSE)
#SODA
sst.anom.soda2 <- sst.anoms(sst.SODA.new2, quadratic = FALSE)
#ORA-S5
sst.anom.oras2 <- sst.anoms(sst.ORAS.new2, son.only = TRUE, quadratic = FALSE)

```

(interpolate SST anoms)

```{r interp_sst}
dim.GODAS <- dim(sst.GODAS.new2)
dim.OISST <- dim(sst.OISST.new2)
dim.SODA <- dim(sst.SODA.new2)
dim.ORAS <- dim(sst.ORAS.new2)

#GODAS Interpolat
nx <- dim.GODAS[1]
ny <- dim.GODAS[2]

#GODAS lat: new.lat, lon: new.lon 
GODAS.new <- array(sst.anom.godas2$anom, dim = c(34, ny, nx)) 
GODAS.new <- aperm(GODAS.new, c(3, 2, 1)) #as [nx, ny, nt]

GODAS.anom <- NULL
for (j in seq_len(34)) {
  GODAS.obj <-  list(x = new.lon, y = new.lat, z = GODAS.new[,,j])

  temp.interp <- interp.surface.grid(GODAS.obj, grid.list)
  GODAS.anom <- abind(GODAS.anom, temp.interp$z, along = 3)
}


#ORAS Interpolat
nx <- dim.ORAS[1]
ny <- dim.ORAS[2]

#ORAS lat: oras.lat, lon: oras.lon 
ORAS.new <- array(sst.anom.oras2$anom, dim = c(34, ny, nx)) 
ORAS.new <- aperm(ORAS.new, c(3, 2, 1)) #as [nx, ny, nt]

ORAS.anom <- NULL
for (j in seq_len(34)) {
  ORAS.obj <-  list(x = oras.lon, y = oras.lat, z = ORAS.new[,,j])

  temp.interp <- interp.surface.grid(ORAS.obj, grid.list)
  ORAS.anom <- abind(ORAS.anom, temp.interp$z, along = 3)
}


#OISST Interpolation
nx <- dim.OISST[1]
ny <- dim.OISST[2]


#OISST lat: lat.values.base, lon: lon.values.base 
OISST.new <- array(sst.anom.oisst2$anom, dim = c(34, ny, nx)) 
OISST.new <- aperm(OISST.new, c(3, 2, 1)) #as [nx, ny, nt]

OISST.anom <- NULL
for (j in seq_len(34)) {
  OISST.obj <-  list(x = lon.values.base, y = lat.values.base, z = OISST.new[,,j])

  temp.interp <- interp.surface.grid(OISST.obj, grid.list)
  OISST.anom <- abind(OISST.anom, temp.interp$z, along = 3)
}


#SODA Interpolation
nx <- dim.SODA[1]
ny <- dim.SODA[2]


#SODA lat: lat.values.soda, lon: lon.values.soda 
SODA.new <- array(sst.anom.soda2$anom, dim = c(34, ny, nx)) 
SODA.new <- aperm(SODA.new, c(3, 2, 1)) #as [nx, ny, nt]

SODA.anom <- NULL
for (j in seq_len(34)) {
  SODA.obj <-  list(x = lon.values.soda, y = lat.values.soda, z = SODA.new[,,j])

  temp.interp <- interp.surface.grid(SODA.obj, grid.list)
  SODA.anom <- abind(SODA.anom, temp.interp$z, along = 3)
}

dim(GODAS.anom)
dim(OISST.anom)
dim(ORAS.anom)
dim(SODA.anom)
```

(compare data products)

## Monthly Data Checks

```{r}
#TODO: update range and breaks with all data when done with above data prep
sst.range <- range(sst.GODAS.new, sst.ORAS.new, 
                   sst.OISST.new, sst.SODA.new, na.rm = TRUE)

cols.ryb <- rev(colorRampPalette(brewer.pal(11, "RdYlBu"))(24))
breaks.sst <- seq(sst.range[1], sst.range[2], length.out = length(cols.ryb) + 1)


#GODAS test
sst.godas.test <- sst.GODAS.new[,,10]

imagePlot(list(x = lon.wide, y = lat.wide, z = sst.godas.test), 
           col = cols.ryb, breaks = breaks.sst, zlim = sst.range,
           xlab = "Lon", ylab = "Lat")
title("GODAS", adj = 0)
world(add = TRUE)

#ORAS test
sst.oras.test <- sst.ORAS.new[,,2]

imagePlot(list(x = lon.wide, y = lat.wide, z = sst.oras.test), 
           col = cols.ryb, breaks = breaks.sst, zlim = sst.range,
           xlab = "Lon", ylab = "Lat")
title("ORA-S5", adj = 0)
world(add = TRUE)

#OISST test
sst.oisst.test <- sst.OISST.new[,,10]

imagePlot(list(x = lon.wide, y = lat.wide, z = sst.oisst.test), 
           col = cols.ryb, breaks = breaks.sst, zlim = sst.range,
           xlab = "Lon", ylab = "Lat")
title("OISST", adj = 0)
world(add = TRUE)

#SODA test
sst.soda.test <- sst.SODA.new[,,10]

imagePlot(list(x = lon.wide, y = lat.wide, z = sst.soda.test), 
           col = cols.ryb, breaks = breaks.sst, zlim = sst.range,
           xlab = "Lon", ylab = "Lat")
title("SODA3.3.1", adj = 0)
world(add = TRUE)



```

## SON Mean Checks

```{r}

```

## SON Anomalies

### Interpolation after ANOMS

```{r 1x1grid}

#get range for all sst.anom objects
anom.range <- range(GODAS.anom, OISST.anom,
                    ORAS.anom, SODA.anom, na.rm = TRUE)
anom.absmax <- max(abs(anom.range))
anom.range <- c(-anom.absmax, anom.absmax)
#color/breaks
cols.ryb <- rev(colorRampPalette(brewer.pal(11, "RdYlBu"))(12))
breaks.dumb <- c(anom.range[1], seq(-1,1, 0.2), anom.range[2])
leg.brks2 <- seq(-1.2, 1.2, 0.2) 

#1997 SON anom detrended (as a test case)
k <- 16

#GODAS
image(list(x = lon.wide, y = lat.wide, z = GODAS.anom[,,k]), 
           col = cols.ryb, breaks = breaks.dumb, zlim = resid.range, 
           xlab = "Lon", ylab = "Lat",
           axes = FALSE)
axis(1, at = c(60, 90, 120))  
axis(2)                      
box()
world(add=TRUE, lwd = 1)
title("GODAS SST Anoms 1997", adj = 0)

#OISST
image(list(x = lon.wide, y = lat.wide, z = OISST.anom[,,k]), 
           col = cols.ryb, breaks = breaks.dumb, zlim = resid.range, 
           xlab = "Lon", ylab = "Lat",
           axes = FALSE)
axis(1, at = c(60, 90, 120))  
axis(2)                      
box()
world(add=TRUE, lwd = 1)
title("OISST SST Anoms 1997", adj = 0)

#ORAS
image(list(x = lon.wide, y = lat.wide, z = ORAS.anom[,,k]), 
           col = cols.ryb, breaks = breaks.dumb, zlim = resid.range, 
           xlab = "Lon", ylab = "Lat",
           axes = FALSE)
axis(1, at = c(60, 90, 120))  
axis(2)                      
box()
world(add=TRUE, lwd = 1)
title("ORA-S5 SST Anoms 1997", adj = 0)

#SODA
image(list(x = lon.wide, y = lat.wide, z = SODA.anom[,,k]), 
           col = cols.ryb, breaks = breaks.dumb, zlim = resid.range, 
           xlab = "Lon", ylab = "Lat",
           axes = FALSE)
axis(1, at = c(60, 90, 120))  
axis(2)                      
box()
world(add=TRUE, lwd = 1)
title("SODA3.3.1 SST Anoms 1997", adj = 0)

```

### Interpolation before ANOMS

```{r pre_interp}
##SST anomalies (detrended)
nt <- 34
ny <- 41
nx <- 91

#GODAS
temp1 <- array(sst.anom.godas$anom, dim = c(nt, ny, nx))  # from [nt, ny*nx] to [nt, ny, nx]
godas.anom.base <- aperm(temp1, c(3, 2, 1))  # from [nt, ny, nx] to [nx, ny, nt]

#ORAS
temp2 <- array(sst.anom.oras$anom, dim = c(nt, ny, nx))  # from [nt, ny*nx] to [nt, ny, nx]
oras.anom.base <- aperm(temp2, c(3, 2, 1))  # from [nt, ny, nx] to [nx, ny, nt]

#OISST
temp3 <- array(sst.anom.oisst$anom, dim = c(nt, ny, nx))  # from [nt, ny*nx] to [nt, ny, nx]
oisst.anom.base <- aperm(temp3, c(3, 2, 1))  # from [nt, ny, nx] to [nx, ny, nt]

#SODA
temp4 <- array(sst.anom.soda$anom, dim = c(nt, ny, nx))  # from [nt, ny*nx] to [nt, ny, nx]
soda.anom.base <- aperm(temp4, c(3, 2, 1))  # from [nt, ny, nx] to [nx, ny, nt]

rm(temp1, temp2, temp3, temp4)

#get range for all sst.anom objects
anom.range <- range(godas.anom.base, oras.anom.base,
                    oisst.anom.base, soda.anom.base, na.rm = TRUE)
anom.absmax <- max(abs(anom.range))
anom.range <- c(-anom.absmax, anom.absmax)
#color/breaks
cols.ryb <- rev(colorRampPalette(brewer.pal(11, "RdYlBu"))(12))
breaks.dumb <- c(anom.range[1], seq(-1,1, 0.2), anom.range[2])
leg.brks2 <- seq(-1.2, 1.2, 0.2) 

#1997 SON anom detrended (as a test case)
k <- 16

#GODAS
image(list(x = lon.wide, y = lat.wide, z = godas.anom.base[,,k]), 
           col = cols.ryb, breaks = breaks.dumb, zlim = resid.range, 
           xlab = "Lon", ylab = "Lat",
           axes = FALSE)
axis(1, at = c(60, 90, 120))  
axis(2)                      
box()
world(add=TRUE, lwd = 1)
title("GODAS SST Anoms 1997", adj = 0)

#OISST
image(list(x = lon.wide, y = lat.wide, z = oisst.anom.base[,,k]), 
           col = cols.ryb, breaks = breaks.dumb, zlim = resid.range, 
           xlab = "Lon", ylab = "Lat",
           axes = FALSE)
axis(1, at = c(60, 90, 120))  
axis(2)                      
box()
world(add=TRUE, lwd = 1)
title("OISST SST Anoms 1997", adj = 0)

#ORAS
image(list(x = lon.wide, y = lat.wide, z = oras.anom.base[,,k]), 
           col = cols.ryb, breaks = breaks.dumb, zlim = resid.range, 
           xlab = "Lon", ylab = "Lat",
           axes = FALSE)
axis(1, at = c(60, 90, 120))  
axis(2)                      
box()
world(add=TRUE, lwd = 1)
title("ORA-S5 SST Anoms 1997", adj = 0)

#SODA
image(list(x = lon.wide, y = lat.wide, z = soda.anom.base[,,k]), 
           col = cols.ryb, breaks = breaks.dumb, zlim = resid.range, 
           xlab = "Lon", ylab = "Lat",
           axes = FALSE)
axis(1, at = c(60, 90, 120))  
axis(2)                      
box()
world(add=TRUE, lwd = 1)
title("SODA3.3.1 SST Anoms 1997", adj = 0)
```

### Differences

```{r}
#1997 differences
k <- 16
godas.diff <- 
oras.diff
oisst.diff
soda.diff



```





## SON Detrending



