---
title: "lasso_work.rmd"
author: "Ryan Peterson"
date: "2024-10-08"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libraries}
suppressMessages(library(pls)) #penalized least squares

#lasso
suppressMessages(library(glmnet)) #base lasso (elastic net, etc.)
suppressMessages(library(penalized)) #other lasso lib
suppressMessages(library(gglasso)) #group lasso
#suppressMessages(library(grplasso))

suppressMessages(library(genlasso)) #used for fused lasso (not a fan)
```

Notes:

For LASSO:
-Pred data must be standardized
-Resp data must be centered


```{r data_import}
setwd("~/CO_AUS/Aus_CO-main")

load( "ne_data.rda")
load( "se_data.rda")

load( "bounded_data.rda")
load( "data_matrix.rda")

load( "lag_list.rda")

source("group_function.R")
```



# Group Lasso (Lasso)

## Clusters

Using the clusters (groups) determined in other work we build group lasso models

```{r group_setup}
#centered response matrices
NEbase_matrix <- scale(resp_matrix[ ,1:32], center = TRUE, scale = FALSE)

SEbase_matrix <- scale(resp_matrix[ ,33:64], center = TRUE, scale = FALSE)

#TODO: create lists of the above matrices

#NEAus
NEAus_1 <- NEbase_matrix[ ,1:3]
NEAus_2 <- NEbase_matrix[ ,4:8]
NEAus_3 <- NEbase_matrix[ ,9:12]
NEAus_4 <- NEbase_matrix[ ,13:17]
NEAus_5 <- NEbase_matrix[ ,18:21]
NEAus_6 <- NEbase_matrix[ ,22:32]

#SEAus
SEAus_1 <- SEbase_matrix[ ,1:3]
SEAus_2 <- SEbase_matrix[ ,4:7]
SEAus_3 <- SEbase_matrix[ ,8:16]
SEAus_4 <- SEbase_matrix[ ,17:20]
SEAus_5 <- SEbase_matrix[ ,21:32]

```

```{r lag_preds}
#lag predictor set-up
#TODO: turn this into a function

## NE lag predictors
#NE group 1: 35-37
NE1_lag <- NE_laglist$`Week  35`[,-(1:2)]
NE1_lag <- rbind(NE1_lag, NE_laglist$`Week  36`[,-(1:2)], NE_laglist$`Week  37`[,-(1:2)])

#NE group 2: 38-42
NE2_lag <- NE_laglist$`Week  38`[,-(1:2)]
NE2_lag <- rbind(NE2_lag, NE_laglist$`Week  39`[,-(1:2)], NE_laglist$`Week  40`[,-(1:2)],
                 NE_laglist$`Week  41`[,-(1:2)], NE_laglist$`Week  42`[,-(1:2)])

#NE group 3: 43-46
NE3_lag <- NE_laglist$`Week  43`[,-(1:2)]
NE3_lag <- rbind(NE3_lag, NE_laglist$`Week  44`[,-(1:2)], NE_laglist$`Week  45`[,-(1:2)],
                 NE_laglist$`Week  46`[,-(1:2)])

#NE group 4: 47-51
NE4_lag <- NE_laglist$`Week  47`[,-(1:2)]
NE4_lag <- rbind(NE4_lag, NE_laglist$`Week  48`[,-(1:2)], NE_laglist$`Week  49`[,-(1:2)],
                 NE_laglist$`Week  50`[,-(1:2)], NE_laglist$`Week  51`[,-(1:2)])

#NE group 5: 52, 1-3
NE5_lag <- NE_laglist$`Week  52`[,-(1:2)]
NE5_lag <- rbind(NE5_lag, NE_laglist$`Week  1`[,-(1:2)], NE_laglist$`Week  2`[,-(1:2)],
                 NE_laglist$`Week  3`[,-(1:2)])

#NE group 6: 4-14
NE6_lag <- NE_laglist$`Week  4`[,-(1:2)]
NE6_lag <- rbind(NE6_lag, NE_laglist$`Week  5`[,-(1:2)], NE_laglist$`Week  6`[,-(1:2)],
                 NE_laglist$`Week  7`[,-(1:2)], NE_laglist$`Week  8`[,-(1:2)],
                 NE_laglist$`Week  9`[,-(1:2)], NE_laglist$`Week  10`[,-(1:2)],
                 NE_laglist$`Week  11`[,-(1:2)], NE_laglist$`Week  12`[,-(1:2)],
                 NE_laglist$`Week  13`[,-(1:2)], NE_laglist$`Week  14`[,-(1:2)])


## SE lag predictors
#SE group 1: 35-37
SE1_lag <- SE_laglist$`Week  35`[,-(1:2)]
SE1_lag <- rbind(SE1_lag, SE_laglist$`Week  36`[,-(1:2)], SE_laglist$`Week  37`[,-(1:2)])

#SE group 2: 38-41
SE2_lag <- SE_laglist$`Week  38`[,-(1:2)]
SE2_lag <- rbind(SE2_lag, SE_laglist$`Week  39`[,-(1:2)], SE_laglist$`Week  40`[,-(1:2)],
                 SE_laglist$`Week  41`[,-(1:2)])

#SE group 3: 42-50
SE3_lag <- SE_laglist$`Week  42`[,-(1:2)]
SE3_lag <- rbind(SE3_lag, SE_laglist$`Week  43`[,-(1:2)], SE_laglist$`Week  44`[,-(1:2)],
                 SE_laglist$`Week  45`[,-(1:2)], SE_laglist$`Week  46`[,-(1:2)],
                 SE_laglist$`Week  47`[,-(1:2)], SE_laglist$`Week  48`[,-(1:2)],
                 SE_laglist$`Week  49`[,-(1:2)], SE_laglist$`Week  50`[,-(1:2)])

#SE group 4: 51-52,1-2
SE4_lag <- SE_laglist$`Week  51`[,-(1:2)]
SE4_lag <- rbind(SE4_lag, SE_laglist$`Week  52`[,-(1:2)], SE_laglist$`Week  1`[,-(1:2)],
                 SE_laglist$`Week  2`[,-(1:2)])

#SE group 5: 3-14
SE5_lag <- SE_laglist$`Week  3`[,-(1:2)]
SE5_lag <- rbind(SE5_lag, SE_laglist$`Week  4`[,-(1:2)], SE_laglist$`Week  5`[,-(1:2)],
                 SE_laglist$`Week  6`[,-(1:2)], SE_laglist$`Week  7`[,-(1:2)],
                 SE_laglist$`Week  8`[,-(1:2)], SE_laglist$`Week  9`[,-(1:2)],
                 SE_laglist$`Week  10`[,-(1:2)], SE_laglist$`Week  11`[,-(1:2)],
                 SE_laglist$`Week  12`[,-(1:2)], SE_laglist$`Week  13`[,-(1:2)],
                 SE_laglist$`Week  14`[,-(1:2)])


```


```{r group_resp}
##test
#NE1_resp <- c(NEAus_1[,1], NEAus_1[,2], NEAus_1[,3])


#NE resp vectors
NEAus1_resp <- as.vector(NEAus_1)
NEAus2_resp <- as.vector(NEAus_2)
NEAus3_resp <- as.vector(NEAus_3)
NEAus4_resp <- as.vector(NEAus_4)
NEAus5_resp <- as.vector(NEAus_5)
NEAus6_resp <- as.vector(NEAus_6)

#SE resp vectors
SEAus1_resp <- as.vector(SEAus_1)
SEAus2_resp <- as.vector(SEAus_2)
SEAus3_resp <- as.vector(SEAus_3)
SEAus4_resp <- as.vector(SEAus_4)
SEAus5_resp <- as.vector(SEAus_5)
```


```{r create_list}
#TODO: create resp and pred lists for NE and SE Aus data.
#lists for two different resp (matrix and vector)
#we need to bring over a lot of support data so we can build CV and non-2019 models.

#TODO: export lists as data for other files.
```


```{r test_block}
#weekly predictor set-up
NE1_preds <- NE_list$`Week  35`[,-(1:2)]
NE2_preds <- NE_list$`Week  38`[,-(1:2)]


temp_view <- NE_laglist$`Week  35`[-19,-(1:2)]
```



## Package Testing

Goal is to check several packages to perform multivariate group lasso.

Packages to try: gglasso, glmnet, penalized

Notes:
gglasso: 
-Does not take a matrix of response, only a vector since the manipulation of the data in the function is "fucky"

```{r gglasso_test}
#example from glmnet
#cv.glmnet(cov_matrix, resp_vec, alpha = 1, nfolds = 4)

#test using a subset of preds
#nino_only <- as.matrix(NE1_lag[,1:52])
nino_only <- as.matrix(NE1_preds[,1:52])
nino_only <- scale(nino_only, center = TRUE, scale = TRUE)
row.names(NEAus_1) <- 1:19

test_group <- rep(1:52, each = 1) #not sure if this is how I want it?

#TODO: currently not working as is.
#cv_fit <- cv.gglasso(x = nino_only, y = NEAus_1, group = test_group, nfolds = 5, loss = "ls")
#plot(cv_fit)
```

glmnet:
alpha = 1 for lasso

```{r glmnet_test}
#example function
#fit <- glmnet(X, Y, family="mgaussian", group=groups)
reduced_preds <- as.matrix(NE1_preds[,1:208])
reduced_preds <- scale(reduced_preds, center = TRUE, scale = TRUE)
row.names(NEAus_1) <- 1:19

set.seed(300)
cv_fit <- cv.glmnet(reduced_preds, NEAus_1, alpha = 0.815, nfolds = 5, family = "mgaussian")
plot(cv_fit)

best_lambda <- cv_fit$lambda.min

test_model <- glmnet(reduced_preds, NEAus_1, alpha = 0.815, family = "mgaussian")
test_pred <- predict(test_model, s = best_lambda, type = "coefficients")
preds <- test_pred$NEAus35@i+1

test_pred$NEAus35@i+1
test_pred$NEAus36@i+1
test_pred$NEAus35[preds,]
test_pred$NEAus36[preds,]
```



```{r error_checks}
#checks for error: "x and y have different number of rows"
nrow(NEAus_1)
nrow(nino_only)

is.numeric(NEAus_1)
is.numeric(nino_only)

dim(nino_only)
length(NEAus_1)

drop(NEAus_1)
```


## Lasso Variations

```{r lag_test}
#testing using "stacked" vectors and matrices for pre-clustered response
NE1_resp <- c(NEAus_1[,1], NEAus_1[,2], NEAus_1[,3])

#set new matrices for  
NE35_lag <- scale(as.matrix(NE_laglist$`Week  35`[,-(1:2)]), center = TRUE, scale = TRUE)
NE36_lag <- scale(as.matrix(NE_laglist$`Week  36`[,-(1:2)]), center = TRUE, scale = TRUE)
NE37_lag <- scale(as.matrix(NE_laglist$`Week  37`[,-(1:2)]), center = TRUE, scale = TRUE)
    
#lag predictor set-up 
NE1_lag <- rbind(NE35_lag, NE36_lag, NE37_lag)
#removing OLR
NE1_lag <- NE1_lag[,1:208]

set.seed(300)
cv_lagfit <- cv.glmnet(NE1_lag, NE1_resp, alpha = 0.5, nfolds = 5)
plot(cv_lagfit)

best_lambda <- cv_lagfit$lambda.min

test_model <- glmnet(NE1_lag, NE1_resp, alpha = 0.5)
test_pred <- predict(test_model, s = best_lambda, type = "coefficients")

preds <- test_pred@i+1
test_pred[preds, ]
```



```{r fused_lasso}
#fused lasso with above data matrix and response vector.

#separate data for each predictor
nino_lag <- NE1_lag[,1:52]
dmi_lag <- NE1_lag[,53:104]
tsa_lag <- NE1_lag[,105:156]
aao_lag <- NE1_lag[,157:208]
olr_lag <- NE1_lag[,209:260]

#D <- getD1d(52)

#TODO: create a new D value that accounts for the jumps between climate modes (predictor groups).

nino_fuse <- fusedlasso(y = NE1_resp, X = nino_lag, D, gamma = 0.75)
dmi_fuse <- fusedlasso(y = NE1_resp, X = dmi_lag, D, gamma = 0.75)
tsa_fuse <- fusedlasso(y = NE1_resp, X = tsa_lag, D, gamma = 0.75)
aao_fuse <- fusedlasso(y = NE1_resp, X = aao_lag, D, gamma = 0.75)
```


```{r}
#nino_fuse$lambda
n <- length(NE1_resp)
#p <- ncol(nino_fuse)
ltest <- sqrt(n * log(52))

nino_coef <- coef(nino_fuse, lambda = ltest)
dmi_coef <- coef(dmi_fuse, lambda = ltest)
tsa_coef <- coef(tsa_fuse, lambda = ltest)
aao_coef <- coef(aao_fuse, lambda = ltest)

#ols <- nino_fuse$bls
#plot(1:52, ols, type = "l")
#lines(1:52, coef_test$beta, lwd=1.5, col = "red")

plot(1:52, nino_coef$beta, type = "l", xlab = "Lag", ylab = "Coeficients", main = "Nino")
abline(h = 0, lty = 2)

plot(1:52, dmi_coef$beta, type = "l", xlab = "Lag", ylab = "Coeficients", main = "DMI")
abline(h = 0, lty = 2)

plot(1:52, tsa_coef$beta, type = "l", xlab = "Lag", ylab = "Coeficients", main = "TSA")
abline(h = 0, lty = 2)

plot(1:52, aao_coef$beta, type = "l", xlab = "Lag", ylab = "Coeficients", main = "AAO")
abline(h = 0, lty = 2)
```


```{r matrix_adj}

D <- getD1d(52)
empty_D <- matrix(rep(0, (52*51)) , ncol = 52, nrow = 51)
D1 <- cbind(D, empty_D, empty_D, empty_D, empty_D)


D2 <- cbind(empty_D, D, empty_D, empty_D, empty_D)


D3 <- cbind(empty_D, empty_D, D, empty_D, empty_D)
D4 <- cbind(empty_D, empty_D, empty_D, D, empty_D)
D5 <- cbind(empty_D, empty_D, empty_D, empty_D, D)

#D_new <- rbind(D1, D2, D3, D4, D5)
D_new <- rbind(D1, D2, D3, D4)
D_new <- D_new[,-(209:260)]
```


```{r combined}
#column bind data
#nino/dmi
#new_preds <- cbind(nino_lag, dmi_lag, tsa_lag, aao_lag, olr_lag)

new_preds <- cbind(nino_lag, dmi_lag, tsa_lag, aao_lag)


new_fuse <- fusedlasso(y = NE1_resp, X = new_preds, D_new, gamma = 1)
```

```{r}
n <- length(NE1_resp)
#p <- ncol(nino_fuse)
ltest <- sqrt(n * log(208))

new_coef <- coef(new_fuse, lambda = ltest)
nino_coef2 <- new_coef$beta[1:52,]
dmi_coef2 <- new_coef$beta[53:104,]
tsa_coef2 <- new_coef$beta[105:156,]
aao_coef2 <- new_coef$beta[157:208,]
#olr_coef2 <- new_coef$beta[209:260,]

#ols <- nino_fuse$bls
#plot(1:52, ols, type = "l")
#lines(1:52, coef_test$beta, lwd=1.5, col = "red")

plot(1:52, nino_coef2, type = "l", xlab = "Lag", ylab = "Coeficients", main = "Nino + DMI", ylim = range(new_coef$beta))
lines(1:52, dmi_coef2, col = "blue")
lines(1:52, tsa_coef2, col = "red")
lines(1:52, aao_coef2, col = "darkgreen")
abline(h = 0, lty = 2)


plot(1:52, nino_coef2, type = "l", xlab = "Lag", ylab = "Coeficients", main = "Nino")
abline(h = 0, lty = 2)

plot(1:52, dmi_coef2, type = "l", xlab = "Lag", ylab = "Coeficients", main = "DMI", col = "blue")
abline(h = 0, lty = 2)

plot(1:52, tsa_coef2, type = "l", xlab = "Lag", ylab = "Coeficients", main = "TSA", col = "red")
abline(h = 0, lty = 2)

plot(1:52, aao_coef2, type = "l", xlab = "Lag", ylab = "Coeficients", main = "AAO", col = "darkgreen")
abline(h = 0, lty = 2)

#plot(1:52, olr_coef2, type = "l", xlab = "Lag", ylab = "Coeficients", main = "OLR", col = "purple")
#abline(h = 0, lty = 2)
```

```{r}

```


```{r predictions}
group1_coef <- as.vector(new_coef$beta)

ne_week35 <- NE_laglist$`Week  35`
ne_week36 <- NE_laglist$`Week  36`
ne_week37 <- NE_laglist$`Week  37`

i <- 15
week35_preds <- as.matrix(ne_week35[i,3:210])
week36_preds <- as.matrix(ne_week36[i,3:210])
week37_preds <- as.matrix(ne_week37[i,3:210])

ne_week35[i,2]
week35_preds %*% group1_coef

ne_week36[i,2]
week36_preds %*% group1_coef

ne_week37[i,2]
week37_preds %*% group1_coef




```


## Group Variations

Test out variations on group lasso, such as sparse group lasso or fused group lasso. 




# Fused Lasso

Come back to this if everything else is not working

```{r data}
#testing with week 36 of NE Aus
week_36 <- NE_laglist[[2]]

cov_matrix <- as.matrix(week_36[,3:54]) #nino only
#cov_matrix <- scale(cov_matrix)
resp_vec <- week_36$NE_Aus
#resp_vec <- scale(resp_vec, center = TRUE, scale = FALSE)

#remove 2019/2020
cov_matrix <- cov_matrix[-19, ]
resp_vec <- resp_vec[-19]
```


```{r}

#c(1:52, 54:105)
#D <- getD1d(52)
#test_fuse <- fusedlasso(resp_vec, cov_matrix, D)

test_fuse <- fusedlasso1d(resp_vec, pos = c(1:52), cov_matrix)

test_lambda <- median(test_fuse$lambda)
plot(test_fuse, lambda = test_lambda)
plot(test_fuse, style = "path")



#plot(test_fuse, style = "trend")
```

instead of clustering can I used change point through trend fitting?

```{r}
resp_year <- scale(resp_matrix, center = TRUE, scale = FALSE)
resp_season <- resp_year[3, 1:32]

resp_sig <- fusedlasso1d(resp_season)
plot(resp_sig)
plot(resp_sig, style = "path")

cv = cv.trendfilter(resp_sig)

plot(resp_sig, lambda=cv$lambda.1se, main="Minimal CV error")
```

