---
title: "lasso_work.rmd"
author: "Ryan Peterson"
date: "2024-10-08"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libraries}
suppressMessages(library(pls)) #penalized least squares

#lasso
suppressMessages(library(glmnet)) #base lasso (elastic net, etc.)
suppressMessages(library(penalized)) #other lasso lib
suppressMessages(library(gglasso)) #group lasso
#suppressMessages(library(grplasso))

suppressMessages(library(genlasso)) #used for fused lasso (not a fan)
```

Notes:

For LASSO:
-Pred data must be standardized
-Resp data must be centered


```{r data_import}
setwd("~/CO_AUS/Aus_CO-main")

load( "ne_data.rda")
load( "se_data.rda")

load( "bounded_data.rda")
load( "data_matrix.rda")

load( "lag_list.rda")
```



# Group Lasso (Lasso)

Using the clusters (groups) determined in other work we build group lasso models

```{r group_setup}
NEbase_matrix <- scale(resp_matrix[, 1:32], center = TRUE, scale = FALSE)

SEbase_matrix <- scale(resp_matrix[,33:64], center = TRUE, scale = FALSE)

#NEAus
NEAus_1 <- NEbase_matrix[ ,1:3]
NEAus_2 <- NEbase_matrix[ ,4:8]
NEAus_3 <- NEbase_matrix[ ,9:12]
NEAus_4 <- NEbase_matrix[ ,13:17]
NEAus_5 <- NEbase_matrix[ ,18:32]

#SEAus
SEAus_1 <- SEbase_matrix[ ,1:3]
SEAus_2 <- SEbase_matrix[ ,4:7]
SEAus_3 <- SEbase_matrix[ ,8:16]
SEAus_4 <- SEbase_matrix[ ,17:20]
SEAus_5 <- SEbase_matrix[ ,21:32]

#TODO: create lists of the above matrices


#lag predictor set-up 
NE1_lag <- NE_laglist$`Week  35`[,-(1:2)]
NE1_lag <- rbind(NE1_lag, NE_laglist$`Week  36`[,-(1:2)], NE_laglist$`Week  37`[,-(1:2)])

#NE_laglist$`Week  35`


#weekly predictor set-up
NE1_preds <- NE_list$`Week  35`[,-(1:2)]
NE2_preds <- NE_list$`Week  38`[,-(1:2)]
```


## Package Testing

Goal is to check several packages to perform multivariate group lasso.

Packages to try: gglasso, glmnet, penalized

Notes:
gglasso: 
-Does not take a matrix of response, only a vector since the manipulation of the data in the function is "fucky"

```{r gglasso_test}
#example from glmnet
#cv.glmnet(cov_matrix, resp_vec, alpha = 1, nfolds = 4)

#test using a subset of preds
#nino_only <- as.matrix(NE1_lag[,1:52])
nino_only <- as.matrix(NE1_preds[,1:52])
nino_only <- scale(nino_only, center = TRUE, scale = TRUE)
row.names(NEAus_1) <- 1:19

test_group <- rep(1:52, each = 1) #not sure if this is how I want it?

#TODO: currently not working as is.
cv_fit <- cv.gglasso(x = nino_only, y = NEAus_1, group = test_group, nfolds = 5, loss = "ls")
plot(cv_fit)
```

glmnet:
-alpha = 1 for 

```{r glmnet_test}
#example function
#fit <- glmnet(X, Y, family="mgaussian", group=groups)

reduced_preds <- as.matrix(NE1_preds[,1:208])
reduced_preds <- scale(reduced_preds, center = TRUE, scale = TRUE)
row.names(NEAus_1) <- 1:19

set.seed(300)
cv_fit <- cv.glmnet(reduced_preds, NEAus_1, alpha = 0.815, nfolds = 5, family = "mgaussian")
plot(cv_fit)

best_lambda <- cv_fit$lambda.min

test_model <- glmnet(reduced_preds, NEAus_1, alpha = 0.815, family = "mgaussian")
test_pred <- predict(test_model, s = best_lambda, type = "coefficients")
preds <- test_pred$NEAus35@i+1

test_pred$NEAus35@i+1
test_pred$NEAus36@i+1
test_pred$NEAus35[preds,]
test_pred$NEAus36[preds,]
```



```{r error_checks}
#checks for error: "x and y have different number of rows"
nrow(NEAus_1)
nrow(nino_only)

is.numeric(NEAus_1)
is.numeric(nino_only)

dim(nino_only)
length(NEAus_1)

drop(NEAus_1)
```


## Lasso Variations

```{r lag_test}
#testing using "stacked" vectors and matrices for pre-clustered response
NE1_resp <- c(NEAus_1[,1], NEAus_1[,2], NEAus_1[,3])

#set new matrices for  
NE35_lag <- scale(as.matrix(NE_laglist$`Week  35`[,-(1:2)]), center = TRUE, scale = TRUE)
NE36_lag <- scale(as.matrix(NE_laglist$`Week  36`[,-(1:2)]), center = TRUE, scale = TRUE)
NE37_lag <- scale(as.matrix(NE_laglist$`Week  37`[,-(1:2)]), center = TRUE, scale = TRUE)
    
#lag predictor set-up 
NE1_lag <- rbind(NE35_lag, NE36_lag, NE37_lag)
#removing OLR
NE1_lag <- NE1_lag[,1:208]

set.seed(300)
cv_lagfit <- cv.glmnet(NE1_lag, NE1_resp, alpha = 0.5, nfolds = 5)
plot(cv_lagfit)

best_lambda <- cv_lagfit$lambda.min

test_model <- glmnet(NE1_lag, NE1_resp, alpha = 0.5)
test_pred <- predict(test_model, s = best_lambda, type = "coefficients")

preds <- test_pred@i+1
test_pred[preds, ]
```


## Group Variations

Test out variations on group lasso, such as sparse group lasso or fused group lasso. 




# Fused Lasso

Come back to this if everything else is not working

```{r data}
#testing with week 36 of NE Aus
week_36 <- NE_laglist[[2]]

cov_matrix <- as.matrix(week_36[,3:54]) #nino only
#cov_matrix <- scale(cov_matrix)
resp_vec <- week_36$NE_Aus
#resp_vec <- scale(resp_vec, center = TRUE, scale = FALSE)

#remove 2019/2020
cov_matrix <- cov_matrix[-19, ]
resp_vec <- resp_vec[-19]
```


```{r}

#c(1:52, 54:105)
#D <- getD1d(52)
#test_fuse <- fusedlasso(resp_vec, cov_matrix, D)

test_fuse <- fusedlasso1d(resp_vec, pos = c(1:52), cov_matrix)

test_lambda <- median(test_fuse$lambda)
plot(test_fuse, lambda = test_lambda)
plot(test_fuse, style = "path")



#plot(test_fuse, style = "trend")
```

instead of clustering can I used change point through trend fitting?

```{r}
resp_year <- scale(resp_matrix, center = TRUE, scale = FALSE)
resp_season <- resp_year[3, 1:32]

resp_sig <- fusedlasso1d(resp_season)
plot(resp_sig)
plot(resp_sig, style = "path")

cv = cv.trendfilter(resp_sig)

plot(resp_sig, lambda=cv$lambda.1se, main="Minimal CV error")
```

