---
title: "lasso_validation"
author: "Ryan Peterson"
date: "2025-02-07"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library}
#libraries
suppressMessages(library(genlasso)) #used for fused lasso 
suppressMessages(library(MASS)) #for matrix shenanigans in functions.

suppressMessages( library(tictoc)) #some timing
```

```{r data_functions}
# Data Set-Up
setwd("~/CO_AUS/Aus_CO-main")

load( "ne_data.rda")
load( "se_data.rda")
load( "bounded_data.rda")
load( "data_matrix.rda")
load( "lag_list.rda")

load( "lasso_pred.rda") #base lasso predictions
#load( "lasso_quantpred.rda")

#functions
source("group_functions.R")
source("lasso_valid_functions.R") #include predict.fusedlasso
source("genlasso_func.R") #includes cv.fusedlasso (DO NOT USE in final work; change, correct, and move)

```


```{r data_setup}
#set up season years/weeks
season_weeks <- c(35:52, 1:14)
season_years <- unique(bounded_resp_df$year)

seasons <- c()
for (i in 1:(length(season_years)-1)) {
  temp_season <- paste0(season_years[i], "-", season_years[i+1])
  #print(temp_season)  
  seasons <- c(seasons, temp_season)
}
rm(i, temp_season)

#center response data
NEbase_matrix <- scale(resp_matrix[ ,1:32], center = TRUE, scale = FALSE)
SEbase_matrix <- scale(resp_matrix[ ,33:64], center = TRUE, scale = FALSE)

#group response matrices
#NEAus
NEAus_1 <- NEbase_matrix[ ,1:3]
NEAus_2 <- NEbase_matrix[ ,4:8]
NEAus_3 <- NEbase_matrix[ ,9:12]
NEAus_4 <- NEbase_matrix[ ,13:17]
NEAus_5 <- NEbase_matrix[ ,18:21]
NEAus_6 <- NEbase_matrix[ ,22:32]

#SEAus
SEAus_1 <- SEbase_matrix[ ,1:3]
SEAus_2 <- SEbase_matrix[ ,4:7]
SEAus_3 <- SEbase_matrix[ ,8:16]
SEAus_4 <- SEbase_matrix[ ,17:20]
SEAus_5 <- SEbase_matrix[ ,21:32]

NEAus_mat <- list(NEAus_1, NEAus_2, NEAus_3, NEAus_4, NEAus_5, NEAus_6)
SEAus_mat <- list(SEAus_1, SEAus_2, SEAus_3, SEAus_4, SEAus_5)

rm(NEAus_1, NEAus_2, NEAus_3, NEAus_4, NEAus_5, NEAus_6, SEAus_1, SEAus_2, SEAus_3, SEAus_4, SEAus_5)

#full model
NE_preds <- NElag_grouping(NE_laglist = NE_laglist_std, j = -c(19))
NE_resp <- NEresp_grouping(NEAus_mat = NEAus_mat, j = -c(19))

SE_preds <- SElag_grouping(SE_laglist = SE_laglist_std, j = -c(19))
SE_resp <- SEresp_grouping(SEAus_mat = SEAus_mat, j = -c(19))

#Update for OLR (D5)
# distance matrices
D <- getD1d(52)
empty_D <- matrix(rep(0, (52*51)) , ncol = 52, nrow = 51)
D1 <- cbind(D, empty_D, empty_D, empty_D, empty_D)
D2 <- cbind(empty_D, D, empty_D, empty_D, empty_D)
D3 <- cbind(empty_D, empty_D, D, empty_D, empty_D)
D4 <- cbind(empty_D, empty_D, empty_D, D, empty_D)
D5 <- cbind(empty_D, empty_D, empty_D, empty_D, D)

D_olr <- rbind(D1, D2, D3, D4, D5)

rm(D, empty_D, D1, D2, D3, D4, D5)
```


```{r base_test}
#non-bootstrap
beta_matrix <- NEfuse_grouplist[[1]]$beta
nino_beta <- beta_matrix[1:52, ]
dmi_beta <- beta_matrix[53:104, ]

boxplot(t(nino_beta), horizontal = TRUE, col = "lightblue", pch = 16, main = "Nino - NE Group 1")
boxplot(t(dmi_beta), horizontal = TRUE, col = "lightblue", pch = 16, main = "DMI - NE Group 1")

```

# Bootstrap

We want to re-use this bootstrap for a lot of things so we only want to do this once.

```{r bootstrap_setup}
#TODO: setup look for all groups



n <- length(NE_resp)
#n <- length(SE_resp)


#for(i in 1:n) {}
i <- 1

NEresp_temp <- NE_resp[[i]]
NEpred_temp <- as.matrix(NE_preds[[i]][ ,1:260])

NE_temp <- cbind(NEresp_temp, NEpred_temp)

SEresp_temp <- SE_resp[[i]]
SEpred_temp <- as.matrix(SE_preds[[i]][ ,1:260])

SE_temp <- cbind(SEresp_temp, SEpred_temp)

B <- 2
set.seed(351)
NE_bootstrap <- lapply(1:B, function(i) NE_temp[sample(1:nrow(NE_temp), replace = TRUE), ])

NE_gamma <- 0.85
NEfuse_grouplist <- list()
NEfuse_cv <- list()
NE_lambdamin <- c()

for (j in 1:B) {
  NEresp_temp <- NE_bootstrap[[j]][ ,1]
  NEpred_temp <- as.matrix(NE_bootstrap[[j]][ ,2:261])
    
  NEgroup_temp <- fusedlasso(y = NEresp_temp, X = NEpred_temp, 
                             D_olr, gamma = NE_gamma)
    
  NEgroup_cv <- cv.fusedlasso(NEgroup_temp, k =10, D_olr) 
      
  NE_lambdamin <- c(NE_lambdamin, NEgroup_cv$lambda.min)  
  NEfuse_grouplist[[paste0("Group_", j)]] <- NEgroup_temp
  NEfuse_cv[[paste0("Group_", j)]] <- NEgroup_cv
}


#TODO: use lambdamin to for each bootstrap to determine which beta's to use

```


```{r}

#full model
NE_preds <- NElag_grouping(NE_laglist = NE_laglist_std, j = -c(19))
NE_resp <- NEresp_grouping(NEAus_mat = NEAus_mat, j = -c(19))

SE_preds <- SElag_grouping(SE_laglist = SE_laglist_std, j = -c(19))
SE_resp <- SEresp_grouping(SEAus_mat = SEAus_mat, j = -c(19))

NE_gamma <- 0.85
NEfuse_grouplist <- list()
#NEfuse_cv <- list()
NE_coefs <- list()
NE_lambdamin <- list()

tic()
n <- length(NE_resp)
for (i in 1:n) {
  NEresp_temp <- NE_resp[[i]]
  NEpred_temp <- as.matrix(NE_preds[[i]][ ,1:260])
  
  NE_temp <- cbind(NEresp_temp, NEpred_temp)
  
  B <- 50
  set.seed(351)
  NE_bootstrap <- lapply(1:B, 
                         function(i) NE_temp[sample(1:nrow(NE_temp), 
                                                    replace = TRUE), ])
  
  NE_beta <- matrix(NA, ncol = 260)
  NEfuse_boot <- list()
  NElambda_boot <- c()
  #NEfuseCV_boot <- list()
  for (j in 1:B) {
    NEresp_boot <- NE_bootstrap[[j]][ ,1]
    NEpred_boot <- as.matrix(NE_bootstrap[[j]][ ,2:261])
    
    NEgroup_temp <- fusedlasso(y = NEresp_boot, X = NEpred_boot, 
                             D_olr, gamma = NE_gamma)
    
    NEgroup_cv <- cv.fusedlasso(NEgroup_temp, k =10, D_olr) 
      
    NElambda_boot <- c(NElambda_boot, NEgroup_cv$lambda.min)
    NE_beta <- rbind(NE_beta, c(coef(NEgroup_temp,
                     lambda = NEgroup_cv$lambda.min)$beta))
    NEfuse_boot[[paste0("Boot_", j)]] <- NEgroup_temp
    #NEfuseCV_boot[[paste0("Boot_", j)]] <- NEgroup_cv
  }

  NE_coefs[[paste0("Group_", i)]] <- NE_beta[-1, ]
  NEfuse_grouplist[[paste0("Group_", i)]] <- NEfuse_boot
  NE_lambdamin[[paste0("Group_", i)]] <- NElambda_boot
  #NEfuse_cv[[paste0("Group_", i)]] <- NEfuseCV_boot
}

toc()

save(NE_coefs, NEfuse_grouplist,NE_lambdamin,
     file = "NE_boot.rda") #save 
```


```{r}

#full model
SE_preds <- SElag_grouping(SE_laglist = SE_laglist_std, j = -c(19))
SE_resp <- SEresp_grouping(SEAus_mat = SEAus_mat, j = -c(19))

SE_gamma <- 0.85
SEfuse_grouplist <- list()
#NEfuse_cv <- list()
SE_coefs <- list()
SE_lambdamin <- list()

tic()
n <- length(SE_resp)
for (i in 1:n) {
  SEresp_temp <- SE_resp[[i]]
  SEpred_temp <- as.matrix(SE_preds[[i]][ ,1:260])
  
  SE_temp <- cbind(SEresp_temp, SEpred_temp)
  
  B <- 50
  set.seed(351)
  SE_bootstrap <- lapply(1:B, 
                         function(i) SE_temp[sample(1:nrow(SE_temp), 
                                                    replace = TRUE), ])
  
  SE_beta <- matrix(NA, ncol = 260)
  SEfuse_boot <- list()
  SElambda_boot <- c()
  #NEfuseCV_boot <- list()
  for (j in 1:B) {
    SEresp_boot <- SE_bootstrap[[j]][ ,1]
    SEpred_boot <- as.matrix(SE_bootstrap[[j]][ ,2:261])
    
    SEgroup_temp <- fusedlasso(y = SEresp_boot, X = SEpred_boot, 
                             D_olr, gamma = SE_gamma)
    
    SEgroup_cv <- cv.fusedlasso(SEgroup_temp, k =10, D_olr) 
      
    SElambda_boot <- c(SElambda_boot, SEgroup_cv$lambda.min)
    SE_beta <- rbind(SE_beta, c(coef(SEgroup_temp,
                     lambda = SEgroup_cv$lambda.min)$beta))
    SEfuse_boot[[paste0("Boot_", j)]] <- SEgroup_temp
    #NEfuseCV_boot[[paste0("Boot_", j)]] <- NEgroup_cv
  }

  SE_coefs[[paste0("Group_", i)]] <- SE_beta[-1, ]
  SEfuse_grouplist[[paste0("Group_", i)]] <- SEfuse_boot
  SE_lambdamin[[paste0("Group_", i)]] <- SElambda_boot
  #NEfuse_cv[[paste0("Group_", i)]] <- NEfuseCV_boot
}

toc()

save(SE_coefs, SEfuse_grouplist,SE_lambdamin,
     file = "SE_boot.rda") #save 
```


```{r}
bootNE_coefs <- NE_coefs
bootNEfuse_grouplist <- NEfuse_grouplist
bootNE_lambdamin <- NE_lambdamin

bootSE_coefs <- SE_coefs
bootSEfuse_grouplist <- SEfuse_grouplist
bootSE_lambdamin <- SE_lambdamin
```


# Coefficients

Reproducing some of the coefficient work from the lasso book.

```{r}
#TODO: create effective viz for all groups and regions
beta_matrix <- bootSE_coefs$Group_4
nino_beta <- beta_matrix[ ,1:52]
dmi_beta <- beta_matrix[ ,53:104]
tsa_beta <- beta_matrix[ ,105:156]
aao_beta <- beta_matrix[ ,157:208]
olr_beta <- beta_matrix[ ,209:260]

#TODO: reduce the size and chage shape of outliers
#TODO: include "true" value from base lasso
boxplot(t(nino_beta), horizontal = TRUE, col = "lightblue", pch = 16, main = "Nino - SE Group 4")
boxplot(t(dmi_beta), horizontal = TRUE, col = "lightblue", pch = 16, main = "DMI - SE Group 4")
boxplot(t(tsa_beta), horizontal = TRUE, col = "lightblue", pch = 16, main = "TSA - SE Group 4")
boxplot(t(aao_beta), horizontal = TRUE, col = "lightblue", pch = 16, main = "AAO - SE Group 4")
boxplot(t(olr_beta), horizontal = TRUE, col = "lightblue", pch = 16, main = "OLR - SE Group 4")

#TODO: compare with "true" coefficient values from the data
```

```{r}
#get zero ration
beta_matrix <- bootSE_coefs$Group_5
SE1_zero <- colSums(beta_matrix != 0)/50

barplot(SE1_zero[1:52], col = "skyblue", border = "black", ylim = c(0,1),
        main = "Nino - SE Group 5 ")
barplot(SE1_zero[53:104], col = "skyblue", border = "black", ylim = c(0,1),
        main = "DMI - SE Group 5 ")
barplot(SE1_zero[105:156], col = "skyblue", border = "black", ylim = c(0,1),
        main = "TSA - SE Group 5 ")
barplot(SE1_zero[157:208], col = "skyblue", border = "black", ylim = c(0,1),
        main = "AAO - SE Group 5 ")
barplot(SE1_zero[209:260], col = "skyblue", border = "black", ylim = c(0,1),
        main = "OLR - SE Group 5 ")
```

```{r lambda_min}
#TODO: plot lambda_min and compare with "theoretical" values
```


# Validation 

Perform validation work, repeated from Report 2 and simple linear models:
(check for de-biased/bias issues)
- Proper scoring rules
- RMSE (maybe?)
- Residuals
- Covariance test statistic

Do we need to repeat some LOO work here?

```{r reload_base}
#TODO: repeat earlier validation work
#start with base then add in 

#load in original data
load( "lasso_pred.rda") #base lasso predictions
load( "lasso_loo.rda") #NE,SE All
```

## Coefs

```{r}
#TODO: add in fuse coefs
```


## Residuals (and RMSE)

```{r insample}
# in-sample resids
#TODO: begin with group based resids

SE_resids <- list()
for (j in 1:length(SEfuse_grouplist)) {
  resp_vec <- SE_resp[[j]]
  pred_matrix <- as.matrix(SE_preds[[j]])

  SE1_coefs <- coef(SEfuse_grouplist[[j]], 
                    lambda = SEfuse_cv[[j]]$lambda.min)$beta

  resp_hat <- c(pred_matrix %*% SE1_coefs)
  resids <- resp_vec - resp_hat 
  SE_resids[[paste0("Group_", j)]] <- resids
}

NE_resids <- list()
for (j in 1:length(NEfuse_grouplist)) {
  resp_vec <- NE_resp[[j]]
  pred_matrix <- as.matrix(NE_preds[[j]])

  NE1_coefs <- coef(NEfuse_grouplist[[j]], 
                    lambda = NEfuse_cv[[j]]$lambda.min)$beta

  resp_hat <- c(pred_matrix %*% NE1_coefs)
  resids <- resp_vec - resp_hat 
  NE_resids[[paste0("Group_", j)]] <- resids
}

boxplot(SE_resids, main = "SE Aus Lasso Residuals", 
        xlab = "Group", ylab = "", pch = 16)
boxplot(NE_resids, main = "NE Aus Lasso Residuals", 
        xlab = "Group", ylab = "", pch = 16)
```


```{r group_setup}
#assign groups and functions

#NE groups
NE_groups <- list(
  NEgroup1 <- season_weeks[1:3],
  NEgroup2 <- season_weeks[4:8],
  NEgroup3 <- season_weeks[9:12],
  NEgroup4 <- season_weeks[13:17],
  NEgroup5 <- season_weeks[18:21],
  NEgroup6 <- season_weeks[22:32] )

#SE groups
SE_groups <- list(
  SEgroup1 <- season_weeks[1:3],
  SEgroup2 <- season_weeks[4:7],
  SEgroup3 <- season_weeks[8:16],
  SEgroup4 <- season_weeks[17:20],
  SEgroup5 <- season_weeks[21:32] )

#define and correct function
find_group <- function(weeks, groups) {
  group_val <- 1:length(groups)
  found_group <- group_val[sapply(groups, function(g) weeks %in% g)]
  return(ifelse(length(found_group) > 0, found_group, NA))
}

```


```{r outofsample}
##TODO: update with correct lambda values

#NE Outofsample resids

NE_weekpreds <- list()
for (k in 1:32) {
  ne_week <- NE_laglist_std[[k]]
  
  week_preds <- as.data.frame(matrix(NA, ncol = 3))
  colnames(week_preds) <- c("True", "Pred", "Resid")
  
  #requires group info
  j <- find_group(season_weeks[k], NE_groups)

  temp_lambda <- temp_fuse$lambda[which.min(abs(temp_fuse$lambda - NEfuse_cv[[j]]$lambda.min))]
  
  for (i in 1:18) {
    temp_preds <- as.matrix(ne_week[i, 3:262])
    temp_resp <- NEbase_matrix[i, k]
    
    #get coeffs
    temp_fuse <- NEfuse_all[[i]][[j]]
    ne_beta <- coef(temp_fuse, lambda = temp_lambda)$beta
    
    pred_temp <- temp_preds %*% ne_beta
    temp_resid <- temp_resp - pred_temp
    
    week_preds <- rbind(week_preds, c(temp_resp, pred_temp, temp_resid))
  }
  
  NE_weekpreds[[paste0("Week_", season_weeks[k])]] <- week_preds[-1, ]
}


#SE Outofsample resids

SE_weekpreds <- list()
for (k in 1:32) {
  se_week <- SE_laglist_std[[k]]
  
  week_preds <- as.data.frame(matrix(NA, ncol = 3))
  colnames(week_preds) <- c("True", "Pred", "Resid")
  
  #requires group info
  j <- find_group(season_weeks[k], SE_groups)

  temp_lambda <- temp_fuse$lambda[which.min(abs(temp_fuse$lambda - SEfuse_cv[[j]]$lambda.min))]
  
  for (i in 1:18) {
    temp_preds <- as.matrix(se_week[i, 3:262])
    temp_resp <- SEbase_matrix[i, k]
    
    #get coeffs
    temp_fuse <- SEfuse_all[[i]][[j]]
    se_beta <- coef(temp_fuse, lambda = temp_lambda)$beta
    
    pred_temp <- temp_preds %*% se_beta
    temp_resid <- temp_resp - pred_temp
    
    week_preds <- rbind(week_preds, c(temp_resp, pred_temp, temp_resid))
  }
  
  SE_weekpreds[[paste0("Week_", season_weeks[k])]] <- week_preds[-1, ]
}


```



```{r resid_viz}

#visualize out-of-sample residuals 
residNE_box_df <- data.frame(values = NA, group = NA)
residSE_box_df <- data.frame(values = NA, group = NA)

for (i in 1:32) {
  temp_NEvals <- NE_weekpreds[[i]]$Resid
  temp_NEgroup <- rep(season_weeks[i], length(NE_weekpreds[[i]]$Resid))
  residNE_box_df <- rbind(residNE_box_df, list(temp_NEvals, temp_NEgroup))
  
  temp_SEvals <- SE_weekpreds[[i]]$Resid
  temp_SEgroup <- rep(season_weeks[i], length(SE_weekpreds[[i]]$Resid))
  residSE_box_df <- rbind(residSE_box_df, list(temp_SEvals, temp_SEgroup))
}

residNE_box_df <- residNE_box_df[-1, ]
residNE_box_df$group <- as.factor(residNE_box_df$group)
residNE_box_df$values <- as.numeric(residNE_box_df$values)

residSE_box_df <- residSE_box_df[-1, ]
residSE_box_df$group <- as.factor(residSE_box_df$group)
residSE_box_df$values <- as.numeric(residSE_box_df$values)



```

```{r}
#TODO: redo with cv

setwd("~/CO_AUS/Aus_CO-main/Figures_Lasso/Pred_Fig")

#TODO:update using resid_lim from the simplified linear model
resid_lim <- c(-20, 40)

png("NEresidsd_out.png", width = 2250, height = 1250, res = 200)
par(mar = c(8, 4, 4, 2) + 0.2)
boxplot(values ~ group, data = residNE_box_df, ylim = resid_lim, ylab = "Residuals", xlab = "",
        main = "NE Aus : Model Residuals",axes = FALSE, pch = 20, 
         cex.main = 2.25, cex.lab = 1.5, cex.axis = 1.5)
box()
axis(2)
axis(1, at = 1:32, labels = c(paste0("Week ", season_weeks)),
     las = 3, cex.axis = 1.6)
abline(h = 0, lty = 2)
abline(v = c(3.5, 8.5, 12.5, 17.5, 21.5), lty =2, col = "red")
text(1.5, -15, "Group 1", col = "red", cex =1)
text(6, -15, "Group 2", col = "red", cex = 1)
text(10.5, -15, "Group 3", col = "red", cex = 1)
text(15, -15, "Group 4", col = "red", cex = 1)
text(19.5, -15, "Group 5", col = "red", cex = 1)
text(25, -15, "Group 6", col = "red", cex = 1)
dev.off()


png("SEresidsd_out.png", width = 2250, height = 1250, res = 200)
par(mar = c(8, 4, 4, 2) + 0.2)
boxplot(values ~ group, data = residSE_box_df, ylim = resid_lim, ylab = "Residuals", xlab = "",
        main = "SE Aus : Model Residuals", axes = FALSE, pch = 20, 
         cex.main = 2.25, cex.lab = 1.5, cex.axis = 1.5)
box()
axis(2)
axis(1, at = 1:32, labels = c(paste0("Week ", season_weeks)),
     las = 3, cex.axis = 1.6)
abline(h = 0, lty = 2)
abline(v = c(3.5, 7.5, 16.5, 20.5), lty =2, col = "red")
text(1.5, -15, "Group 1", col = "red", cex = 1)
text(5.5, -15, "Group 2", col = "red", cex = 1)
text(12, -15, "Group 3", col = "red", cex = 1)
text(18.5, -15, "Group 4", col = "red", cex = 1)
text(24, -15, "Group 5", col = "red", cex = 1)
dev.off()

```

## RMSE

```{r in-sample}
#brought in from AGU_viz.rmd
NEgroup_list <- c(NEgroup1_list, NEgroup2_list, NEgroup3_list, NEgroup4_list, NEgroup5_list, NEgroup6_list)

SEgroup_list <- c(SEgroup1_list, SEgroup2_list, SEgroup3_list, SEgroup4_list, SEgroup5_list)

#TODO: add in rm() for both


#rmse
NE_rmse <- c()
SE_rmse <- c()
for (i in 1:32) {
  temp_NEresid <- NEgroup_list[[i]]$Resid
  temp_NErmse <- sqrt(mean(temp_NEresid^2))
  
  temp_SEresid <- SEgroup_list[[i]]$Resid
  temp_SErmse <- sqrt(mean(temp_SEresid^2))
  
  NE_rmse <- c(NE_rmse, temp_NErmse)
  SE_rmse <- c(SE_rmse, temp_SErmse)
}

#TODO: compare the following to simple linear model with var select 
plot(1:32, NE_rmse, type = "l", main = "NE Aus - RMSE")
plot(1:32, SE_rmse, type = "l", main = "SE Aus - RMSE")
```

## Scoring Validation

CPRS
Int Score 95\%

Do I need the bootstrap for this? Since we need a se.fit

```{r}
setwd("~/CO_AUS/Aus_CO-main")
source("predictionTest_functions.R")



```

