---
title: "new_lasso.rmd"
author: "Ryan Peterson"
date: "2025-02-20"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library}
#libraries
suppressMessages(library(genlasso)) #used for fused lasso 
suppressMessages(library(MASS)) #for matrix shenanigans in functions.
suppressMessages( library(glmnet)) #elastic net and relaxed

suppressMessages( library( fields))
```

```{r data_functions}
# Data Set-Up
setwd("~/CO_AUS/Aus_CO-main")

load( "ne_data.rda")
load( "se_data.rda")
load( "bounded_data.rda")
load( "data_matrix.rda")
load( "lag_list.rda")

source("group_functions.R")
source("lasso_valid_functions.R") #include predict.fusedlasso
source("genlasso_func.R") #includes cv.fusedlasso (DO NOT USE in final work, correct and move)
```

Redoing earlier work using modifications from meeting.

Changes:
1. Combines groups 
  - NE group 1,2,3 -> single group
  - SE group 1,2 -> single group
  
  Other Combinations
  - NE group 1 (old 1,2,3; new 1)
  - NE group 2 (new 2,3,4)
  
  - SE group 1 (old 1,2; new 1,2)
  - SE group 2 (new 3,4)

2. (other/placeholder)
  - More HierNet work

3. Relaxed Lasso fit
  - glmnet(,, relaxed = TRUE)
  
  
# New Response Groupings
  
```{r setup}
#center response data
NEbase_matrix <- scale(resp_matrix[ ,1:32], center = TRUE, scale = FALSE)
SEbase_matrix <- scale(resp_matrix[ ,33:64], center = TRUE, scale = FALSE)

#group response matrices
#NEAus
NEAus_1 <- NEbase_matrix[ ,1:12] #early season
NEAus_2 <- NEbase_matrix[ ,13:17] #primary NE fire season
NEAus_3 <- NEbase_matrix[ ,18:21] #feedback from SE
NEAus_4 <- NEbase_matrix[ ,22:32] #late season

#SEAus
SEAus_1 <- SEbase_matrix[ ,1:7] #early season
SEAus_2 <- SEbase_matrix[ ,8:16] #feedback from NE
SEAus_3 <- SEbase_matrix[ ,17:20] #primary SE fire season
SEAus_4 <- SEbase_matrix[ ,21:32] #late season

NEAus_mat <- list(NEAus_1, NEAus_2, NEAus_3, NEAus_4)
SEAus_mat <- list(SEAus_1, SEAus_2, SEAus_3, SEAus_4)

rm(NEAus_1, NEAus_2, NEAus_3, NEAus_4, SEAus_1, SEAus_2, SEAus_3, SEAus_4)
```



```{r}
# distance matrices
D <- getD1d(52)
empty_D <- matrix(rep(0, (52*51)) , ncol = 52, nrow = 51)

#Update for OLR (D5)
D1 <- cbind(D, empty_D, empty_D, empty_D, empty_D)
D2 <- cbind(empty_D, D, empty_D, empty_D, empty_D)
D3 <- cbind(empty_D, empty_D, D, empty_D, empty_D)
D4 <- cbind(empty_D, empty_D, empty_D, D, empty_D)
D5 <- cbind(empty_D, empty_D, empty_D, empty_D, D)

D_olr <- rbind(D1, D2, D3, D4, D5)

rm(D, empty_D, D1, D2, D3, D4, D5)
```


```{r}
#full model
NE_preds <- NElag_grouping(NE_laglist = NE_laglist_std, j = -c(19))
NE_resp <- NEresp_grouping(NEAus_mat = NEAus_mat, j = -c(19))

SE_preds <- SElag_grouping(SE_laglist = SE_laglist_std, j = -c(19))
SE_resp <- SEresp_grouping(SEAus_mat = SEAus_mat, j = -c(19))

#TODO: rebuild cv.fusedlasso to include all of our metrics since...

NE_gamma <- 0.75
NEfuse_grouplist <- list()
NEfuse_cv <- list()
NE_lambdamin <- c()

n <- length(NE_resp)
for (i in 1:n) {
  NEresp_temp <- NE_resp[[i]]
  NEpred_temp <- as.matrix(NE_preds[[i]][ ,1:260])
  
  NEgroup_temp <- fusedlasso(y = NEresp_temp, X = NEpred_temp, D_olr, gamma = NE_gamma)
  
  NEgroup_cv <- cv.fusedlasso(NEgroup_temp, k =5, D_olr) 
    
  NE_lambdamin <- c(NE_lambdamin, NEgroup_cv$lambda.min)  
  NEfuse_grouplist[[paste0("Group_", i)]] <- NEgroup_temp
  NEfuse_cv[[paste0("Group_", i)]] <- NEgroup_cv
}

SE_gamma <- 0.75
SEfuse_grouplist <- list()
SEfuse_cv <- list()
SE_lambdamin <- c()

n <- length(SE_resp)
for (i in 1:n) {
  SEresp_temp <- SE_resp[[i]]
  SEpred_temp <- as.matrix(SE_preds[[i]][ ,1:260])
  
  SEgroup_temp <- fusedlasso(y = SEresp_temp, X = SEpred_temp, D_olr, gamma = SE_gamma)
  
  SEgroup_cv <- cv.fusedlasso(SEgroup_temp, k =5, D_olr) 
  
  SE_lambdamin <- c(SE_lambdamin, SEgroup_cv$lambda.min) 
  SEfuse_grouplist[[paste0("Group_", i)]] <- SEgroup_temp
  SEfuse_cv[[paste0("Group_", i)]] <- SEgroup_cv
}
```

## Variations of Response Regions

### Additional Data Cleaning

```{r}
j = -c(19)

#prediction set-up
NE_laglist = NE_laglist_std

NEfull_lag <- NE_laglist[[1]][j, -(1:2)]
for (i in 2:length(NE_laglist)) {
  NEfull_lag <-  rbind(NEfull_lag, NE_laglist[[i]][j, -(1:2)])
}

SE_laglist = SE_laglist_std

SEfull_lag <- SE_laglist[[1]][j, -(1:2)]
for (i in 2:length(SE_laglist)) {
  SEfull_lag <-  rbind(SEfull_lag, SE_laglist[[i]][j, -(1:2)])
}

#response
NEfull_resp <- rbind(cbind(NE_resp[[1]]), cbind(NE_resp[[2]]), 
                     cbind(NE_resp[[3]]), cbind(NE_resp[[4]]))
SEfull_resp <- rbind(cbind(SE_resp[[1]]), cbind(SE_resp[[2]]), 
                     cbind(SE_resp[[3]]), cbind(SE_resp[[4]]))

#split response regions
NElag1 <- rbind(NE_preds[[1]])
NElag2 <- rbind(NE_preds[[2]], NE_preds[[3]], NE_preds[[4]])

SElag1 <- rbind(SE_preds[[1]], SE_preds[[2]])
SElag2 <- rbind(SE_preds[[3]], SE_preds[[4]])

NEresp1 <- NE_preds[[1]]
NEresp2 <- rbind(cbind(NE_resp[[2]]), cbind(NE_resp[[3]]), cbind(NE_resp[[4]]))
  
SEresp1 <- rbind(cbind(SE_resp[[1]]), cbind(SE_resp[[2]]))
SEresp2 <- rbind(cbind(SE_resp[[3]]), cbind(SE_resp[[4]]))

#TODO: update as a list.

```

### Full Response Season 

```{r full_response}
NE_gamma <- 0.75
NEfuse_grouplist <- list()
NEfuse_cv <- list()
NE_lambdamin <- c()
  
NEgroup_temp <- fusedlasso(y = NEfull_resp, X = as.matrix(NEfull_lag), D_olr, gamma = NE_gamma)
  
NEgroup_cv <- cv.fusedlasso(NEgroup_temp, k =5, D_olr) 
    
NE_lambdamin <- c(NE_lambdamin, NEgroup_cv$lambda.min)  
NEfuse_grouplist[[paste0("Group_", i)]] <- NEgroup_temp
NEfuse_cv[[paste0("Group_", i)]] <- NEgroup_cv


SE_gamma <- 0.75
SEfuse_grouplist <- list()
SEfuse_cv <- list()
SE_lambdamin <- c()

SEgroup_temp <- fusedlasso(y = SEfull_resp, X = as.matrix(SEfull_lag), D_olr, gamma = SE_gamma)
  
SEgroup_cv <- cv.fusedlasso(SEgroup_temp, k =5, D_olr) 
  
SE_lambdamin <- c(SE_lambdamin, SEgroup_cv$lambda.min) 
SEfuse_grouplist[[paste0("Group_", i)]] <- SEgroup_temp
SEfuse_cv[[paste0("Group_", i)]] <- SEgroup_cv


```

```{r repeat_coefs}
plot(NEfuse_cv[[1]])
plot(SEfuse_cv[[1]])

NE_coefs <- list()
#full coef list
NEfuse_coefs <- list()
NE_range <- c()

k <- 1

lambdaNE <- NE_lambdamin[[k]]
#lambda1 <- NEfuse_cv[[k]]$lambda.1se

NEgroup_coef <- coef(NEfuse_grouplist[[k]], lambda = lambdaNE)

NEfuse <- NEgroup_coef$beta
colnames(NEfuse) <- c("NEgroup")
NEfuse_coefs[[paste0("Group_", k)]] <- as.data.frame(NEfuse)

NE_range <- c(NE_range, range(NEgroup_coef$beta))

#extract each index
nino_coef <- NEgroup_coef$beta[1:52,]
dmi_coef <- NEgroup_coef$beta[53:104,]
tsa_coef <- NEgroup_coef$beta[105:156,]
aao_coef <- NEgroup_coef$beta[157:208,]
olr_coef <- NEgroup_coef$beta[209:260,]

NE_coefs[[paste0("Group_", k)]] <- data.frame(nino_coef, dmi_coef, tsa_coef, aao_coef, olr_coef)

#SE Visualizations
SE_coefs <- list()
#full coef list
SEfuse_coefs <- list()

SE_range <- c()

lambdaSE <- SE_lambdamin[k]

SEgroup_coef <- coef(SEfuse_grouplist[[k]], lambda = lambdaSE)

SEfuse <- SEgroup_coef$beta
colnames(SEfuse) <- c("SEgroup")
SEfuse_coefs[[paste0("Group_", k)]] <- as.data.frame(SEfuse)

SE_range <- c(SE_range, range(SEgroup_coef$beta))

#extract each index
nino_coef <- SEgroup_coef$beta[1:52, ]
dmi_coef <- SEgroup_coef$beta[53:104, ]
tsa_coef <- SEgroup_coef$beta[105:156, ]
aao_coef <- SEgroup_coef$beta[157:208, ]
olr_coef <- SEgroup_coef$beta[209:260, ]

SE_coefs[[paste0("Group_", k)]] <- data.frame(nino_coef, dmi_coef, tsa_coef, aao_coef, olr_coef)
  


```

```{r coef_viz}
par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, NE_coefs$Group_1$nino_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "NE Aus : Coefficients", ylim = NE_range, 
     col = "darkmagenta", lwd = 1.5)
lines(1:52, NE_coefs$Group_1$dmi_coef, col = "blue", lwd = 1.5)
lines(1:52, NE_coefs$Group_1$tsa_coef, col = "red", lwd = 1.5)
lines(1:52, NE_coefs$Group_1$aao_coef, col = "darkgreen", lwd = 1.5)
lines(1:52, NE_coefs$Group_1$olr_coef, col = "orange3", lwd = 1.5)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = legend2_names,
       col = legend2_col, 
       lty = legend2_lty, lwd = 2, bty = "o") #, bg = "white")


par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, SE_coefs$Group_1$nino_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "SE Aus : Coefficients", ylim = SE_range, 
     col = "darkmagenta", lwd = 1.5)
lines(1:52, SE_coefs$Group_1$dmi_coef, col = "blue", lwd = 1.5)
lines(1:52, SE_coefs$Group_1$tsa_coef, col = "red", lwd = 1.5)
lines(1:52, SE_coefs$Group_1$aao_coef, col = "darkgreen", lwd = 1.5)
lines(1:52, SE_coefs$Group_1$olr_coef, col = "orange3", lwd = 1.5)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = legend2_names,
       col = legend2_col, 
       lty = legend2_lty, lwd = 2, bty = "o") #, bg = "white")
```

```{r preds}
j <- 19
SEresp_test <- SEbase_matrix[j,]
#NEresp_test <- NEbase_matrix[j, ]

season_range <- range(SEresp_test)

#group 1 preds
se_group <- c()
for(i in 1:32) {
  pred_out <- as.matrix(SE_laglist_std[[i]][j,-c(1,2)])
  coef_out <- c(SE_coefs$Group_1$nino_coef, SE_coefs$Group_1$dmi_coef,
              SE_coefs$Group_1$tsa_coef, SE_coefs$Group_1$aao_coef,
              SE_coefs$Group_1$olr_coef)
  se_group <-  c(se_group, pred_out %*% coef_out)
}

plot(1:32, SEresp_test, type = "l", ylim = season_range, main = "SE Aus - Preds")
lines(1:32, se_group, col = "magenta3")
abline(h = 0, lty = 2)



NEresp_test <- NEbase_matrix[j, ]

season_range <- range(NEresp_test)

#group 1 preds
ne_group <- c()
for(i in 1:32) {
  pred_out <- as.matrix(NE_laglist_std[[i]][j,-c(1,2)])
  coef_out <- c(NE_coefs$Group_1$nino_coef, NE_coefs$Group_1$dmi_coef,
              NE_coefs$Group_1$tsa_coef, NE_coefs$Group_1$aao_coef,
              NE_coefs$Group_1$olr_coef)
  ne_group <-  c(ne_group, pred_out %*% coef_out)
}

plot(1:32, NEresp_test, type = "l", ylim = season_range, main = "SE Aus - Preds")
lines(1:32, ne_group, col = "magenta3")
abline(h = 0, lty = 2)

```

### Split Response Season

```{r split_response}

```


## Previous Coeffs

```{r}
#NE Aus
plot(NEfuse_cv[[1]])
plot(NEfuse_cv[[2]])
plot(NEfuse_cv[[3]])
plot(NEfuse_cv[[4]])



#SE Aus
plot(SEfuse_cv[[1]])
plot(SEfuse_cv[[2]]) #use one stand error
plot(SEfuse_cv[[3]])
plot(SEfuse_cv[[4]])


```


```{r coef_setup}
#NE Visualizations
NE_coefs <- list()
#full coef list
NEfuse_coefs <- list()
NE_range <- c()

for(k in 1:length(NEfuse_grouplist)){

  lambda1 <- NE_lambdamin[[k]]
  #lambda1 <- NEfuse_cv[[k]]$lambda.1se
  
  NEgroup_coef <- coef(NEfuse_grouplist[[k]], lambda = lambda1)
  
  NEfuse <- NEgroup_coef$beta
  colnames(NEfuse) <- c("NEgroup")
  NEfuse_coefs[[paste0("Group_", k)]] <- as.data.frame(NEfuse)
  
  NE_range <- c(NE_range, range(NEgroup_coef$beta))

  #extract each index
  nino_coef <- NEgroup_coef$beta[1:52,]
  dmi_coef <- NEgroup_coef$beta[53:104,]
  tsa_coef <- NEgroup_coef$beta[105:156,]
  aao_coef <- NEgroup_coef$beta[157:208,]
  olr_coef <- NEgroup_coef$beta[209:260,]
  
  NE_coefs[[paste0("Group_", k)]] <- data.frame(nino_coef, dmi_coef, tsa_coef, aao_coef, olr_coef)
}


#SE Visualizations
SE_coefs <- list()
#full coef list
SEfuse_coefs <- list()

SE_range <- c()

for(k in 1:length(SEfuse_grouplist)){

  lambda1 <- SE_lambdamin[k]
  
  SEgroup_coef <- coef(SEfuse_grouplist[[k]], lambda = lambda1)
  
  SEfuse <- SEgroup_coef$beta
  colnames(SEfuse) <- c("SEgroup")
  SEfuse_coefs[[paste0("Group_", k)]] <- as.data.frame(SEfuse)
  
  SE_range <- c(SE_range, range(SEgroup_coef$beta))
  
  #extract each index
  nino_coef <- SEgroup_coef$beta[1:52, ]
  dmi_coef <- SEgroup_coef$beta[53:104, ]
  tsa_coef <- SEgroup_coef$beta[105:156, ]
  aao_coef <- SEgroup_coef$beta[157:208, ]
  olr_coef <- SEgroup_coef$beta[209:260, ]
  
  SE_coefs[[paste0("Group_", k)]] <- data.frame(nino_coef, dmi_coef, tsa_coef, aao_coef, olr_coef)
  
}

#for base preds (indices)
legend1_names <- c("Nino",  "DMI", "TSA", "AAO")
legend1_col <- c("darkmagenta", "blue", "red", "darkgreen")
legend1_lty <- rep(1, length.out = 4)

#with olr
legend2_names <- c("Nino",  "DMI", "TSA", "AAO", "OLR")
legend2_col <- c("darkmagenta", "blue", "red", "darkgreen", "orange3")
legend2_lty <- rep(1, length.out = 5)

#group 
legend3_names <- c("Group 1",  "Group 2", "Group 3", 
                   "Group 4")
legend3_col <- c("red2","green4", "blue2", "orange3")
legend3_lty <- rep(1, length.out = 4)

#coefs ranges
#nino
NEnino_range <- range(NE_coefs$Group_1$nino_coef,
                    NE_coefs$Group_2$nino_coef,
                    NE_coefs$Group_3$nino_coef,
                    NE_coefs$Group_4$nino_coef,
                    NE_coefs$Group_5$nino_coef,
                    NE_coefs$Group_6$nino_coef)
SEnino_range <- range(SE_coefs$Group_1$nino_coef,
                    SE_coefs$Group_2$nino_coef,
                    SE_coefs$Group_3$nino_coef,
                    SE_coefs$Group_4$nino_coef,
                    SE_coefs$Group_5$nino_coef)


nino_range <- range(NEnino_range, SEnino_range)

#dmi 
NEdmi_range <- range(NE_coefs$Group_1$dmi_coef,
                    NE_coefs$Group_2$dmi_coef,
                    NE_coefs$Group_3$dmi_coef,
                    NE_coefs$Group_4$dmi_coef,
                    NE_coefs$Group_5$dmi_coef,
                    NE_coefs$Group_6$dmi_coef)
SEdmi_range <- range(SE_coefs$Group_1$dmi_coef,
                    SE_coefs$Group_2$dmi_coef,
                    SE_coefs$Group_3$dmi_coef,
                    SE_coefs$Group_4$dmi_coef,
                    SE_coefs$Group_5$dmi_coef)

dmi_range <- range(NEdmi_range, SEdmi_range)

#tsa
NEtsa_range <- range(NE_coefs$Group_1$tsa_coef,
                    NE_coefs$Group_2$tsa_coef,
                    NE_coefs$Group_3$tsa_coef,
                    NE_coefs$Group_4$tsa_coef,
                    NE_coefs$Group_5$tsa_coef,
                    NE_coefs$Group_6$tsa_coef)
SEtsa_range <- range(SE_coefs$Group_1$tsa_coef,
                    SE_coefs$Group_2$tsa_coef,
                    SE_coefs$Group_3$tsa_coef,
                    SE_coefs$Group_4$tsa_coef,
                    SE_coefs$Group_5$tsa_coef)

tsa_range <- range(NEtsa_range, SEtsa_range)

#aao
NEaao_range <- range(NE_coefs$Group_1$aao_coef,
                    NE_coefs$Group_2$aao_coef,
                    NE_coefs$Group_3$aao_coef,
                    NE_coefs$Group_4$aao_coef,
                    NE_coefs$Group_5$aao_coef,
                    NE_coefs$Group_6$aao_coef)
SEaao_range <- range(SE_coefs$Group_1$aao_coef,
                    SE_coefs$Group_2$aao_coef,
                    SE_coefs$Group_3$aao_coef,
                    SE_coefs$Group_4$aao_coef,
                    SE_coefs$Group_5$aao_coef)

aao_range <- range(NEaao_range, SEaao_range)


#olr
NEolr_range <- range(NE_coefs$Group_1$olr_coef,
                    NE_coefs$Group_2$olr_coef,
                    NE_coefs$Group_3$olr_coef,
                    NE_coefs$Group_4$olr_coef,
                    NE_coefs$Group_5$olr_coef,
                    NE_coefs$Group_6$olr_coef)
SEolr_range <- range(SE_coefs$Group_1$olr_coef,
                    SE_coefs$Group_2$olr_coef,
                    SE_coefs$Group_3$olr_coef,
                    SE_coefs$Group_4$olr_coef,
                    SE_coefs$Group_5$olr_coef)

olr_range <- range(NEolr_range, SEolr_range)

```


```{r base_vis}
#nino vis
par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, NE_coefs$Group_1$nino_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "NE Aus : Nino Coefficients", ylim = range(nino_range), 
     col = "red2", lwd = 1.5)
lines(1:52, NE_coefs$Group_2$nino_coef, col = "green4", lwd = 1.5)
lines(1:52, NE_coefs$Group_3$nino_coef, col = "blue2", lwd = 1.5)
lines(1:52, NE_coefs$Group_4$nino_coef, col = "orange3", lwd = 1.5)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = legend3_names,
       col = legend3_col, 
       lty = legend3_lty, lwd = 2, bty = "o") #, bg = "white")

par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, SE_coefs$Group_1$nino_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "SE Aus : Nino Coefficients", ylim = range(nino_range), 
     col = "red2", lwd = 1.5)
lines(1:52, SE_coefs$Group_2$nino_coef, col = "green4", lwd = 1.5)
lines(1:52, SE_coefs$Group_3$nino_coef, col = "blue2", lwd = 1.5)
lines(1:52, SE_coefs$Group_4$nino_coef, col = "orange3", lwd = 1.5)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = legend3_names[1:4],
       col = legend3_col[1:4], 
       lty = legend3_lty[1:4], lwd = 2, bty = "o") #, bg = "white")


#dmi vis
par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, NE_coefs$Group_1$dmi_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "NE Aus : DMI Coefficients", ylim = range(dmi_range), 
     col = "red2", lwd = 1.5)
lines(1:52, NE_coefs$Group_2$dmi_coef, col = "green4", lwd = 1.5)
lines(1:52, NE_coefs$Group_3$dmi_coef, col = "blue2", lwd = 1.5)
lines(1:52, NE_coefs$Group_4$dmi_coef, col = "orange3", lwd = 1.5)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = legend3_names,
       col = legend3_col, 
       lty = legend3_lty, lwd = 2, bty = "o") #, bg = "white")

par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, SE_coefs$Group_1$dmi_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "SE Aus : DMI Coefficients", ylim = range(dmi_range), 
     col = "red2", lwd = 1.5)
lines(1:52, SE_coefs$Group_2$dmi_coef, col = "green4", lwd = 1.5)
lines(1:52, SE_coefs$Group_3$dmi_coef, col = "blue2", lwd = 1.5)
lines(1:52, SE_coefs$Group_4$dmi_coef, col = "orange3", lwd = 1.5)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = legend3_names[1:4],
       col = legend3_col[1:4], 
       lty = legend3_lty[1:4], lwd = 2, bty = "o") #, bg = "white")



par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, NE_coefs$Group_1$tsa_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "NE Aus : TSA Coefficients", ylim = range(tsa_range), 
     col = "red2", lwd = 1.5)
lines(1:52, NE_coefs$Group_2$tsa_coef, col = "green4", lwd = 1.5)
lines(1:52, NE_coefs$Group_3$tsa_coef, col = "blue2", lwd = 1.5)
lines(1:52, NE_coefs$Group_4$tsa_coef, col = "orange3", lwd = 1.5)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = legend3_names,
       col = legend3_col, 
       lty = legend3_lty, lwd = 2, bty = "o") #, bg = "white")

par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, SE_coefs$Group_1$tsa_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "SE Aus : TSA Coefficients", ylim = range(tsa_range), 
     col = "red2", lwd = 1.5)
lines(1:52, SE_coefs$Group_2$tsa_coef, col = "green4", lwd = 1.5)
lines(1:52, SE_coefs$Group_3$tsa_coef, col = "blue2", lwd = 1.5)
lines(1:52, SE_coefs$Group_4$tsa_coef, col = "orange3", lwd = 1.5)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = legend3_names[1:4],
       col = legend3_col[1:4], 
       lty = legend3_lty[1:4], lwd = 2, bty = "o") #, bg = "white")

#aao viz
par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, NE_coefs$Group_1$aao_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "NE Aus : AAO Coefficients", ylim = range(aao_range), 
     col = "red2", lwd = 1.5)
lines(1:52, NE_coefs$Group_2$aao_coef, col = "green4", lwd = 1.5)
lines(1:52, NE_coefs$Group_3$aao_coef, col = "blue2", lwd = 1.5)
lines(1:52, NE_coefs$Group_4$aao_coef, col = "orange3", lwd = 1.5)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = legend3_names,
       col = legend3_col, 
       lty = legend3_lty, lwd = 2, bty = "o") #, bg = "white")

par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, SE_coefs$Group_1$aao_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "SE Aus : AAO Coefficients", ylim = range(aao_range), 
     col = "red2", lwd = 1.5)
lines(1:52, SE_coefs$Group_2$aao_coef, col = "green4", lwd = 1.5)
lines(1:52, SE_coefs$Group_3$aao_coef, col = "blue2", lwd = 1.5)
lines(1:52, SE_coefs$Group_4$aao_coef, col = "orange3", lwd = 1.5)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = legend3_names[1:4],
       col = legend3_col[1:4], 
       lty = legend3_lty[1:4], lwd = 2, bty = "o") #, bg = "white")


par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, NE_coefs$Group_1$olr_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "NE Aus : OLR Coefficients", ylim = range(olr_range), 
     col = "red2", lwd = 1.5, cex.main = 2.25, cex.lab = 1.5, cex.axis = 1.5)
lines(1:52, NE_coefs$Group_2$olr_coef, col = "green4", lwd = 1.5)
lines(1:52, NE_coefs$Group_3$olr_coef, col = "blue2", lwd = 1.5)
lines(1:52, NE_coefs$Group_4$olr_coef, col = "orange3", lwd = 1.5)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.2, 0),
       legend = legend3_names,
       col = legend3_col, 
       lty = legend3_lty, lwd = 2, bty = "o", cex = 1.3) #, bg = "white")

par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, SE_coefs$Group_1$olr_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "SE Aus : OLR Coefficients", ylim = range(olr_range), 
     col = "red2", lwd = 1.5,  cex.main = 2.25, cex.lab = 1.5, cex.axis = 1.5)
lines(1:52, SE_coefs$Group_2$olr_coef, col = "green4", lwd = 1.5)
lines(1:52, SE_coefs$Group_3$olr_coef, col = "blue2", lwd = 1.5)
lines(1:52, SE_coefs$Group_4$olr_coef, col = "orange3", lwd = 1.5)
legend("topright", inset = c(-0.3, 0),
       legend = legend3_names[1:4],
       col = legend3_col[1:4], 
       lty = legend3_lty[1:4], lwd = 2, bty = "o", cex = 1.3) #, bg = "white")

```


```{r group_vis}
par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, SE_coefs$Group_1$nino_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "SE Aus : Group 1 Coefficients", ylim = SE_range, 
     col = "darkmagenta", lwd = 1.5)
lines(1:52, SE_coefs$Group_1$dmi_coef, col = "blue", lwd = 1.5)
lines(1:52, SE_coefs$Group_1$tsa_coef, col = "red", lwd = 1.5)
lines(1:52, SE_coefs$Group_1$aao_coef, col = "darkgreen", lwd = 1.5)
lines(1:52, SE_coefs$Group_1$olr_coef, col = "orange3", lwd = 1.5)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = legend2_names,
       col = legend2_col, 
       lty = legend2_lty, lwd = 2, bty = "o") #, bg = "white")

par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, SE_coefs$Group_2$nino_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "SE Aus : Group 2 Coefficients", ylim = range(SE_coefs$Group_2), 
     col = "darkmagenta", lwd = 1.5)
lines(1:52, SE_coefs$Group_2$dmi_coef, col = "blue", lwd = 1.5)
lines(1:52, SE_coefs$Group_2$tsa_coef, col = "red", lwd = 1.5)
lines(1:52, SE_coefs$Group_2$aao_coef, col = "darkgreen", lwd = 1.5)
lines(1:52, SE_coefs$Group_2$olr_coef, col = "orange3", lwd = 1.5)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = legend2_names,
       col = legend2_col, 
       lty = legend2_lty, lwd = 2, bty = "o") #, bg = "white")

par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, SE_coefs$Group_3$nino_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "SE Aus : Group 3 Coefficients", ylim = range(SE_coefs$Group_3), 
     col = "darkmagenta", lwd = 1.5)
lines(1:52, SE_coefs$Group_3$dmi_coef, col = "blue", lwd = 1.5)
lines(1:52, SE_coefs$Group_3$tsa_coef, col = "red", lwd = 1.5)
lines(1:52, SE_coefs$Group_3$aao_coef, col = "darkgreen", lwd = 1.5)
lines(1:52, SE_coefs$Group_3$olr_coef, col = "orange3", lwd = 1.5)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = legend2_names,
       col = legend2_col, 
       lty = legend2_lty, lwd = 2, bty = "o") #, bg = "white")

par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, SE_coefs$Group_4$nino_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "SE Aus : Group 4 Coefficients", ylim = range(SE_coefs$Group_4), 
     col = "darkmagenta", lwd = 1.5)
lines(1:52, SE_coefs$Group_4$dmi_coef, col = "blue", lwd = 1.5)
lines(1:52, SE_coefs$Group_4$tsa_coef, col = "red", lwd = 1.5)
lines(1:52, SE_coefs$Group_4$aao_coef, col = "darkgreen", lwd = 1.5)
lines(1:52, SE_coefs$Group_4$olr_coef, col = "orange3", lwd = 1.5)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = legend2_names,
       col = legend2_col, 
       lty = legend2_lty, lwd = 2, bty = "o") #, bg = "white")

```


# 2 Predictions and Prediction "Fields"

```{r prediction}
#in-sample predictions of peak years
j <- 12
SEresp_test <- SEbase_matrix[j,]
NEresp_test <- NEbase_matrix[j, ]

season_range <- range(SEresp_test, NEresp_test)

plot(1:32, NEresp_test, type = "l", ylim = season_range)
lines(1:32, SEresp_test, col = "magenta3")
xline(c(13,16.9), lty = 2, col = "red3")
xline(c(17.1,20), lty = 2, col = "blue3")
abline(h = 0, lty = 2)

```


```{r}
#Prediction test for insample 2003
j <- 12
SEresp_test <- SEbase_matrix[j,]
#NEresp_test <- NEbase_matrix[j, ]

season_range <- range(SEresp_test)

#group 1 preds
se_group1 <- c()
for(i in 1:7) {
  pred_out <- as.matrix(SE_laglist_std[[i]][j,-c(1,2)])
  coef_out <- c(SE_coefs$Group_1$nino_coef, SE_coefs$Group_1$dmi_coef,
              SE_coefs$Group_1$tsa_coef, SE_coefs$Group_1$aao_coef,
              SE_coefs$Group_1$olr_coef)
  se_group1 <-  c(se_group1, pred_out %*% coef_out)
}



plot(1:7, SEresp_test[1:7], type = "l", ylim = season_range, main = "SE Aus - Group 1 Preds")
lines(1:7, se_group1, col = "magenta3")
abline(h = 0, lty = 2)

#se group 2
se_group2 <- c()
for(i in 8:16) {
  pred_out <- as.matrix(SE_laglist_std[[i]][j,-c(1,2)])
  coef_out <- c(SE_coefs$Group_2$nino_coef, SE_coefs$Group_2$dmi_coef,
              SE_coefs$Group_2$tsa_coef, SE_coefs$Group_2$aao_coef,
              SE_coefs$Group_2$olr_coef)
  se_group2 <-  c(se_group2, pred_out %*% coef_out)
}


plot(1:9, SEresp_test[8:16], type = "l", ylim = season_range, main = "SE Aus - Group 2 Preds")
lines(1:9, se_group2, col = "magenta3")
abline(h = 0, lty = 2)


#se group 3
se_group3 <- c()
for(i in 17:20) {
  pred_out <- as.matrix(SE_laglist_std[[i]][j,-c(1,2)])
  coef_out <- c(SE_coefs$Group_3$nino_coef, SE_coefs$Group_3$dmi_coef,
              SE_coefs$Group_3$tsa_coef, SE_coefs$Group_3$aao_coef,
              SE_coefs$Group_3$olr_coef)
  se_group3 <-  c(se_group3, pred_out %*% coef_out)
}


plot(1:4, SEresp_test[17:20], type = "l", ylim = season_range, main = "SE Aus - Group 3 Preds")
lines(1:4, se_group3, col = "magenta3")
abline(h = 0, lty = 2)


#se group 4
se_group4 <- c()
for(i in 21:32) {
  pred_out <- as.matrix(SE_laglist_std[[i]][j,-c(1,2)])
  coef_out <- c(SE_coefs$Group_4$nino_coef, SE_coefs$Group_4$dmi_coef,
              SE_coefs$Group_4$tsa_coef, SE_coefs$Group_4$aao_coef,
              SE_coefs$Group_4$olr_coef)
  se_group4 <-  c(se_group4, pred_out %*% coef_out)
}


plot(1:12, SEresp_test[21:32], type = "l", ylim = season_range, main = "SE Aus - Group 4 Preds")
lines(1:12, se_group4, col = "magenta3")
abline(h = 0, lty = 2)


```

```{r}
#TODO: explore the listed years coeffs and other relationship in the data and model.
```



```{r pred_fields}
#testing my idea on prediction fields where all possible values of certain lags are given on an axis
#TODO: test on NE group 2 (weeks 47-51) and low Nino/Dmi lag (Nino: 1-5, DMI: 1-5)
#lag 1
nino1_range <- range(NE_preds[[2]]$nino_lag1)
dmi1_range <- range(NE_preds[[2]]$dmi_lag1)

#lag 2
nino2_range <- range(NE_preds[[2]]$nino_lag2)
dmi2_range <- range(NE_preds[[2]]$dmi_lag2)

#lag 3
nino3_range <- range(NE_preds[[2]]$nino_lag3)
dmi3_range <- range(NE_preds[[2]]$dmi_lag3)

#lag 3
nino4_range <- range(NE_preds[[2]]$nino_lag4)
dmi4_range <- range(NE_preds[[2]]$dmi_lag4)


#lag coef
j <- 3
k <- 4
nino_beta <- NE_coefs$Group_2$nino_coef[j]
dmi_beta <- NE_coefs$Group_2$dmi_coef[k]

#nino_seq <- 
#dmi_seq <-

out <-  outer(seq(nino3_range[1], nino3_range[2], ,20) * nino_beta ,
              seq(dmi4_range[1], dmi4_range[2], ,20) * dmi_beta, "+")

image.plot(out, xlab = "Nino", ylab = "DMI")

#diag(out)
```


## Coeff Analysis with 2019/2020 Data


```{r fusedlasso_loop}

SE_preds <- SElag_grouping(SE_laglist = SE_laglist_std, j = 1:19)
SE_resp <- SEresp_grouping(SEAus_mat = SEAus_mat, j = 1:19)


SE_gamma <- 0.75
SEfuse_grouplist_new <- list()
SEfuse_cv_new <- list()
SE_lambdamin_new <- c()

n <- length(SE_resp)
for (i in 1:n) {
  SEresp_temp <- SE_resp[[i]]
  SEpred_temp <- as.matrix(SE_preds[[i]][ ,1:260])
  
  SEgroup_temp <- fusedlasso(y = SEresp_temp, X = SEpred_temp, D_olr, gamma = SE_gamma)
  
  SEgroup_cv <- cv.fusedlasso(SEgroup_temp, k =5, D_olr) 
  
  SE_lambdamin_new <- c(SE_lambdamin_new, SEgroup_cv$lambda.min) 
  SEfuse_grouplist_new[[paste0("Group_", i)]] <- SEgroup_temp
  SEfuse_cv_new[[paste0("Group_", i)]] <- SEgroup_cv
}


NE_preds <- NElag_grouping(NE_laglist = NE_laglist_std, j = 1:19)
NE_resp <- NEresp_grouping(NEAus_mat = NEAus_mat, j = 1:19)


NE_gamma <- 0.75
NEfuse_grouplist_new <- list()
NEfuse_cv_new <- list()
NE_lambdamin_new <- c()

n <- length(NE_resp)
for (i in 1:n) {
  NEresp_temp <- NE_resp[[i]]
  NEpred_temp <- as.matrix(NE_preds[[i]][ ,1:260])
  
  NEgroup_temp <- fusedlasso(y = NEresp_temp, X = NEpred_temp, D_olr, gamma = NE_gamma)
  
  NEgroup_cv <- cv.fusedlasso(NEgroup_temp, k =5, D_olr) 
  
  NE_lambdamin_new <- c(NE_lambdamin_new, NEgroup_cv$lambda.min) 
  NEfuse_grouplist_new[[paste0("Group_", i)]] <- NEgroup_temp
  NEfuse_cv_new[[paste0("Group_", i)]] <- NEgroup_cv
}
```


```{r lambdaCV_check}
#NE Aus
plot(NEfuse_cv_new[[1]])
plot(NEfuse_cv_new[[2]])
plot(NEfuse_cv_new[[3]])
plot(NEfuse_cv_new[[4]])



#SE Aus
plot(SEfuse_cv_new[[1]])
plot(SEfuse_cv_new[[2]]) #use one stand error
plot(SEfuse_cv_new[[3]])
plot(SEfuse_cv_new[[4]])
```

### SE Aus with Nino/DMI

```{r get_coefs}

#SE Visualizations
SEcoefs_new <- list()
#full coef list
SEfusecoefs_new <- list()

SErange_new <- c()

for(k in 1:length(SEfuse_grouplist_new)){

  lambda1 <- SE_lambdamin_new[k]
  
  SEgroup_coef <- coef(SEfuse_grouplist_new[[k]], lambda = lambda1)
  
  SEfuse <- SEgroup_coef$beta
  colnames(SEfuse) <- c("SEgroup")
  SEfusecoefs_new[[paste0("Group_", k)]] <- as.data.frame(SEfuse)
  
  SErange_new <- c(SErange_new, range(SEgroup_coef$beta))
  
  #extract each index
  nino_coef <- SEgroup_coef$beta[1:52, ]
  dmi_coef <- SEgroup_coef$beta[53:104, ]
  tsa_coef <- SEgroup_coef$beta[105:156, ]
  aao_coef <- SEgroup_coef$beta[157:208, ]
  olr_coef <- SEgroup_coef$beta[209:260, ]
  
  SEcoefs_new[[paste0("Group_", k)]] <- data.frame(nino_coef, dmi_coef, tsa_coef, aao_coef, olr_coef)
  
}


#for base preds (indices)
new_names <- c("Nino",  "DMI", "Nino-Full", "DMI-Full")
new_col <- c("magenta3", "cyan4", "magenta4", "blue1")
new_lty <- c(1,1,2,2)

SEgroup1_new <- range(SE_coefs$Group_1$nino_coef,
                      SE_coefs$Group_1$dmi_coef,
                      SEcoefs_new$Group_1$nino_coef,
                      SEcoefs_new$Group_1$dmi_coef)

SEgroup2_new <- range(SE_coefs$Group_2$nino_coef,
                      SE_coefs$Group_2$dmi_coef,
                      SEcoefs_new$Group_2$nino_coef,
                      SEcoefs_new$Group_2$dmi_coef)

SEgroup3_new <- range(SE_coefs$Group_3$nino_coef,
                      SE_coefs$Group_3$dmi_coef,
                      SEcoefs_new$Group_3$nino_coef,
                      SEcoefs_new$Group_3$dmi_coef)

SEgroup4_new <- range(SE_coefs$Group_4$nino_coef,
                      SE_coefs$Group_4$dmi_coef,
                      SEcoefs_new$Group_4$nino_coef,
                      SEcoefs_new$Group_4$dmi_coef)


```


```{r compare_coefs}

#SE group comparison between model w/o and w/ 2019-2020 wildfire season

par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, SE_coefs$Group_1$nino_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "SE Aus : Group 1 Coefficients", ylim = range(SEgroup1_new), 
     col = "magenta3", lwd = 1.5)
lines(1:52, SE_coefs$Group_1$dmi_coef, col = "cyan4", lwd = 1.5)
lines(1:52, SEcoefs_new$Group_1$nino_coef, col = "magenta4", lwd = 1.5, lty = 2)
lines(1:52, SEcoefs_new$Group_1$dmi_coef, col = "blue1", lwd = 1.5, lty = 2)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = new_names,
       col = new_col, 
       lty = new_lty, lwd = 2, bty = "o") #, bg = "white")

par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, SE_coefs$Group_2$nino_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "SE Aus : Group 2 Coefficients", ylim = range(SEgroup2_new), 
     col = "magenta3", lwd = 1.5)
lines(1:52, SE_coefs$Group_2$dmi_coef, col = "cyan4", lwd = 1.5)
lines(1:52, SEcoefs_new$Group_2$nino_coef, col = "magenta4", lwd = 1.5, lty = 2)
lines(1:52, SEcoefs_new$Group_2$dmi_coef, col = "blue1", lwd = 1.5, lty = 2)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = new_names,
       col = new_col, 
       lty = new_lty, lwd = 2, bty = "o") #, bg = "white")

#TODO: repeat this plot later on but only lag 0-15
par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, SE_coefs$Group_3$nino_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "SE Aus : Group 3 Coefficients", ylim = range(SEgroup3_new), 
     col = "magenta3", lwd = 1.5)
lines(1:52, SE_coefs$Group_3$dmi_coef, col = "cyan4", lwd = 1.5)
lines(1:52, SEcoefs_new$Group_3$nino_coef, col = "magenta4", lwd = 1.5, lty = 2)
lines(1:52, SEcoefs_new$Group_3$dmi_coef, col = "blue1", lwd = 1.5, lty = 2)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = new_names,
       col = new_col, 
       lty = new_lty, lwd = 2, bty = "o") #, bg = "white")



par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, SE_coefs$Group_4$nino_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "SE Aus : Group 4 Coefficients", ylim = range(SEgroup4_new),
     col = "magenta3", lwd = 1.5)
lines(1:52, SE_coefs$Group_4$dmi_coef, col = "cyan4", lwd = 1.5)
lines(1:52, SEcoefs_new$Group_4$nino_coef, col = "magenta4", lwd = 1.5, lty = 2)
lines(1:52, SEcoefs_new$Group_4$dmi_coef, col = "blue1", lwd = 1.5, lty = 2)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = new_names,
       col = new_col, 
       lty = new_lty, lwd = 2, bty = "o") #, bg = "white")



```


### NE Aus with Nino/DMI

```{r}

#NE Visualizations
NEcoefs_new <- list()
#full coef list
NEfusecoefs_new <- list()

NErange_new <- c()

for(k in 1:length(NEfuse_grouplist_new)){

  lambda1 <- NE_lambdamin_new[k]
  
  NEgroup_coef <- coef(NEfuse_grouplist_new[[k]], lambda = lambda1)
  
  NEfuse <- NEgroup_coef$beta
  colnames(NEfuse) <- c("NEgroup")
  NEfusecoefs_new[[paste0("Group_", k)]] <- as.data.frame(NEfuse)
  
  NErange_new <- c(NErange_new, range(NEgroup_coef$beta))
  
  #extract each index
  nino_coef <- NEgroup_coef$beta[1:52, ]
  dmi_coef <- NEgroup_coef$beta[53:104, ]
  tsa_coef <- NEgroup_coef$beta[105:156, ]
  aao_coef <- NEgroup_coef$beta[157:208, ]
  olr_coef <- NEgroup_coef$beta[209:260, ]
  
  NEcoefs_new[[paste0("Group_", k)]] <- data.frame(nino_coef, dmi_coef, tsa_coef, aao_coef, olr_coef)
  
}

new2_names <- c("Nino",  "DMI", "TSA", "Nino-Full", "DMI-Full", "TSA-Full")
new2_col <- c("magenta3", "cyan4", "orange3", "magenta4", "blue1", "darkorange")
new2_lty <- c(1,1,1,2,2,2)

NEgroup1_new <- range(NE_coefs$Group_1$nino_coef,
                      NE_coefs$Group_1$dmi_coef,
                      NE_coefs$Group_1$tsa_coef,
                      NEcoefs_new$Group_1$nino_coef,
                      NEcoefs_new$Group_1$dmi_coef,
                      NEcoefs_new$Group_1$tsa_coef)

NEgroup2_new <- range(NE_coefs$Group_2$nino_coef,
                      NE_coefs$Group_2$dmi_coef,
                      NE_coefs$Group_2$tsa_coef,
                      NEcoefs_new$Group_2$nino_coef,
                      NEcoefs_new$Group_2$dmi_coef,
                      NEcoefs_new$Group_2$tsa_coef)

NEgroup3_new <- range(NE_coefs$Group_3$nino_coef,
                      NE_coefs$Group_3$dmi_coef,
                      NE_coefs$Group_3$tsa_coef,
                      NEcoefs_new$Group_3$nino_coef,
                      NEcoefs_new$Group_3$dmi_coef,
                      NEcoefs_new$Group_3$tsa_coef)

NEgroup4_new <- range(NE_coefs$Group_4$nino_coef,
                      NE_coefs$Group_4$dmi_coef,
                      NE_coefs$Group_4$tsa_coef,
                      NEcoefs_new$Group_4$nino_coef,
                      NEcoefs_new$Group_4$dmi_coef,
                      NEcoefs_new$Group_4$tsa_coef)

```


```{r}

par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, NE_coefs$Group_1$nino_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "NE Aus : Group 1 Coefficients", ylim = range(NEgroup1_new), 
     col = "magenta3", lwd = 1.5)
lines(1:52, NE_coefs$Group_1$dmi_coef, col = "cyan4", lwd = 1.5)
lines(1:52, NE_coefs$Group_1$tsa_coef, col = "orange3", lwd = 1.5)
lines(1:52, NEcoefs_new$Group_1$nino_coef, col = "magenta4", lwd = 1.5, lty = 2)
lines(1:52, NEcoefs_new$Group_1$dmi_coef, col = "blue1", lwd = 1.5, lty = 2)
lines(1:52, NEcoefs_new$Group_1$tsa_coef, col = "darkorange", lwd = 1.5, lty = 2)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = new2_names,
       col = new2_col, 
       lty = new2_lty, lwd = 2, bty = "o") #, bg = "white")


par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, NE_coefs$Group_2$nino_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "NE Aus : Group 2 Coefficients", ylim = range(NEgroup2_new), 
     col = "magenta3", lwd = 1.5)
lines(1:52, NE_coefs$Group_2$dmi_coef, col = "cyan4", lwd = 1.5)
lines(1:52, NEcoefs_new$Group_2$nino_coef, col = "magenta4", lwd = 1.5, lty = 2)
lines(1:52, NEcoefs_new$Group_2$dmi_coef, col = "blue1", lwd = 1.5, lty = 2)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = new_names,
       col = new_col, 
       lty = new_lty, lwd = 2, bty = "o") #, bg = "white")


par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, NE_coefs$Group_3$nino_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "NE Aus : Group 3 Coefficients", ylim = range(NEgroup3_new), 
     col = "magenta3", lwd = 1.5)
lines(1:52, NE_coefs$Group_3$dmi_coef, col = "cyan4", lwd = 1.5)
lines(1:52, NEcoefs_new$Group_3$nino_coef, col = "magenta4", lwd = 1.5, lty = 2)
lines(1:52, NEcoefs_new$Group_3$dmi_coef, col = "blue1", lwd = 1.5, lty = 2)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = new_names,
       col = new_col, 
       lty = new_lty, lwd = 2, bty = "o") #, bg = "white")


par(mar = c(5, 4, 4, 9) + 0.2, xpd = TRUE)  # Increase the right margin (fourth value) to make space for the legend
plot(1:52, NE_coefs$Group_4$nino_coef, type = "l", xlab = "Lag", ylab = "Coefficients",
     main = "NE Aus : Group 4 Coefficients", ylim = range(NEgroup4_new), 
     col = "magenta3", lwd = 1.5)
lines(1:52, NE_coefs$Group_4$dmi_coef, col = "cyan4", lwd = 1.5)
lines(1:52, NEcoefs_new$Group_4$nino_coef, col = "magenta4", lwd = 1.5, lty = 2)
lines(1:52, NEcoefs_new$Group_4$dmi_coef, col = "blue1", lwd = 1.5, lty = 2)
segments(x0 = -1, y0 = 0, x1 = 54, y1 = 0, lty = 2)
legend("topright", inset = c(-0.3, 0),
       legend = new_names,
       col = new_col, 
       lty = new_lty, lwd = 2, bty = "o") #, bg = "white")


```


# 3. Relaxed Lasso

Explore using a relaxed lasso for our data so that we are only looking at the essential lag values.

So far, so good. What's next:
-perform for all response groups with predictions.
-check on glmnet followed by relaxed.glmnet (with different alpha values).
-repeat with different response groups sizes. 

```{r}

#modify pred/resp for above code to include relaxed and the correct data.
#full model
NE_preds <- NElag_grouping(NE_laglist = NE_laglist_std, j = -c(19))
NE_resp <- NEresp_grouping(NEAus_mat = NEAus_mat, j = -c(19))

SE_preds <- SElag_grouping(SE_laglist = SE_laglist_std, j = -c(19))
SE_resp <- SEresp_grouping(SEAus_mat = SEAus_mat, j = -c(19))


test_X <- as.matrix(SE_preds[[2]])
test_y <- SE_resp[[2]]

set.seed(351)
test_cv <- cv.glmnet(test_X, test_y, alpha = 0.5, nfolds = 5, relax = TRUE)
plot(test_cv)

test_fit <- glmnet(test_X, test_y, alpha = 0.5, relax = TRUE)

plot(test_fit, gamma = 0.75)
xline(log(test_cv$relaxed$lambda.min))
xline(log(test_cv$relaxed$lambda.1se), col = "red", lty = 2)

plot(test_fit, gamma = test_cv$relaxed$gamma.min)
xline(log(test_cv$relaxed$lambda.min))
xline(log(test_cv$relaxed$lambda.1se), col = "red", lty = 2)

plot(test_fit, gamma = test_cv$relaxed$gamma.1se)
xline(log(test_cv$relaxed$lambda.min))
xline(log(test_cv$relaxed$lambda.1se), col = "red", lty = 2)

#plot(fit, gamma = 0.5, main = "gamma = 0.5")
#plot(fit, gamma = 0, main = "gamma = 0")

test_pred <- predict(test_fit, s = test_cv$relaxed$lambda.min,
                     gamma = test_cv$relaxed$gamma.1se,
                     type = "coefficients")

#test_pred <- predict(test_fit, s = test_cv$relaxed$lambda.min,
#                     gamma = 0.75,
#                     type = "coefficients")

coef_index <- test_pred@i
test_pred@Dimnames[[1]][test_pred@i+1]
test_pred@x

coef_df <- data.frame(names = test_pred@Dimnames[[1]][test_pred@i+1], value = test_pred@x)

plot(test_pred@x, pch = 16, ylab = "Coef")
yline(0, lty = 2)
xline(c(1.5, 7.5, 16.5, 18.5, 26.5), col = "red", lty = 2)
```

