---
title: "new_interaction"
author: "Ryan Peterson"
date: "2025-03-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r library}
suppressMessages( library(hierNet))

suppressMessages( library( colorspace)) #for some color alternatives
```

```{r data_functions}
# Data Set-Up
setwd("~/CO_AUS/Aus_CO-main/Interactions")

load( "Data/ne_data.rda")
load( "Data/se_data.rda")
load( "Data/bounded_data.rda")
load( "Data/data_matrix.rda")
load( "Data/lag_list.rda")
load( "Data/data_quantile.rda")

#functions:
source("group_functions.R") #grouping/clustering
```

Goal of this is to include interaction terms into our methodology.

Beginning with:
1. hierNet
2. Adding indicator terms into Will's quadratic fit. 
3. Other hierarchical methods.

#1 HierNet

Notes on HierNet:
- Use weak hierarchy to start
- Slowly build up with increasing "groups" of parameters.

Using different response groupings:
1. Base response clusters (e.g 4 groups)
2. Split response groups (2 groups; early/late)
3. Full response for each region

## Base Response Groups

NE Groups:
1. Weeks 35-46; Index 1-12
2. Weeks 47-51; Index 13-17
3. Weeks 52,1-3; Index 18-21
4. Weeks 4-14; Index 22-32

SE Groups:
1. Weeks 35-41; Index 1-7
2. Weeks 42-50; Index 8-16
3. Weeks 51,52,1,2; Index 17-20
4. Weeks 3-14; Index 21-32

```{r setup}
#set up 

#season years/weeks
season_weeks <- c(35:52, 1:14)
season_years <- unique(bounded_resp_df$year)

seasons <- c()
for (i in 1:(length(season_years)-1)) {
  temp_season <- paste0(season_years[i], "-", season_years[i+1])
  #print(temp_season)  
  seasons <- c(seasons, temp_season)
}
rm(i, temp_season)

#center response data
NEbase_matrix <- scale(resp_matrix[ ,1:32], center = TRUE, scale = FALSE)
SEbase_matrix <- scale(resp_matrix[ ,33:64], center = TRUE, scale = FALSE)

#group response matrices
#NEAus
NEAus_1 <- NEbase_matrix[ ,1:12] #early season
NEAus_2 <- NEbase_matrix[ ,13:17] #primary NE fire season
NEAus_3 <- NEbase_matrix[ ,18:21] #feedback from SE
NEAus_4 <- NEbase_matrix[ ,22:32] #late season

#SEAus
SEAus_1 <- SEbase_matrix[ ,1:7] #early season
SEAus_2 <- SEbase_matrix[ ,8:16] #feedback from NE
SEAus_3 <- SEbase_matrix[ ,17:20] #primary SE fire season
SEAus_4 <- SEbase_matrix[ ,21:32] #late season

NEAus_mat <- list(NEAus_1, NEAus_2, NEAus_3, NEAus_4)
SEAus_mat <- list(SEAus_1, SEAus_2, SEAus_3, SEAus_4)

rm(NEAus_1, NEAus_2, NEAus_3, NEAus_4, SEAus_1, SEAus_2, SEAus_3, SEAus_4)
```

```{r model_data}
#full model
NE_preds <- NElag_grouping(NE_laglist = NE_laglist_std, j = -c(19))
NE_resp <- NEresp_grouping(NEAus_mat = NEAus_mat, j = -c(19))

SE_preds <- SElag_grouping(SE_laglist = SE_laglist_std, j = -c(19))
SE_resp <- SEresp_grouping(SEAus_mat = SEAus_mat, j = -c(19))

#quantile 90 indicator
NE_preds_q90 <- NElag_grouping(NE_laglist = NE_laglist_q90, j = -c(19))
SE_preds_q90 <- SElag_grouping(SE_laglist = SE_laglist_q90, j = -c(19))

#quantile 75 indicator
NE_preds_q75 <- NElag_grouping(NE_laglist = NE_laglist_q75, j = -c(19))
SE_preds_q75 <- SElag_grouping(SE_laglist = SE_laglist_q75, j = -c(19))
```

### Testing (Building-up Model)

Develop hierNet with simpler combinations
- Nino + DMI

```{r test_block}

NE_path <- list()
NE_cv <- list()
NE_fit <- list()

#TODO: change to for loop over all groups
n <- length(NE_resp) #setup for loop over list of groups
for (i in 1:n) {
  y_1 <- as.numeric(NE_resp[[i]])

  #using only nino/dmi
  X_1 <- cbind(as.matrix(NE_preds[[i]][ ,1:104]),
             as.matrix(NE_preds_q75[[i]][ ,1:104])  )

  #path -> cv -> fit
  temp_path <- hierNet.path( X_1, y_1, strong = FALSE, diagonal = TRUE)
  temp_cv <- hierNet.cv(temp_path, X_1, y_1, nfolds = 5)

  temp_fit <- hierNet(X_1, y_1, lam = temp_cv$lamhat, strong = FALSE, diagonal = TRUE)
  
  NE_path[[paste0("Group_", i)]] <- temp_path
  NE_cv[[paste0("Group_", i)]] <- temp_cv
  NE_fit[[paste0("Group_", i)]] <- temp_fit
}

plot(NE_cv[[1]])
plot(NE_cv[[2]])
plot(NE_cv[[3]])
plot(NE_cv[[4]])

#SE--------------##
SE_path <- list()
SE_cv <- list()
SE_fit <- list()

n <- length(SE_resp) #setup for loop over list of groups
for (i in 1:n) {
  y_1 <- as.numeric(SE_resp[[i]])

  #using only nino/dmi
  X_1 <- cbind(as.matrix(SE_preds[[i]][ ,1:104]),
                as.matrix(SE_preds_q75[[i]][ ,1:104]  ))

  #path -> cv -> fit
  temp_path <- hierNet.path( X_1, y_1, strong = FALSE, diagonal = TRUE)
  temp_cv <- hierNet.cv(temp_path, X_1, y_1, nfolds = 5)

  temp_fit <- hierNet(X_1, y_1, lam = temp_cv$lamhat, strong = FALSE, diagonal = TRUE)
  
  SE_path[[paste0("Group_", i)]] <- temp_path
  SE_cv[[paste0("Group_", i)]] <- temp_cv
  SE_fit[[paste0("Group_", i)]] <- temp_fit
}

plot(SE_cv[[1]])
plot(SE_cv[[2]])
plot(SE_cv[[3]])
plot(SE_cv[[4]])

```

```{r predict}
NE_new <- NElag_grouping(NE_laglist = NE_laglist_std, j = 19)
SE_new <- SElag_grouping(SE_laglist = SE_laglist_std, j = 19)

NE_resp <- NEresp_grouping(NEAus_mat = NEAus_mat, j = 19)
SE_resp <- SEresp_grouping(SEAus_mat = SEAus_mat, j = 19)

#quantile 75 indicator
NE_preds_q75 <- NElag_grouping(NE_laglist = NE_laglist_q75, j = 19)
SE_preds_q75 <- SElag_grouping(SE_laglist = SE_laglist_q75, j = 19)

ne_yhat <- list()
neresp_new <- c()
n <- length(NE_resp)
for (i in 1:n) {
  y_1 <- as.numeric(NE_resp[[i]])
  neresp_new <- c(neresp_new, y_1)
  
  X_1 <- cbind(as.matrix(NE_new[[i]][ ,1:104]),
             as.matrix(NE_preds_q75[[i]][ ,1:104])  )
  yhat <- predict(NE_fit[[i]], X_1)
  
  ne_yhat[[paste0("Group_", i)]] <- yhat
}


se_yhat <- list()
seresp_new <- c()
n <- length(SE_resp)
for (i in 1:n) {
  y_1 <- as.numeric(SE_resp[[i]])
  seresp_new <- c(seresp_new, y_1)
  
    
  X_1 <- cbind(as.matrix(SE_new[[i]][ ,1:104]),
             as.matrix(SE_preds_q75[[i]][ ,1:104])  )
  yhat <- predict(SE_fit[[i]], X_1)
  
  se_yhat[[paste0("Group_", i)]] <- yhat
}


y_nehat <- c(ne_yhat[[1]], ne_yhat[[2]], ne_yhat[[3]], ne_yhat[[4]]) 
y_sehat <- c(se_yhat[[1]], se_yhat[[2]], se_yhat[[3]], se_yhat[[4]]) 

NE_g1 <- seq(12, 216, length.out = 18)
NE_g2 <- seq(5, 90, length.out = 18)
NE_g3 <- seq(4, 72, length.out = 18)
NE_g4 <- seq(11, 198, length.out = 18)


SE_g1 <- seq(7, 126, length.out = 18)
SE_g2 <- seq(9, 162, length.out = 18)
SE_g3 <- seq(4, 72, length.out = 18)
SE_g4 <- seq(12, 216, length.out = 18)
```


```{r }
#TODO: do full season predictions (Create nice in/out of sample preds along with residual plots)

plot(1:32, neresp_new,  type = "l")
lines(1:32, y_nehat, col = "magenta3")
abline(h = 0, lty = 2)

plot(1:32, seresp_new,  type = "l")
lines(1:32, y_sehat, col = "magenta3")
abline(h = 0, lty = 2)
```

### Predictions

```{r}
NE_season <- list()
SE_season <- list()

for (k in 1:18) {
    
  NE_new <- NElag_grouping(NE_laglist = NE_laglist_std, j = k)
  SE_new <- SElag_grouping(SE_laglist = SE_laglist_std, j = k)
  
  NE_resp <- NEresp_grouping(NEAus_mat = NEAus_mat, j = k)
  SE_resp <- SEresp_grouping(SEAus_mat = SEAus_mat, j = k)
  
  #quantile 75 indicator
  NE_preds_q75 <- NElag_grouping(NE_laglist = NE_laglist_q75, j = k)
  SE_preds_q75 <- SElag_grouping(SE_laglist = SE_laglist_q75, j = k)
  
  ne_yhat <- list()
  neresp_new <- c()
  n <- length(NE_resp)
  for (i in 1:n) {
    y_1 <- as.numeric(NE_resp[[i]])
    neresp_new <- c(neresp_new, y_1)
    
    X_1 <- cbind(as.matrix(NE_new[[i]][ ,1:104]),
               as.matrix(NE_preds_q75[[i]][ ,1:104])  )
    yhat <- predict(NE_fit[[i]], X_1)
    
    ne_yhat[[paste0("Group_", i)]] <- yhat
  }
  
  
  se_yhat <- list()
  seresp_new <- c()
  n <- length(SE_resp)
  for (i in 1:n) {
    y_1 <- as.numeric(SE_resp[[i]])
    seresp_new <- c(seresp_new, y_1)
    
      
    X_1 <- cbind(as.matrix(SE_new[[i]][ ,1:104]),
               as.matrix(SE_preds_q75[[i]][ ,1:104])  )
    yhat <- predict(SE_fit[[i]], X_1)
    
    se_yhat[[paste0("Group_", i)]] <- yhat
  }
  
  
  y_nehat <- c(ne_yhat[[1]], ne_yhat[[2]], ne_yhat[[3]], ne_yhat[[4]]) 
  y_sehat <- c(se_yhat[[1]], se_yhat[[2]], se_yhat[[3]], se_yhat[[4]]) 
  
  NE_season[[paste0("Season_", seasons[k])]] <- y_nehat
  SE_season[[paste0("Season_", seasons[k])]] <- y_sehat
  
  #visualizations
  x_vals <- 1:32
  
  setwd("~/CO_AUS/Aus_CO-main/Interactions")
  
  f_names <- paste0("Season_", seasons[k],".png" )
  
  png(filename = f_names, width = 3200, height = 1600, res = 200)
  set.panel(1,2)
  #par(mar = c(7, 4, 4, 11) + 0.3, xpd = TRUE) 
  plot(x_vals, neresp_new, type = "l", lwd = 2, ylim = range(neresp_new, y_nehat), 
          ylab = "Atmospheric CO",
          xlab = "",  main = paste0("NE Aus: ", seasons[k]), axes = FALSE, 
          cex.main = 2.25, cex.lab = 1.5, cex.axis = 1.5)
  box()
  axis(2)
  axis(1, at = 1:32, labels = c(paste0("Week ", season_weeks)),
       las = 3, cex.axis = 1.6)
  lines(1:32, y_nehat, col = "magenta3", lwd = 2)
  abline(h = 0, lty = 2) #TODO: correct this line
  
  #par(mar = c(7, 4, 4, 11) + 0.3, xpd = TRUE) 
  plot(x_vals, seresp_new, type = "l", lwd = 2, ylim = range(seresp_new, y_sehat), 
          ylab = "Atmospheric CO",
          xlab = "",  main = paste0("SE Aus: ", seasons[k]), axes = FALSE, 
          cex.main = 2.25, cex.lab = 1.5, cex.axis = 1.5)
  box()
  axis(2)
  axis(1, at = 1:32, labels = c(paste0("Week ", season_weeks)),
       las = 3, cex.axis = 1.6)
  lines(1:32, y_sehat, col = "magenta3", lwd = 2)
  abline(h = 0, lty = 2) #TODO: correct this line
  

}

dev.off()
```


### Residuals

```{r}
#get residuals (y - yhat)
NE_resids <- matrix(NA, ncol = 32)
SE_resids <- matrix(NA, ncol = 32)

for (k in 1:18) {
  temp_NE <- NEbase_matrix[k, ] - NE_season[[k]]
  temp_SE <- SEbase_matrix[k, ] - SE_season[[k]]
  
  NE_resids <- rbind(NE_resids, temp_NE)
  SE_resids <- rbind(SE_resids, temp_SE)
}

NE_resids <- NE_resids[-1, ]
SE_resids <- SE_resids[-1, ]

```


```{r}
boxplot(NE_resids, pch = 20, ylim = c(-20,20))
abline(h = 0, lty = 2)

boxplot(SE_resids, pch = 20, ylim = c(-20,20))
abline(h = 0, lty = 2)
```



```{r var_imp}
var_imp <- hierNet.varimp(test_fit, X_1, y_1)

plot(var_imp[,1], var_imp[,2], pch = 16)
```

### Coefficients

```{r coefs}

#TODO: get a good description of interactions
test_coef <- test_fit$bp-test_fit$bn

plot(1:52, test_coef[1:52], pch = 16, col = "red3")
points(1:52, test_coef[53:104], pch = 16, col = "blue3")
abline(h = 0)

set.panel(1,2)
image.plot(test_fit$th[ ,1:52], col = diverge_hsv(256))
image.plot(test_fit$th, col = diverge_hsv(256))
abline(h=0.5, lty = 2)

th_nino <- test_fit$th[1:52, 1:52]
th_dmi <- test_fit$th[53:104, 53:104]

nino_int <- which(th_nino !=0, arr.ind = TRUE)
dmi_int <- which(th_dmi !=0, arr.ind = TRUE)
#TODO: add coefs into the above matrices (change to df)

image.plot(test_fit$th[1:52, 1:52], col = diverge_hsv(256))
image.plot(test_fit$th[53:104, 53:104], col = diverge_hsv(256))

#temp <- (th+t(th))/2
#test_interact <- which(temp !=0, arr.ind = TRUE)


test_int[1:42,]

```



# glinternet 

Testing and exploring another form of interaction models with lasso

```{r test_code}
#TODO: delete when done


```

