---
title: "test_validation_cv.rmd"
author: "Ryan Peterson"
date: "2025-02-12"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Code for testing out modifications to cv.fusedlasso() (or similar variant) to perform various validation statistics.

Work on cv R^2 first, potentially include crps and int score

(Look into the predict function to figure out how the std error is determined and replicate this for crps and int score.)


```{r set-up}
#library, data, and functions

#libraries
suppressMessages(library(genlasso)) #used for fused lasso 
suppressMessages(library(MASS)) #for matrix shenanigans in functions.

# Data Set-Up
setwd("~/CO_AUS/Aus_CO-main")

load( "ne_data.rda")
load( "se_data.rda")
load( "bounded_data.rda")
load( "data_matrix.rda")
load( "lag_list.rda")

source("group_functions.R")
source("lasso_valid_functions.R") #include predict.fusedlasso
source("genlasso_func.R") #includes cv.fusedlasso (DO NOT USE in final work, correct and move)
source("predictionTest_functions.R") #

#additional function
Seq <- function(a, b, ...) {
  if (a<=b) return(seq(a,b,...))
  else return(numeric(0))
}


#set up season years/weeks
season_weeks <- c(35:52, 1:14)
season_years <- unique(bounded_resp_df$year)

seasons <- c()
for (i in 1:(length(season_years)-1)) {
  temp_season <- paste0(season_years[i], "-", season_years[i+1])
  #print(temp_season)  
  seasons <- c(seasons, temp_season)
}
rm(i, temp_season)

#center response data
NEbase_matrix <- scale(resp_matrix[ ,1:32], center = TRUE, scale = FALSE)
SEbase_matrix <- scale(resp_matrix[ ,33:64], center = TRUE, scale = FALSE)

#group response matrices
#NEAus
NEAus_1 <- NEbase_matrix[ ,1:3]
NEAus_2 <- NEbase_matrix[ ,4:8]
NEAus_3 <- NEbase_matrix[ ,9:12]
NEAus_4 <- NEbase_matrix[ ,13:17]
NEAus_5 <- NEbase_matrix[ ,18:21]
NEAus_6 <- NEbase_matrix[ ,22:32]

#SEAus
SEAus_1 <- SEbase_matrix[ ,1:3]
SEAus_2 <- SEbase_matrix[ ,4:7]
SEAus_3 <- SEbase_matrix[ ,8:16]
SEAus_4 <- SEbase_matrix[ ,17:20]
SEAus_5 <- SEbase_matrix[ ,21:32]

NEAus_mat <- list(NEAus_1, NEAus_2, NEAus_3, NEAus_4, NEAus_5, NEAus_6)
SEAus_mat <- list(SEAus_1, SEAus_2, SEAus_3, SEAus_4, SEAus_5)

rm(NEAus_1, NEAus_2, NEAus_3, NEAus_4, NEAus_5, NEAus_6, SEAus_1, SEAus_2, SEAus_3, SEAus_4, SEAus_5)


# distance matrices
D <- getD1d(52)
empty_D <- matrix(rep(0, (52*51)) , ncol = 52, nrow = 51)

#Update for OLR (D5)
D1 <- cbind(D, empty_D, empty_D, empty_D, empty_D)
D2 <- cbind(empty_D, D, empty_D, empty_D, empty_D)
D3 <- cbind(empty_D, empty_D, D, empty_D, empty_D)
D4 <- cbind(empty_D, empty_D, empty_D, D, empty_D)
D5 <- cbind(empty_D, empty_D, empty_D, empty_D, D)

D_olr <- rbind(D1, D2, D3, D4, D5)

rm(D, empty_D, D1, D2, D3, D4, D5)

# grouping functions 

#full model
NE_preds <- NElag_grouping(NE_laglist = NE_laglist_std, j = -c(19))
NE_resp <- NEresp_grouping(NEAus_mat = NEAus_mat, j = -c(19))

SE_preds <- SElag_grouping(SE_laglist = SE_laglist_std, j = -c(19))
SE_resp <- SEresp_grouping(SEAus_mat = SEAus_mat, j = -c(19))


```


```{r functions}


#updated cv.fusedlasso to include 
#TODO: build test function
cv.validation <- function(object, k =5, D) {
  cl = match.call()
  
  y <- object$y
  X <- object$X
  D_new <- Matrix(D, sparse=TRUE)
  n <- length(y)
  
  foldid <- c(0, rep(Seq(1, k), n-2)[Seq(1, n-2)], 0) #fold id
  lambda <- object$lambda
  
  cvall <- matrix(0, nrow = k, ncol = length(lambda))
  cvr2 <- matrix(0, nrow = k, ncol = length(lambda))
  
  for (i in Seq(1, k)) {
    
    otr <- which(foldid != i) #training id 
    ntr <- length(otr) #length of training data
    ytr <- y[otr] #training response
    Xtr <- X[otr, ] #training predictors
    
    gamma <- object$gamma
    
    out_new <- fusedlasso(y = ytr, X = Xtr, D, gamma = gamma, minlam = min(lambda))
    
    b_new <- coef(out_new, lambda = lambda)$beta
    
    ote <- which(foldid == i) #testing id
    yte <- matrix(y[ote], length(ote), length(lambda)) #testing data
    Xte <- X[ote, ]
    
    pred_new <- Xte%*%b_new
    cvall[i,] <- colMeans((yte-pred_new)^2) #cv mse
    cvr2[i, ] <- 1-(colMeans((yte-pred_new)^2)/var(y[ote])) #cv r^2
    
  }
  #directly from cv.trendfilter.R
  cverr <- colMeans(cvall)
  #cvse <- apply(cvall,2,sd)/sqrt(k)
  names(cverr) = round(lambda,3)
  i0 = which.min(cverr)
  lam.min = lambda[i0]
  i.min = which(lambda==lam.min)
  
  
  out_ls <- list(MSE = cvall[,i.min], R2 = cvr2[,i.min], lambda_min = lam.min)
  return(out_ls)
}

```


# Function testing
Building cv.validation()

add in:
-cv r^2
-cv rmse
-cv scoring functions

```{r}


NE_gamma <- 0.85
NEfuse_grouplist <- list()
NEfuse_cv <- list()
NE_lambdamin <- c()

j <- 1
NEresp_temp <- NE_resp[[j]]
NEpred_temp <- as.matrix(NE_preds[[j]][ ,1:260])

NEgroup_temp <- fusedlasso(y = NEresp_temp, X = NEpred_temp, D_olr, gamma = NE_gamma)
#NEgroup_cv <- cv.fusedlasso(NEgroup_temp, k =10, D_olr) 

#TODO: move this into lasso cv code
test_list <- cv.validation(NEgroup_temp, k = 10, D = D_olr)

test_list[[3]]

#params:
object <- NEgroup_temp #fusedlasso object  
k <- 10 #number of folds
D <- D_olr #D matrix

cl = match.call()
  
y <- object$y
X <- object$X
D_new <- Matrix(D, sparse=TRUE)
n <- length(y)
  
foldid <- c(0, rep(Seq(1, k), n-2)[Seq(1, n-2)], 0) #fold id
lambda <- object$lambda
  
cvall <- matrix(0, nrow = k, ncol = length(lambda))
cvr2 <- matrix(0, nrow = k, ncol = length(lambda))

#Seq(1, k)
for (i in Seq(1, k)) {
#i <- 1 #fold 1 test
    
  otr <- which(foldid != i) #training id 
  ntr <- length(otr) #length of training data
  ytr <- y[otr] #training response
  Xtr <- X[otr, ] #training predictors
  
  gamma <- object$gamma
  
  out_new <- fusedlasso(y = ytr, X = Xtr, D, 
                        gamma = gamma, minlam = min(lambda))
  
  b_new <- coef(out_new, lambda = lambda)$beta
  
  ote <- which(foldid == i) #testing id
  yte <- matrix(y[ote], length(ote), length(lambda)) #testing data
  Xte <- X[ote, ]
  
  pred_new <- Xte%*%b_new
  cvall[i,] <- colMeans((yte-pred_new)^2) #cv mse
  cvr2[i, ] <- 1-(colMeans((yte-pred_new)^2)/var(y[ote])) #cv r^2
  

}
#get pred sd (might not work with lasso)
#pred_sd <- apply(pred_new, 2, sd)

#directly from cv.trendfilter.R
cverr <- colMeans(cvall)
#cvse <- apply(cvall,2,sd)/sqrt(k)
names(cverr) = round(lambda,3)
i0 = which.min(cverr)
lam.min = lambda[i0]
i.min = which(lambda==lam.min)


out_ls <- list(MSE = cvall[,i.min], R2 = cvr2[,i.min], lambda_min = lam.min)


```


```{r}
NE_gamma <- 0.85
NEfuse_grouplist <- list()
NEvalid_cv <- list()
NE_lambdamin <- c()

n <- length(NE_resp)
for (i in 1:n) {
  NEresp_temp <- NE_resp[[i]]
  NEpred_temp <- as.matrix(NE_preds[[i]][ ,1:260])
  
  NEgroup_temp <- fusedlasso(y = NEresp_temp, X = NEpred_temp, D_olr, gamma = NE_gamma)
  
  NEgroup_cv <- cv.validation(NEgroup_temp, k =10, D_olr) 
  
  #note: NEgroup_cv[[3]] lambda min  
  NE_lambdamin <- c(NE_lambdamin, NEgroup_cv[[3]])  
  NEfuse_grouplist[[paste0("Group_", i)]] <- NEgroup_temp
  NEvalid_cv[[paste0("Group_", i)]] <- NEgroup_cv
}


SE_gamma <- 0.85
SEfuse_grouplist <- list()
SEvalid_cv <- list()
SE_lambdamin <- c()

n <- length(SE_resp)
for (i in 1:n) {
  SEresp_temp <- SE_resp[[i]]
  SEpred_temp <- as.matrix(SE_preds[[i]][ ,1:260])
  
  SEgroup_temp <- fusedlasso(y = SEresp_temp, X = SEpred_temp, D_olr, gamma = SE_gamma)
  
  SEgroup_cv <- cv.validation(SEgroup_temp, k =10, D_olr) 
  
  #note: SEgroup_cv[[3]] lambda min  
  SE_lambdamin <- c(SE_lambdamin, SEgroup_cv[[3]]) 
  SEfuse_grouplist[[paste0("Group_", i)]] <- SEgroup_temp
  SEvalid_cv[[paste0("Group_", i)]] <- SEgroup_cv
}

save(SEfuse_grouplist, NEfuse_grouplist, file = "fuse_grouplist.rda")
save(NEvalid_cv, SEvalid_cv, file = "valid_cv.rda")
```


## CV Validation

```{r}

NE_rmse <- c()
NE_r2 <- c()
NE_r2sd <- c()
for(j in 1:length(NEvalid_cv)) {
  NE_rmse <- c(NE_rmse, sqrt(mean(NEvalid_cv[[j]]$MSE)))
  NE_r2 <- c(NE_r2, mean(NEvalid_cv[[j]]$R2))
  NE_r2sd <- c(NE_r2sd, sd(NEvalid_cv[[j]]$R2))
}

SE_rmse <- c()
SE_r2 <- c()
SE_r2sd <- c()
for(j in 1:length(SEvalid_cv)) {
  SE_rmse <- c(SE_rmse, sqrt(mean(SEvalid_cv[[j]]$MSE)))
  SE_r2 <- c(SE_r2, mean(SEvalid_cv[[j]]$R2))
  SE_r2sd <- c(SE_r2sd, sd(SEvalid_cv[[j]]$R2))
}

NE_r2
SE_r2

SEvalid_cv[[1]]$R2
```


# CV: lambda min v. 1se

```{r}
#looking at cv.fusedlass() standard error values
k <- 2 #group

#plot lambdas (again)
plot(NEfuse_cv[[k]])

temp_cv <- NEfuse_cv[[k]]

temp_cv$lambda.min
temp_cv$lambda.1se

temp_cv$se[temp_cv$i.min]
temp_cv$se[temp_cv$i.1se]

#k-fold rmse
sqrt(temp_cv$err[temp_cv$i.min])

#SEfuse_cv


```

# Coeffs

```{r}

NEcoef_cv1 <- coef(NEfuse_grouplist[[k]], lambda = temp_cv$lambda.min)
NEcoef_cv2 <- coef(NEfuse_grouplist[[k]], lambda = temp_cv$lambda.1se)  

NEfuse1 <- NEcoef_cv1$beta
NEfuse2 <- NEcoef_cv2$beta
```

